### 2019-11-14 paper/acks.tex
the first draft

\section{Acknowledgments}

Osama Ashraf would like to thank the Egyptian Ministry of Higher Education (MoHE), as well as MEPhI's Competitiveness Program for providing financial support for this research. The facility and tools needed to conduct this work were supported by MEPhI.

The authors contributed to this work as described below.

Osama Ashraf conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper.

Andrei Rykhlevskii conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper. Andrei Rykhlevskii 
is supported by  DOE ARPA-E MEITNER program award DE-AR0000983.

G. V. Tikhomirov directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper. Prof. Tikhomirov is supported by Rosatom, he is Deputy Director of the Institute of Nuclear Physics and Engineering MEPhI. Board member of Nuclear society of Russia.

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the NNSA Office of Defense Nuclear Nonproliferation R\&D through the Consortium for Verification Technologies and the Consortium for Nonproliferation Enabling Capabilities,  the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 and 
ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the 
University of Illinois at Urbana-Champaign and its National Center for 
Supercomputing Applications

### 2019-11-14 paper/conclusion.tex
the first draft

\section{Conclusion} \label{Conclusion}

\section{Future work}

\section{Declaration of Competing Interest}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

### 2019-11-14 paper/introduction.tex
the first draft

\section{Introduction} \label{Introduction}

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). The MSR is the only liquid-fueled reactor among these reactors. Major nuclear centers pursue MSRs with renewed interest \cite{betzler_impacts_2019,ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}. The MSR is a promising technology because of its dynamics, especially for thorium fuel utilization. However, this technology has challenges in safety, online reprocessing, and fuel handling. Safety is one of the technological goals of the MSR systems that require further research and investigation. The unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, etc.) strongly affect its control system design. The MSRs have a negative temperature coefficient of reactivity. Doppler effect and thermal expansion of the fuel reduce core reactivity when the core heats up. However, graphite thermal expansion positively affect the core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a dominating factor, thus core reactivity will decrease automatically when the core heats up \cite{li_optimization_2018}. The MSR designs have a drain tank to collect the liquid fuel in an emergency case. A freeze plug, which located under the core, melts when the temperature reaches a critical point. Then the fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}

Safety aspects in the MSRs can be listed as follows \cite{elsheikh2013safety,merle2008optimization}:
\begin{enumerate}
\item The negative coefficient of reactivity - high core temperature will reduce reactivity.
\item The fuel feed rate - decreasing the refueling rate slows down and eventually stops the nuclear chain reaction.
\item The drain tanks, which have subcritical geometry and passively cooled.
\item The control rods compensate the excess reactivity, temperature regulation, and/or shut down the reactor.
\item The continuous removing of fission products and radioactive gasses minimize the chance of radiation exposure.
\item The reactor system chamber.
\item The outer containment vessel.
\end{enumerate}

At the Beginning of Life (BOL), we must load the MSR with larger amount of fuel than that required to achieve criticality (necessary for long term core operation). This leads to excess reactivity at the BOL \cite{duderstadt650nuclear}. Additionally, during burnup, the online reprocessing and refueling leads to change the reactivity of the MSRs \cite{ashraf2019whole_core}. The most common procedure for reactor control is to insert or withdraw control rods with large neutron absorption cross section (e.g. boron and cadmium) \cite{duderstadt650nuclear}. The control rods introduce an amount of negative reactivity into the core. This negative reactivity helps to compensate the excess reactivity and adjust the power level of the core or even shut down the reactor in an emergency situation \cite{glasstone1967nuclear}. Therefore, we should estimate the reactivity worth of the control rods \cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}. The reactivity worth of control rods correlates with the interference (shadowing effects) between control rod clusters. \cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is used in control rods \cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. However, we may need to enrich the effective boron isotope ($^{10}$B) to reach the necessary absorptivity. Notably, the spatial self-shielding effect correlates with $^{10}$B concentration.
For example, B$_4$C enriched to 90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its absorption ability is about 2.3 times compared with natural B$_4$C. Additionally, issues related to helium gas release, swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C lifespan \cite{guo2019optimized}.

Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the potential alternative absorbers in Generation-IV reactors such as hafnium-based materials and rare earth element oxides. These absorbers have high thermal conductivity, good resistance to neutron irradiation, and release no gas \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2250 MW$_{th}$ \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated molten salt reactor. Recent studies on MSRs show that the excess reactivity at the beginning of the operation is quite large for many fueling scenarios \cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}. Adjusting fertile and fissile feed rates helps to control the reactivity of the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a reliable safety system beside the online feed system to control the excess reactivity. Therefore, the main objective of our study is to introduce a new safety system based on control rods in the \gls{SD-TMSR} to control the reactivity during normal operation. Five different absorber materials are applied to study the main neutronics and safety parameters in the SD-TMSR. We focus on the control rod design, absorption ability, integral and differential control rod worths, shutdown margin of absorber materials, and shadowing effects at steady state calculation.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system in the GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes \cite{petrie1984keno} to calculate the reactivity worth and analyze the performance of this control system \cite{vcerba2017optimization}. Since no final geometry design of the control rods system is available for the SD-TMSR, \v{C}erba's methodology \cite{vcerba2017optimization}  helped us as a starting point of this analysis.

All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.

This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

### 2019-11-14 paper/methods.tex
the first draft

\section{Model description} \label{Model-description}
\subsection{Reactor design}

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2250 MW$_{th}$. The 
design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
\cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential} after modifying the geometry to 
control the positive temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry is described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2019whole_core}. The active zone of the \gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile materials). Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} LWR \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, respectively.
The liquid fuel salt circulates continuously through the fuel tubes that pierce the graphite hexagonal 
prisms. The active zone is surrounded by axial and radial graphite reflectors to minimize the neutron leakage. Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of a Hastelloy N alloy. The main 
characteristics of the \gls{SD-TMSR} are summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | l}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Control rod design} \label{CRD}

The reactivity of the SD-TMSR core is controlled through two systems of control assemblies:
\begin{enumerate}
\item The Control Safety Devices (CSD), and
\item The Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, five different absorber materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item B$_4$C with boron enriched to 90\% $^{10}$B isotope,
\item hafnium diboride (HfB$_2$),
\item hafnium hydride (HfH$_{1.62}$),
\item gadolinium oxide (Gd$_2$O$_3$), and
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}
Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching B$_4$C increases the fraction of highly neutron absorber isotope (i.e. $^{10}$B) and helps to reach the necessary absorptivity. However, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. The absorber material is surrounded by a 0.25-cm-thick clad made of AIM1 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of SiC structural material (see Figure~\ref{fig:cr}). A small gap between the cladding and rod follower is considered to facilitate the control rod movement.

Since the total quantity and distribution of the SD-TMSR control assemblies are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the four control rods. The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{Graphite element with the four control rods (cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{Axial view of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring). The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red color stands for SSD1-9 clusters.
We distributed the graphite elements with control rods clusters homogeneously in the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
The selected core segment in the above corner of the Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four control rods located at the same distance from the fuel channel.

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core.}
	\label{fig:core_25}
\end{figure}

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}

In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to perform steady state calculations for the full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with control rod design. We adopted the ENDF-VII.0 cross section library for all calculations in the present work. The results demonstrate whole-core runs of $12.5\times 10^6$ neutron histories per depletion step. The statistical error in $k_{eff}$ from SERPENT-2 output is equal to $\pm$ $25$ $pcm$.

The initial calculation state of the SD-TMSR is identified by normal operation conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods clusters. In this case, the control rods are located above the upper plenum as shown in Figure~\ref{fig:core_26}. To validate the proposed control rods system we adopted the same operation conditions (as in the initial case) and changed the position of the control rod clusters along $Z$ direction. The main calculated parameters including reactivity, control rod worth, and interference effects (shadowing effects) will describe in the following parts.

\begin{figure}[t!] % replace 't' with 'b' to \centering
	\centering
	\includegraphics[width=\textwidth]{core_26.png}
	\caption{$XZ$ section of the full-core model of the SD-TMSR, CRs are fully withdrawn.}
	\label{fig:core_26}
\end{figure}

\subsubsection{Reactivity calculation}

The excess reactivity $\rho$$_e$ is the reactivity of the core when all control rods are withdrawn. $\rho$$_e$ is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core and $\beta_{eff}$ is the effective fraction of delayed neutrons. The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using perturbation technique in SERPENT-2 \cite{leppanen2014calculation}.

\begin{equation}
\label{Equ:1}
{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}{{\beta}_{eff}}},
\end{equation}

\subsubsection{The control rod worths (CRW)}

The control rod worth (CRW) is the amount of negative reactivity that associated with the control rod insertion. The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after i$^{th}$ CR insertion \cite{vcerba2017optimization}.

\begin{equation}
\label{Equ:2}
{{\Delta}{\rho}_{CRi}}={{\rho}_{e}}-{{\rho}_{CRi}},
\end{equation}

\subsubsection{Shutdown Margin (SDM)}

The shutdown margin (SDM) is the amount of reactivity by which a full reactor core is subcritical from a given state. The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity.

\begin{equation}
\label{Equ:6}
{SDM}={{\Delta}{\rho}_{SSD}}-{{\rho}_{e}},
\end{equation}

\subsubsection{Interference effects (shadowing effects)}

Interference between control rods (CRs) or shadowing effects occurs when one (or more) control rod affects the reactivity worth of another control rod in the surroundings. Thus, anti-shadowing is observed when the combined rod worth is greater than the sum of the individual worths, however, the shadowing effect appears when the combined rod worth is less than the sum of the individual worths.
The core height-to-diameter ratio (H/D) and the three-dimensional configuration of the control rods affect the degree of the interference between CRs \cite{girardin2007control}.

The amplification factor (A$_{CRi}$) of i$^{th}$ control rod helps to evaluate the shadowing effects between control rod clusters. The amplification factor is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all control rods (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the investigated one i$^{th}$ and $\Delta\rho$$_{CRi}$ the worth of the i$^{th}$ rod.

\begin{equation}
\label{Equ:3}
{{A}_{CRi}}=\dfrac{{{\Delta}{\rho}_{CR(1,2,\ldots N)}}-{{\Delta}{\rho}_{CR(1,2,\ldots N-i)}}}{{\Delta}{\rho}_{CRi}},
\end{equation}

If A$_{CRi}$ is $<$1, the control rod worth is reduced due to shadowing effects, while if A$_{CRi}$ is $>$1 the control rod worth is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.

\subsubsection{Integral and differential control rod worth}

The integral CRW is the total reactivity change due to control rod insertion or withdrawal. However, the differential CRW is the amount of reactivity inserted per unit of withdrawal [$\$/cm$]. We change the position of CRs clusters parallel to the z-axis from top to the bottom of the core. Equation~\ref{Equ:4} is used to calculate the integral CRW [\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.

\begin{equation}
\label{Equ:4}
{{\Delta}{\rho}_{i}}=\sum_{i=1}^{N}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
\end{equation}

Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where $\Delta H$ is the height change of control rod [cm] before and after insertions.

\begin{equation}
\label{Equ:5}
\dfrac{{\partial}{\rho}_{i}}{{\partial{H}}}=\dfrac{1}{{\Delta}{H}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
\end{equation}

### 2019-11-14 paper/results.tex
the first draft

\section{Results and discussion} \label{Results-and-discussion}

\subsection{The excess reactivity $\rho$$_e$}

The full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is loaded by three different types of initial fissile materials: $^{233}$U, reactor-grade Pu, and transuranic (TRU) elements from \gls{LWR} \gls{SNF}.
The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state calculation), when all CRs are fully withdrawn. The excess reactivities for $^{233}$U, reactor-grade Pu, and TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively. For $^{233}$U case, the maximum excess reactivity $\rho$$_e$ is about $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of reactor operation (see Figure~\ref{fig:keff_25}). The SD-TMSR is able to control the reactivity by adjusting the online refueling and reprocessing rates. An effective and reliable reactivity control system must be designed beside the online feed system to operate with such reactivity changes during burnup.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2019whole_core}.} 
	\label{fig:keff_25}
\end{figure}

\subsection{Control rod parameters}

The control rod parameters including control rod worth (CRW), interference between CR clusters, and integral and differential control rod worths are described in this part. Five different absorber materials are considered based on their neutronics and safety performance (see part \ref{CRD}). The results of the control rod worth, the amplification factor (A$_{CRi}$), and the type of interference for the five absorber materials are listed in Table~\ref{tab:worth}.

\begin{sidewaystable}
	\tiny
	\centering
	\caption{The control rod worths and shadowing effects for different CR materials.}
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.6cm}|}
		\hline
		\multirow{2}{4em}{CR clusters}		& \multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	&\multicolumn{3}{c|}{HfH$_{1.62}$} &\multicolumn{3}{c|}{Gd$_2$O$_3$}	& 	\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
		\cline{2-16}
		&  $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Interference	&$\Delta\rho$$_{CRi}$ [\$]&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$ &	Interference \\
		\hline                   
		ALL CRs        				& $48.19\pm0.68$   &	&	&$40.4\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.7\pm0.4$	&	&	&$42.39\pm0.48$	& &	 \\
		\hline 
		CSD 							& $25.5\pm0.23$   &$1.24\pm0.01$	&$\star$	&$21.9\pm0.17$	&$1.1\pm0.01$	&$\star$	&$20.62\pm0.34$	&$1.1\pm0.01$	&$\star$	&$18.48\pm0.25$	&$1.17\pm0.01$	&$\star$	&$22.96\pm0.18$	&$1.2\pm0.01$ &$\star$ \\
		\hline 
		SSD		  		&$16.39\pm0.11$ &$1.38\pm0.02$	&$\star$	&$14.27\pm0.21$	&$1.29\pm0.01$	&$\star$	&$13.23\pm0.18$	&$1.3\pm0.06$	&$\star$	&$12\pm0.2$	&$1.26\pm0.01$	&$\star$	&$14.58\pm0.11$	&$1.3\pm0.02$	&$\star$ \\
		\hline 
		CSD inner ring  &  $18.42\pm0.05$  &$1.6\pm0.04$	&$\star$		&$16.29\pm0.29$	&$1.48\pm0.02$	&$\star$	&$15.5\pm0.17$	& $1.46\pm0.01$ &$\star$	&$14.12\pm0.07$	&$1.39\pm0.01$	&$\star$	&$16.92\pm0.13$	&$1.5\pm0.01$	 &$\star$\\
		\hline 
		CSD outer ring            	    &$2.26\pm0.02$ &$4.21\pm0.07$	&$\star$	&$2.1\pm0.06$	&$3.11\pm0.1$&$\star$	&$1.85\pm0.07$	&$3.24\pm0.06$	&$\star$	&$1.8\pm0.1$	&$2.54\pm0.14$	&$\star$	&$2.14\pm0.05$	&$3.2\pm0.05$	 &$\star$	\\  
		\hline 
		CSD2								& $2.25\pm0.04$   &$3.69\pm0.16$	&$\star$	&$2.24\pm0.05$	&$2.42\pm0.1$	&$\star$	&$2\pm0.1$	&$2.68\pm0.03$	&$\star$	&$1.8\pm0.1$	&$2.55\pm0.2$	&$\star$	&$2.19\pm0.12$	&$2.9\pm0.08$	&$\star$ \\
		\hline 
		CSD9								& $0.15\pm0.04$   & $10.53\pm0.01$	&$\star$$\star$	&$0.1\pm0.05$	&$5.1\pm0.05$	&$\star$	&$0.05\pm0.01$	&$16.4\pm0.1$	&$\star$$\star$	&$0.09\pm0.07$	&$5.55\pm0.2$	&$\star$$\star$	&$0.07\pm0.05$	&$14\pm0.1$	&$\star$$\star$ \\ 
		\hline
		SSD1					& $4.18\pm0.07$   &$1.59\pm0.08$	&$\star$	&$3.95\pm0.13$	&$1.3\pm0.07$	&$\star$	&$3.59\pm0.03$	&$1.49\pm0.01$	&$\star$	&$3.45\pm0.12$	&$1.4\pm0.08$	&$\star$	&$3.91\pm0.06$	&$1.4\pm0.01$&$\star$ \\
		\hline 
		SSD4					&  $0.57\pm0.09$  &$7.84\pm0.15$	&$\star$$\star$	&$0.63\pm0.06$	&$4.4\pm0.1$	&$\star$	&$1\pm0.05$	&$2.51\pm0.16$	&$\star$	&$0.6\pm0.8$	&$3.31\pm0.27$	&$\star$	&$0.6\pm0.08$	&$5.1\pm0.28$	&$\star$$\star$ \\
		\hline
	\end{tabularx}
	\begin{tablenotes}
		\tiny
		\item  $\star$  means anti-shadowing effects.
		\item  $\star$$\star$ means strong anti-shadowing effects.
	\end{tablenotes}
	\label{tab:worth}
\end{sidewaystable}

\subsubsection{CRW} \label{CR_worth}

The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ \$ (Table~\ref{tab:worth}). Enriched B$_4$C-90 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with the other absorber materials in this study. This result agrees with macroscopic absorption cross sections data \cite{guo2019optimized}. Enriched B$_4$C-90 has the highest macroscopic absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and finally Gd$_2$O$_3$. The absorber materials are consumed during burnup. The effect of burnup on absorption ability will be investigated specifically in the second part of this paper.

Additionally, the worth of the CSD clusters is by factor $1.56$ greater than the worth of the SSD system for all absorber materials. Both CSD and SSD clusters are separately able to shut down the reactor initially loaded by $^{233}$U and reactor-grade Pu regardless of the absorber material type. However, only SSD clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded by transuranic (TRU) elements. Increasing the number of SSD cluster or changing their location would increase their worth.

The inner ring of the CSD is located in the central zone of the SD-TMSR core (Figure~\ref{fig:core_25}), where the ratio between molten salt and graphite moderator is $0.357$. Results show that the inner ring of the CSD has the worth almost equal to the worth of all other CRs together regardless of the absorber material type (Table~\ref{tab:worth}). This may be attributed to the fact that the absorption cross section decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much greater than in fast spectrum.

In case of malfunction of the other CR clusters (e.g. stuck in the upper position), the outer ring of the CSD failures to counteract the excess reactivity of the core initially loaded by reactor-grade Pu and transuranic (TRU) elements. However, the worth of the outer ring of the CSD is sufficient to compensate the excess reactivity for the core with $^{233}$U refueled.

We separately calculate the worth of CSD2, CSD9, SSD1, and SSD4 clusters to investigate the variation of CRW with the position in the active core.
The CRW decreases in the direction of the peripheral zone. The peripheral zone has a high ratio between molten salt and graphite moderator about ($1.162$) compared with the central zone ($0.357$). As mentioned previously, the absorption ability decreases in fast spectrum.

\subsubsection{Shutdown Margin (SDM)}

The SSD clusters are designed mainly for an emergency shutdown, thus it should provide the reactor core with sufficient and adequate negative reactivity. The shutdown margin (SDM) is calculated by equation~\ref{Equ:6}. Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core initially loaded by $^{233}$U,  reactor-grade Pu, and transuranic (TRU) elements for different absorber materials.
All absorber materials provide an adequate shutdown margin for the SD-TMSR core that initially loaded by $^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters ineffective to shut down the reactor in these cases.

\begin{table}  %[!ht]
	\caption{The shutdown margins for the SD-TMSR core for different absorber materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{2cm}|s|s|s}
		\hline
		Absorber materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ &$1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.8\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.89\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\subsubsection{Interference between CR systems}

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The anti-shadowing is observed when the combined rod worth is greater than the sum of the individual worths. The strongest anti-shadowing effect has occurred in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
The obtained results emphasize the absence of the effect of the absorption material on the interference between the control rod clusters.

Insertion of the control rod affects the neutron flux distribution, which is the basic reason for the amplification of CR worths indicated in Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial neutron flux distribution at mid-core with different CRs position: (1) all CRs withdrawn (2) all CRs inserted (3) all CSD inserted (4) all SSD inserted. We chose the B$_4$C-90 as absorber materials because of its high absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions. This shifts the neutron flux from the core center towards the periphery. A maximum neutron flux shift occurs when all CRs are inserted into the core.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at mid-core with different CRs position: (1) all CRs withdrawn (2) all CRs inserted (3) all CSD inserted (4) all SSD inserted.} 
	\label{fig:totalflux}
\end{figure}

\subsubsection{Integral and differential CRW}

The integral and differential control rod worth are calculated for three different systems: all control rods, CSD, and SSD systems. The CRs are inserted gradually into the core from top to bottom. Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and differential CRW. Figure~\ref{fig:integ} illustrates the integral CRW for CRs made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD clusters are about $48.39$ , $25.3$, and $16.46$ \$, respectively. The integral worth of SSD clusters is sufficient to shut down the reactor from any state.

The differential CRWs are demonstrated in Figure~\ref{fig:diff}. Ideally, at the top of the core, the CR insertion has little effect since this region has low thermal neutron flux. Thus, the differential CRW has the lowest values in this region. The effect of CR insertion increases gradually near the center of the core. At the center of the core (region with maximum thermal neutron flux), the differential CRW is the largest and changes slowly with rod insertion. From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux). Figure~\ref{fig:diff} shows that the maximum differential CRW  is shifted toward the bottom of the core. This because (Need to find a reason(s)).

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five different absorber materials. The results show that all absorber materials have almost the same integral rod worth in the upper quarter of the core ($x$<$130$). Further insertion of the control rod clusters shows the unique absorption characteristics of each material see part \ref{CR_worth}. Enriched B$_4$C-90 absorbs neutrons much grater than the Gd$_2$O$_3$ that has the lowest absorption ability among the other absorber materials in this study. All result are based on steady state calculations. Further and detailed analysis including burnup calculation will be represented in the near future.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{integ.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:integ}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{diff.png}
	\vspace{-0.5in}
	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters.} 
	\label{fig:diff}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{CSD.png}
	\vspace{-0.5in}
	\caption{Integral control rod worth of CSD clusters for different absorber materials.} 
	\label{fig:CSD}
\end{figure}

### 2019-11-14 data/B4C_90/All except CSD 1 ring/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Aug  3 20:08:58 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Aug  3 20:18:44 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564852138668 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/All except CSD2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Aug  4 23:19:52 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Aug  4 23:28:57 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564949992539 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/All except DSD1/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Aug  4 14:20:52 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Aug  4 14:30:24 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564917652661 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/All except DSD4/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Aug  4 20:45:51 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Aug  4 20:55:24 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564940751658 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/CSD9/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Aug  5 00:50:40 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Aug  5 01:00:03 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564955440585 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/CSDring2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Aug  4 01:57:04 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Aug  4 02:06:51 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564873024678 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/DSD/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Aug  3 17:13:55 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Aug  3 17:23:44 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564841635618 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/All down/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Aug  5 03:25:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Aug  5 03:34:31 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1564964723478 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/All down/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Aug  5 15:12:08 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Aug  5 15:17:20 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565007128801 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/All down/0/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Aug  5 15:18:42 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Aug  5 15:23:54 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565007522321 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/All down/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Aug  5 15:27:49 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Aug  5 15:33:02 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565008069709 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/CSD/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 01:05:29 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 01:14:03 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565129129514 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/CSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 00:54:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 01:02:59 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565128463513 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/CSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 00:01:40 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 00:10:20 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565125300557 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/CSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 00:29:16 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 00:37:58 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565126956513 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/DSD/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 12:25:00 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 12:29:30 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565169900752 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/DSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 03:16:51 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 03:25:29 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565137011634 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/DSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 02:26:27 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 02:35:07 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565133987638 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/DSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 02:11:32 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 02:20:13 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565133092341 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/B4C_90/Different position/DSD/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Aug  7 02:00:11 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Aug  7 02:08:51 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1565132411613 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/All except CSD9/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 01:45:57 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 01:53:22 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573166757548 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/All except DSD1/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Nov  7 18:22:08 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Nov  7 18:30:07 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573140128952 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/CSD9/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 38])  = '/mnt/pool/4/osama.ashraf/work/testCR11' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 00:56:28 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 01:04:06 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573163788904 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/CSDring2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Nov  7 11:01:50 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Nov  7 11:13:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573113710489 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/DSD1/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 38])  = '/mnt/pool/4/osama.ashraf/work/testCR11' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Nov  7 15:22:32 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Nov  7 15:31:52 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573129352864 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/DSD4/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR6' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Nov  7 19:31:52 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Nov  7 19:40:13 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573144312926 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/All down/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 17:55:17 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 18:00:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573224917023 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/All down/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 18:54:07 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 18:59:02 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573228447992 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/All down/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 17:42:13 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 17:47:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573224133994 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/All down/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 18:37:51 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 18:43:01 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573227471973 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/All down/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 11:49:30 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 12:04:12 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573202970895 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/CSD/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 21:55:07 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 22:00:09 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573239307961 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/CSD/-156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 22:36:05 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 22:41:09 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573241765031 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/CSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 21:17:58 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 21:27:49 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573237078672 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/CSD/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  9 01:12:46 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  9 01:24:26 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573251166830 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/CSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  8 19:29:59 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  8 19:36:09 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573230599945 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/DSD/-260/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  9 09:32:46 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  9 09:37:39 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573281166998 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/DSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  9 09:05:10 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  9 09:10:15 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573279510993 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/Different position/DSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  9 01:53:28 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  9 01:58:34 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573253608076 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Eu2O3/with25CRALLDOWN50000/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 20:52:19 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 21:00:52 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573062739569 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/CSD/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 10:55:20 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 11:00:36 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572940520775 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/CSD2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 00:09:07 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 00:17:51 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572988147147 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/CSD9/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR6' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 01:56:35 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 02:05:17 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572994595742 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/DSD/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 11:35:26 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 11:40:43 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572942926779 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/DSD4/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 16:36:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 16:41:39 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572960983798 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/All down/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR5' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 11:01:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 11:10:10 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573027283722 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/All down/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR8' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 12:01:32 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 12:10:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573030892521 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/CSD/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR5' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 15:39:13 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 15:48:02 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573043953707 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/CSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR3' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 15:30:16 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 15:39:02 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573043416806 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/CSD/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR8' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 15:57:14 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 16:06:02 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573045034939 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/CSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 16:24:55 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 16:33:49 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573046695219 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/DSD/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR9' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 18:30:33 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 18:39:27 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573054233059 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/DSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR3' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 18:48:30 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 18:57:20 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573055310153 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/DSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 17:55:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 18:04:11 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573052123972 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/Different position/DSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n07.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Wed Nov  6 17:46:25 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Wed Nov  6 17:55:13 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1573051585721 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/Gd2O3/with25CRALLDOWN50000/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n112.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 02:13:03 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 02:31:10 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572909183906 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/All except CSD 1 ring/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Oct 31 18:09:29 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Oct 31 18:14:01 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572534569915 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/All except CSD 2 ring/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Oct 31 19:01:22 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Oct 31 19:05:51 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572537682776 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/All except CSD2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n112.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  1 00:53:16 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  1 01:07:50 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572558796045 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/All except CSD9/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  1 01:53:09 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  1 02:01:41 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572562389528 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/All except DSD4/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Oct 31 23:03:02 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Oct 31 23:07:29 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572552182789 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/CSD2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Fri Nov  1 00:13:44 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Fri Nov  1 00:18:16 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572556424828 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/CSDring2/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 30])  = 'n14.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Oct 31 19:29:25 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Oct 31 19:33:58 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572539365595 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/All down/0/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 02:08:23 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 02:22:34 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572649703076 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/All down/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 30])  = 'n06.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 02:51:22 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 02:56:46 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572652282843 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/-156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 23:13:19 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 23:20:56 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572725599024 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 23:22:48 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 23:30:08 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572726168076 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR3' ;
+HOSTNAME                  (idx, [1: 30])  = 'n06.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 12:52:37 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 12:58:36 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572688357276 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/0/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 12:30:09 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 12:39:22 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572687009981 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 13:44:32 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 13:54:03 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572691472994 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 14:08:13 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 14:17:36 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572692893026 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/CSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n06.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sat Nov  2 12:30:43 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sat Nov  2 12:36:39 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572687043843 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 01:17:45 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 01:25:22 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572733065644 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/-208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR5' ;
+HOSTNAME                  (idx, [1: 23])  = 'n119.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 02:28:30 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 02:42:58 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572737310686 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/-260/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 11:29:18 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 11:36:21 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572769758698 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 00:11:33 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 00:45:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572729093520 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n08.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 01:15:59 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 01:48:01 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572732959521 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 01:58:39 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 02:09:19 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572735519325 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 02:15:41 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 02:26:17 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572736541050 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/Different position/DSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 00:41:58 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 00:56:30 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572730918531 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-14 data/HfB2/with25CRALLDOWN50000/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n06.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Thu Oct 31 13:34:18 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Thu Oct 31 13:40:16 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572518059001 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/All except CSD 1 ring/TMSR_res.m
HfH1_62 data

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n113.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 12:39:11 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 12:53:08 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572860351932 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/CSD/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 14:36:57 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 14:44:16 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572781017655 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/DSD/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 15:51:19 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 15:59:12 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572785479036 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/DSD1/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n109.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 16:23:15 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 16:38:18 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572873795804 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/All down/-156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR7' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 21:55:22 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 22:00:47 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572893722804 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/All down/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR3' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 22:23:08 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 22:28:34 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572895388779 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/All down/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR6' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 21:49:43 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 21:55:11 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572893383614 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/All down/208/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR8' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 22:00:59 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 22:06:27 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572894059425 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/All down/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 21:32:51 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 21:38:17 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572892371593 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/CSD/-104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR5' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 23:30:42 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 23:36:08 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572899442708 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/CSD/-260/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 38])  = '/mnt/pool/4/osama.ashraf/work/testCR10' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 23:58:49 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:04:25 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572901129238 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/CSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Mon Nov  4 23:25:04 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Mon Nov  4 23:30:31 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572899104819 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/-156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR7' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 00:30:01 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:35:29 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572903001682 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/-260/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 38])  = '/mnt/pool/4/osama.ashraf/work/testCR10' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 00:41:19 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:46:56 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572903679471 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/-52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR3' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 00:52:45 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:58:10 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572904365011 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/104/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR4' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 00:13:05 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:18:32 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572901985655 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/156/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR6' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 00:24:21 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 00:29:50 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572902661826 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/Different position/DSD/52/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR2' ;
+HOSTNAME                  (idx, [1: 30])  = 'n13.unicluster.campus.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 47])  = 'Intel(R) Xeon(R) CPU           E5450  @ 3.00GHz' ;
+CPU_MHZ                   (idx, 1)        = 2571.0 ;
+START_DATE                (idx, [1: 24])  = 'Tue Nov  5 01:08:17 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Tue Nov  5 01:13:44 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572905297752 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 data/HfH1_62/with25CRALLDOWN50000/TMSR_res.m

@@ -1,0 +1,328 @@
+
+% Increase counter:
+
+if (exist('idx', 'var'));
+  idx = idx + 1;
+else;
+  idx = 1;
+end;
+
+% Version, title and date:
+
+VERSION                   (idx, [1: 14])  = 'Serpent 2.1.31' ;
+COMPILE_DATE              (idx, [1: 20])  = 'Jan  1 1970 00:00:00' ;
+DEBUG                     (idx, 1)        = 0 ;
+TITLE                     (idx, [1:  7])  = 'SD-TMSR' ;
+CONFIDENTIAL_DATA         (idx, 1)        = 0 ;
+INPUT_FILE_NAME           (idx, [1:  4])  = 'TMSR' ;
+WORKING_DIRECTORY         (idx, [1: 37])  = '/mnt/pool/4/osama.ashraf/work/testCR1' ;
+HOSTNAME                  (idx, [1: 23])  = 'n121.basov.hpc.mephi.ru' ;
+CPU_TYPE                  (idx, [1: 40])  = 'Intel(R) Xeon(R) CPU E5-2680 0 @ 2.70GHz' ;
+CPU_MHZ                   (idx, 1)        = 1808.0 ;
+START_DATE                (idx, [1: 24])  = 'Sun Nov  3 13:07:26 2019' ;
+COMPLETE_DATE             (idx, [1: 24])  = 'Sun Nov  3 13:14:52 2019' ;
+
+% Run parameters:
+
+POP                       (idx, 1)        = 50000 ;
+CYCLES                    (idx, 1)        = 500 ;
+SKIP                      (idx, 1)        = 50 ;
+BATCH_INTERVAL            (idx, 1)        = 1 ;
+SRC_NORM_MODE             (idx, 1)        = 2 ;
+SEED                      (idx, 1)        = 1572775646094 ;
+UFS_MODE                  (idx, 1)        = 0 ;
+UFS_ORDER                 (idx, 1)        = 1.00000;
+NEUTRON_TRANSPORT_MODE    (idx, 1)        = 1 ;
+PHOTON_TRANSPORT_MODE     (idx, 1)        = 0 ;
+GROUP_CONSTANT_GENERATION (idx, 1)        = 0 ;
+B1_CALCULATION            (idx, [1:  3])  = [ 0 0 0 ];
[…]

### 2019-11-15 paper/acros.tex

\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{TRU}{TRU}{transuranic elements}
\newacronym{LEU}{LEU}{low-enriched uranium}
\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{ANS}{ANS}{American Nuclear Society}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{BR}{BR}{Breeding Ratio}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CAS}{CAS}{Chinese Academy of Sciences} 
\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDF}{EDF}{Électricité de France}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EFPY}{EFPY}{effective full-power years}
\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EPR}{EPR}{European Pressurized Reactors}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{EU}{EU}{European Union}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{FP}{FP}{Fission Product}
\newacronym{FTC}{FTC}{Fuel Temperature Coefficient}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GIF}{GIF}{Generation IV International Forum}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{IHX}{IHX}{Intermediate Heat Exchanger}
\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
\newacronym{IRP}{IRP}{Integrated Research Project}
\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
\newacronym{ISRG}{ISRG}{Independent Student Research Group}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOSART}{MOSART}{MOlten Salt Actinide Recycler and Transmuter}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MPI}{MPI}{Message Passing Interface}
\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{MTC}{MTC}{Moderator Temperature Coefficient}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NPP}{NPP}{Nuclear Power Plant}
\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWF}{NWF}{Nuclear Waste Fund}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PRIS}{PRIS}{Power Reactor Information System}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PWR}{PWR}{Pressurized Water Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{REE}{REE}{rare earth element}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{ROD}{ROD}{Reactor Optimum Design}
\newacronym{SD-TMSR}{SD-TMSR}{Single-fluid Double-zone Thorium-based Molten Salt Reactor}	
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}
\newacronym{CNRS}{CNRS}{National Center for Scientific Research}		
\newacronym{CRAM}{CRAM}{Chebyshev Rational Approximation Method}
\newacronym{DT}{DT}{Doubling Time}		
\newacronym{Euratom}{Euratom}{European Atomic Energy Community}
\newacronym{FPs}{FPs}{fission products} 
\newacronym{HM}{HM}{heavy metal}
\newacronym{MAs}{MAs}{Minor Actinides}
\newacronym{OpenMP}{OpenMP}{Open Multi-Processing}
\newacronym{TCR}{TCR}{Temperature Coefficient of Reactivity}
\newacronym{3D}{3D}{Three Dimensions}			
\newacronym{TS-MSR}{TS-MSR}{Thermal-Spectrum Molten Salt Reactor}
\newacronym{FS-MSR}{FS-MSR}{Fast-Spectrum Molten Salt Reactor}
\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}
\newacronym{TMSR}{TMSR}{Thorium-based Molten Salt Reactor}

### 2019-11-15 paper/discussion.tex

\section{Discussion}
% This should explore the significance of the results of the work, not repeat
% them. A combined Results and Discussion section is often appropriate. Avoid
% extensive citations and discussion of published literature.
Short 2-3 paragraph discussion. This will emphasize:
\begin{itemize}
  \item Discuss reason of spectral shift (heavy \gls{FP} accumulation, Pu isotopes).
  \item Neutron spectral shift which causes safety parameters worsening.  
  \item Couple words about power profile.
\end{itemize}

### 2019-11-28 paper/acks.tex
Abstract and conclusion added

@@
 Prof.
-Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the NNSA Office of Defense Nuclear Nonproliferation R\&D through the Consortium for Verification Technologies and the Consortium for Nonproliferation Enabling Capabilities,  the International Institute for Carbon Neutral Energy Research (WPI-I2CNER),
+Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER),
 sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2019-11-28 paper/methods.tex
Abstract and conclusion added

@@
 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
-\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2250 MW$_{th}$. The 
+\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2,250 MW$_{th}$. The 
 design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
 \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential} after modifying the geometry to 
-control the positive temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
-geometry is described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
+control the positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
+geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
 \cite{li_optimization_2018,ashraf2019whole_core}.
@@
 
-In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (i.e.
-$^{232}$Th and fissile materials).
-Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} LWR \gls{SNF} \cite{de2000scenarios}.
+In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e.
+$^{232}$Th and fissile materials), and $N$ is dependent on the chosen fissile material and the thermochemical state of the liquid fuel salt.
+Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
 The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, respectively.
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{l | l}
+	\begin{tabularx}{\textwidth}{l | r}
 		\hline
 		Thermal power, MW$_{th}$          				&  2,250  \\ 
-		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
+		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
 		Fuel composition, mole\%                        & 70-17.5-12.5    \\
@@
 
-Since the total quantity and distribution of the SD-TMSR control assemblies are unknown, we proposed an original distribution as a starting point of this analysis.
+Since the total quantity and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis.
 We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
 Every four control rods (cluster) can move together as one group.
-Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the four control rods.
+Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
 The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.
@@
 In this case, the control rods are located above the upper plenum as shown in Figure~\ref{fig:core_26}.
-To validate the proposed control rods system we adopted the same operation conditions (as in the initial case) and changed the position of the control rod clusters along $Z$ direction.
+To validate the proposed control rods system we adopted the same operation conditions (as in the initial calculation state) and changed the position of the control rod clusters along $Z$ direction.
 The main calculated parameters including reactivity, control rod worth, and interference effects (shadowing effects) will describe in the following parts.
@@
 The control rod worth (CRW) is the amount of negative reactivity that associated with the control rod insertion.
-The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after i$^{th}$ CR insertion \cite{vcerba2017optimization}.
+The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion i$^{th}$ CR \cite{vcerba2017optimization}.
 

### 2019-11-28 paper/conclusion.tex

@@
 \section{Conclusion} \label{Conclusion}
+The full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is loaded by three different types of initial fissile materials: $^{233}$U, reactor-grade Pu, and transuranic (TRU) elements from \gls{LWR} \gls{SNF}.
+The excess reactivity $\rho$$_e$ is calculated at zero burnup when all CRs are fully withdrawn.
+The excess reactivities for $^{233}$U, reactor-grade Pu, and TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
+
+Five different absorber materials are considered based on their neutronics and safety performance: B$_4$C-90, HfB$_2$, HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$.
+Enriched B$_4$C-90 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with the other absorber materials in this study.
+Both CSD and SSD clusters are separately able to shut down the reactor initially loaded by $^{233}$U and reactor-grade Pu regardless of the absorber material type.
+However, only SSD clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded by transuranic (TRU) elements.
+
+In case of malfunction of the other CR clusters (e.g.
+stuck in the upper position), the outer ring of the CSD failures to counteract the excess reactivity of the core initially loaded by reactor-grade Pu and transuranic (TRU) elements.
+However, the worth of the outer ring of the CSD is sufficient to compensate the excess reactivity for the core refueled by $^{233}$U.
+
+All absorber materials provide an adequate shutdown margin for the SD-TMSR core that initially loaded by $^{233}$U and reactor-grade Pu.
+However, the shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters ineffective to shut down the reactor loaded by TRU.
+
+The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects.
+The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio.
+
+The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions. This shifts the neutron flux from the core center towards the periphery.
+
+The integral and differential control rod worth are calculated for three different systems: all control rods, CSD, and SSD systems.
+The results show that all absorber materials have almost the same integral rod worth in the upper quarter of the core ($x$$<$$130$).
+Further insertion of the control rods shows the unique absorption characteristics of each material.
 
 \section{Future work}
+The effect of burnup on the absorption ability of control rods will be investigated specifically in the second part of this paper. Additionally, .......
 

### 2019-11-28 paper/introduction.tex

@@
 The unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, etc.) strongly affect its control system design.
-The MSRs have a negative temperature coefficient of reactivity.
+Graphite-moderated MSRs have a negative temperature coefficient of reactivity \cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when the core heats up.
@@
 The graphite expansion is not a dominating factor, thus core reactivity will decrease automatically when the core heats up \cite{li_optimization_2018}.
-The MSR designs have a drain tank to collect the liquid fuel in an emergency case.
+MSR designs have a drain tank(s) to collect the liquid fuel in an emergency case.
 A freeze plug, which located under the core, melts when the temperature reaches a critical point.
-Then the fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}
+Then the fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.
 
@@
 \item The drain tanks, which have subcritical geometry and passively cooled.
-\item The control rods compensate the excess reactivity, temperature regulation, and/or shut down the reactor.
+\item The control rods compensate the excess reactivity, regulate temperature, and/or shut down the reactor.
 \item The continuous removing of fission products and radioactive gasses minimize the chance of radiation exposure.
-\item The reactor system chamber.
 \item The outer containment vessel.
@@
 boron and cadmium) \cite{duderstadt650nuclear}.
-The control rods introduce an amount of negative reactivity into the core.
+Insertion of control rods introduces an amount of negative reactivity into the core.
 This negative reactivity helps to compensate the excess reactivity and adjust the power level of the core or even shut down the reactor in an emergency situation \cite{glasstone1967nuclear}.
@@
 Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the potential alternative absorbers in Generation-IV reactors such as hafnium-based materials and rare earth element oxides.
-These absorbers have high thermal conductivity, good resistance to neutron irradiation, and release no gas \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
+These absorbers have high thermal conductivity, good resistance to neutron irradiation, and release almost no gas \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
 
-The \gls{SD-TMSR} with a thermal power of 2250 MW$_{th}$ \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated molten salt reactor.
-Recent studies on MSRs show that the excess reactivity at the beginning of the operation is quite large for many fueling scenarios \cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
+The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated molten salt reactor.
+Recent studies on MSRs show that the excess reactivity at the beginning of the operation is quite large for many refueling scenarios \cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
 Adjusting fertile and fissile feed rates helps to control the reactivity of the SD-TMSR \cite{ashraf2019whole_core}.

### 2019-11-28 paper/results.tex

@@
 For $^{233}$U case, the maximum excess reactivity $\rho$$_e$ is about $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of reactor operation (see Figure~\ref{fig:keff_25}).
-The SD-TMSR is able to control the reactivity by adjusting the online refueling and reprocessing rates.
+The SD-TMSR is able to control the reactivity by adjusting the online refueling and reprocessing rates \cite{ashraf2019whole_core}.
 An effective and reliable reactivity control system must be designed beside the online feed system to operate with such reactivity changes during burnup.
@@
 The absorber materials are consumed during burnup.
-The effect of burnup on absorption ability will be investigated specifically in the second part of this paper.
+The effect of burnup on the absorption ability will be investigated specifically in the second part of this paper.
 
@@
 stuck in the upper position), the outer ring of the CSD failures to counteract the excess reactivity of the core initially loaded by reactor-grade Pu and transuranic (TRU) elements.
-However, the worth of the outer ring of the CSD is sufficient to compensate the excess reactivity for the core with $^{233}$U refueled.
+However, the worth of the outer ring of the CSD is sufficient to compensate the excess reactivity for the core refueled by $^{233}$U .
 
@@
 All absorber materials provide an adequate shutdown margin for the SD-TMSR core that initially loaded by $^{233}$U and reactor-grade Pu.
-However, the shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters ineffective to shut down the reactor in these cases.
+However, the shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters ineffective to shut down the reactor loaded by TRU.
 
@@
 Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five different absorber materials.
-The results show that all absorber materials have almost the same integral rod worth in the upper quarter of the core ($x$<$130$).
-Further insertion of the control rod clusters shows the unique absorption characteristics of each material see part \ref{CR_worth}.
+The results show that all absorber materials have almost the same integral rod worth in the upper quarter of the core ($x$$<$$130$).
+Further insertion of the control rods shows the unique absorption characteristics of each material see part \ref{CR_worth}.
 Enriched B$_4$C-90 absorbs neutrons much grater than the Gd$_2$O$_3$ that has the lowest absorption ability among the other absorber materials in this study.

### 2019-12-16 paper/introduction.tex
Intro startes

@@
 
-The \gls{GIF} \cite{doe2002technology} determined six innovative reactor systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR).
-The MSR is the only liquid-fueled reactor among these reactors.
-Major nuclear centers pursue MSRs with renewed interest \cite{betzler_impacts_2019,ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
-The MSR is a promising technology because of its dynamics, especially for thorium fuel utilization.
-However, this technology has challenges in safety, online reprocessing, and fuel handling.
-Safety is one of the technological goals of the MSR systems that require further research and investigation.
-The unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, etc.) strongly affect its control system design.
-Graphite-moderated MSRs have a negative temperature coefficient of reactivity \cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
-Doppler effect and thermal expansion of the fuel reduce core reactivity when the core heats up.
-However, graphite thermal expansion positively affect the core reactivity \cite{mathieu2006thorium}.
-The graphite expansion is not a dominating factor, thus core reactivity will decrease automatically when the core heats up \cite{li_optimization_2018}.
-MSR designs have a drain tank(s) to collect the liquid fuel in an emergency case.
-A freeze plug, which located under the core, melts when the temperature reaches a critical point.
-Then the fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.
+The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
+systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
+Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
+the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
+The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
+centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
+ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
+ The MSR is a promising technology because of its dynamics, especially for 
+thorium fuel utilization. However, this technology has difficulties in safety, 
+online reprocessing, and fuel handling. Safety is one of the primary goals of 
+the MSR systems, which was understudied and require further investigation. The 
+unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
+etc.) strongly affect its control system design. Graphite-moderated MSRs have a 
+negative total temperature coefficient of reactivity 
+\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
+ Doppler effect and thermal expansion of the fuel reduce core reactivity when 
+the core heats up. However, graphite thermal expansion positively affect the 
+core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a 
+dominating factor, thus core reactivity will decrease automatically when the 
+core heats up \cite{li_optimization_2018}. MSR designs have a drain tank(s) to 
+collect the liquid fuel in an emergency case. A freeze plug, which located 
+under the core, melts when the temperature reaches a critical point. Then the 
+fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.
 

### 2019-12-16 paper/introduction.tex
Introduction edited

@@
 unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
-etc.) strongly affect its control system design. Graphite-moderated MSRs have a 
-negative total temperature coefficient of reactivity 
+etc.) strongly affect its control system design. Graphite-moderated MSRs have 
+a negative total temperature coefficient of reactivity 
 \cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
  Doppler effect and thermal expansion of the fuel reduce core reactivity when 
-the core heats up. However, graphite thermal expansion positively affect the 
-core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a 
+the core heats up. However, temperature coefficient of reactivity for graphite 
+is small but positive due to Doppler effect \cite{mathieu2006thorium, 
+rykhlevskii_full-core_2017}. The graphite expansion is not a 
 dominating factor, thus core reactivity will decrease automatically when the 
-core heats up \cite{li_optimization_2018}. MSR designs have a drain tank(s) to 
-collect the liquid fuel in an emergency case. A freeze plug, which located 
-under the core, melts when the temperature reaches a critical point. Then the 
-fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.
+core heats up \cite{li_optimization_2018}. MSR designs have a drain tanks to 
+hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
+located under the core, passively melts when the fuel temperature reaches a 
+critical point, and drains the fuel salt from the reactor vessel to the drain 
+tanks. The drain tanks have a subcritical
+configuration with a large free 
+surface area to readily dissipate heat by passive cooling 
+\cite{elsheikh2013safety}.
 
-Safety aspects in the MSRs can be listed as follows \cite{elsheikh2013safety,merle2008optimization}:
+Safety aspects in the MSRs can be listed as follows 
+\cite{elsheikh2013safety,merle2008optimization}:
 \begin{enumerate}
@@
 
-At the Beginning of Life (BOL), we must load the MSR with larger amount of fuel than that required to achieve criticality (necessary for long term core operation).
-This leads to excess reactivity at the BOL \cite{duderstadt650nuclear}.
-Additionally, during burnup, the online reprocessing and refueling leads to change the reactivity of the MSRs \cite{ashraf2019whole_core}.
-The most common procedure for reactor control is to insert or withdraw control rods with large neutron absorption cross section (e.g.
-boron and cadmium) \cite{duderstadt650nuclear}.
-Insertion of control rods introduces an amount of negative reactivity into the core.
-This negative reactivity helps to compensate the excess reactivity and adjust the power level of the core or even shut down the reactor in an emergency situation \cite{glasstone1967nuclear}.
-Therefore, we should estimate the reactivity worth of the control rods \cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
-The reactivity worth of control rods correlates with the interference (shadowing effects) between control rod clusters.
+At the Beginning of Life (BOL), we must load the MSR with larger amount of 
+fuel than that required to achieve criticality (necessary for long term core 
+operation). This leads to excess reactivity at the BOL 
+\cite{duderstadt650nuclear}. Additionally, during burnup, the online 
+reprocessing and refueling leads to slow reactivity change, which 
+should be compensated \cite{ashraf2019whole_core}. The most common procedure 
+for reactor control is to insert or withdraw control rods made of material 
+with large neutron absorption cross section (e.g., boron, cadmium) 
+\cite{duderstadt650nuclear}. 
+Insertion of control rods introduces an amount of negative reactivity into the 
+core. This negative reactivity helps to compensate the excess reactivity and 
+adjust the power level of the core or shut down the reactor in case of  
+emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
+the reactivity worth of the control rods 
+\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
+ The reactivity worth of control rods correlates with the interference 
+(shadowing effects) between control rod clusters 
 \cite{girardin2008development,vcerba2017optimization}. 
@@
 
-Boron carbide (B$_4$C) is used in control rods \cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}.
-However, we may need to enrich the effective boron isotope ($^{10}$B) to reach the necessary absorptivity.
-Notably, the spatial self-shielding effect correlates with $^{10}$B concentration.
-For example, B$_4$C enriched to 90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its absorption ability is about 2.3 times compared with natural B$_4$C.
-Additionally, issues related to helium gas release, swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C lifespan \cite{guo2019optimized}.
+Boron carbide (B$_4$C) is commonly used material for the control rods 
+\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
+However, we may need to enrich the boron isotope ($^{10}$B) to reach 
+the necessary absorption cross section. Notably, the spatial self-shielding 
+effect correlates with $^{10}$B concentration. For example, B$_4$C enriched to 
+90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its 
+absorption ability is about 2.3 times compared with natural B$_4$C. 
+Additionally, issues related to helium gas release, swelling, melting risk, 
+and high loss of the reactivity worth limit the B$_4$C lifespan 
+\cite{guo2019optimized}.
 
-Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the potential alternative absorbers in Generation-IV reactors such as hafnium-based materials and rare earth element oxides.
-These absorbers have high thermal conductivity, good resistance to neutron irradiation, and release almost no gas \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
+Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
+potential alternative absorbers for Generation-IV reactors such as 
+hafnium-based materials and rare earth element oxides. These absorbers have 
+high thermal conductivity, good resistance to neutron irradiation, and release 
+almost no gas 
+\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
 
-The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated molten salt reactor.
-Recent studies on MSRs show that the excess reactivity at the beginning of the operation is quite large for many refueling scenarios \cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
-Adjusting fertile and fissile feed rates helps to control the reactivity of the SD-TMSR \cite{ashraf2019whole_core}.
-However, we should introduce a reliable safety system beside the online feed system to control the excess reactivity.
-Therefore, the main objective of our study is to introduce a new safety system based on control rods in the \gls{SD-TMSR} to control the reactivity during normal operation.
-Five different absorber materials are applied to study the main neutronics and safety parameters in the SD-TMSR.
-We focus on the control rod design, absorption ability, integral and differential control rod worths, shutdown margin of absorber materials, and shadowing effects at steady state calculation.
+The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
+\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
+molten salt reactor. Recent studies on MSRs showed that the excess reactivity 
+at the beginning of the operation is quite large for many refueling scenarios 
+\cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
+ Adjusting fertile and fissile feed rates helps to control the reactivity of 
+the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a 
+reliable safety system beside the online feed system to control the excess 
+reactivity. Therefore, the main objective of our study is to introduce a new 
+fast reactivity control based on control rods in the \gls{SD-TMSR} to control 
+the reactivity during normal operation. Five different absorber materials are 
+applied to study the main neutronics and safety parameters in the SD-TMSR. We 
+focus on the control rod design, absorption ability, integral and differential 
+control rod worths, shutdown margin of absorber materials, and shadowing 
+effects at steady state calculation.
 
-\v{C}erba \emph{et al.} (2017) designed a reactivity control system in the GFR.
-They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes \cite{petrie1984keno} to calculate the reactivity worth and analyze the performance of this control system \cite{vcerba2017optimization}.
-Since no final geometry design of the control rods system is available for the SD-TMSR, \v{C}erba's methodology \cite{vcerba2017optimization}  helped us as a starting point of this analysis.
+\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
+GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes 
+\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
+performance of this control system \cite{vcerba2017optimization}. Since no 
+final geometry design of the control rods system is available for the SD-TMSR, 
+\v{C}erba's methodology \cite{vcerba2017optimization}  helped us as a starting 
+point of this analysis.
 

### 2019-12-16 paper/results.tex
Results changed

@@
 
-The full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is loaded by three different types of initial fissile materials: $^{233}$U, reactor-grade Pu, and transuranic (TRU) elements from \gls{LWR} \gls{SNF}.
-The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state calculation), when all CRs are fully withdrawn.
-The excess reactivities for $^{233}$U, reactor-grade Pu, and TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
-For $^{233}$U case, the maximum excess reactivity $\rho$$_e$ is about $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of reactor operation (see Figure~\ref{fig:keff_25}).
-The SD-TMSR is able to control the reactivity by adjusting the online refueling and reprocessing rates \cite{ashraf2019whole_core}.
-An effective and reliable reactivity control system must be designed beside the online feed system to operate with such reactivity changes during burnup.
+The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
+calculation), when all CRs are fully withdrawn. $\rho_e$ for $^{233}$U, 
+reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
+$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively. For $^{233}$U 
+case, the maximum excess reactivity $\rho$$_e$ is about $4.27\pm0.01$ $\$$ 
+during 60 effective full-power years (EFPY) of reactor operation (see 
+Figure~\ref{fig:keff_25}). 
+The SD-TMSR is able to control the reactivity by adjusting the online 
+refueling and reprocessing rates \cite{ashraf2019whole_core}. An effective and 
+reliable reactivity control system must be designed beside the online feed 
+system to operate with such reactivity changes during burnup.
 
@@
 
-The control rod parameters including control rod worth (CRW), interference between CR clusters, and integral and differential control rod worths are described in this part.
-Five different absorber materials are considered based on their neutronics and safety performance (see part \ref{CRD}).
-The results of the control rod worth, the amplification factor (A$_{CRi}$), and the type of interference for the five absorber materials are listed in Table~\ref{tab:worth}.
+The control rod parameters including control rod worth (CRW), interference 
+between CR clusters, and integral and differential control rod worths are 
+described in this part. Five different absorber materials are considered based 
+on their neutronics and safety performance (see part \ref{CRD}). 
+Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
+factor (A$_{CRi}$), and the type of interference for five different 
+absorbers.
 
 \begin{sidewaystable}
-	\tiny
+	\fontsize{6}{9}\selectfont
 	\centering
-	\caption{The control rod worths and shadowing effects for different CR materials.}
+	\caption{The control rod worth and shadowing effect for different CR 
+	materials.}
 	\vspace{1ex}
-	\begin{tabularx}{\textwidth}{|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.8cm}|p{0.6cm}|}
+	\begin{tabularx}{\textwidth}{|X|p{0.65cm}|p{0.65cm}|p{0.65cm}| 
+	p{0.65cm}|p{0.65cm}|p{0.65cm}| p{0.65cm}|p{0.65cm}|p{0.65cm}| 
+	p{0.65cm}|p{0.65cm}|p{0.65cm}| p{0.65cm}|p{0.65cm}|p{0.65cm}|}
 		\hline
-		\multirow{2}{4em}{CR clusters}		& \multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	&\multicolumn{3}{c|}{HfH$_{1.62}$} &\multicolumn{3}{c|}{Gd$_2$O$_3$}	& 	\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
+		\multirow{2}{*}{Control Rod group}		& 
+		\multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	
+		&\multicolumn{3}{c|}{HfH$_{1.62}$} 
+		&\multicolumn{3}{c|}{Gd$_2$O$_3$}	& 	
+		\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
 		\cline{2-16}
-		&  $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Interference	&$\Delta\rho$$_{CRi}$ [\$]&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	&Interference	&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$ &	Interference \\
+		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Interfe\-rence	
+		&$\Delta\rho$$_{CRi}$ [\$]&A$_{CRi}$	& Interfe\-rence	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Interfe\-rence	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Interfe\-rence	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  &	Interfe\-rence \\
 		\hline                   
-		ALL CRs        				& $48.19\pm0.68$   &	&	&$40.4\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.7\pm0.4$	&	&	&$42.39\pm0.48$	& &	 \\
+		All control rods        				& $48.19\pm0.68$   &	&	
+		&$40.4\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.7\pm0.4$	&	
+		&	&$42.39\pm0.48$	& &	 \\
 		\hline 
@@
 		\tiny
-		\item  $\star$  means anti-shadowing effects.
-		\item  $\star$$\star$ means strong anti-shadowing effects.
+		\item  $\star$  anti-shadowing effects observed
+		\item  $\star$$\star$ strong anti-shadowing effects observed
 	\end{tablenotes}
@@
 
-The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ \$ (Table~\ref{tab:worth}).
-Enriched B$_4$C-90 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with the other absorber materials in this study.
-This result agrees with macroscopic absorption cross sections data \cite{guo2019optimized}.
-Enriched B$_4$C-90 has the highest macroscopic absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and finally Gd$_2$O$_3$.
-The absorber materials are consumed during burnup.
-The effect of burnup on the absorption ability will be investigated specifically in the second part of this paper.
+The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ 
+\$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
+has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
+absorption compared with the other absorber materials in this study. This 
+result agrees with macroscopic absorption cross sections data 
+\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
+absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
+finally Gd$_2$O$_3$. The control rod material are being transmuted during 
+operation. The effect of the fuel salt burnup on the control rod worth is not 
+considered herein, and will be investigated and presented in Part II of this 
+study.
 
-Additionally, the worth of the CSD clusters is by factor $1.56$ greater than the worth of the SSD system for all absorber materials.
-Both CSD and SSD clusters are separately able to shut down the reactor initially loaded by $^{233}$U and reactor-grade Pu regardless of the absorber material type.
-However, only SSD clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded by transuranic (TRU) elements.
-Increasing the number of SSD cluster or changing their location would increase their worth.
+Additionally, the worth of the CSD clusters is by factor $1.56$ greater than 
+the worth of the SSD system for all absorber materials. Either CSD or SSD 
+clusters are able to shut down the reactor initially loaded by 
+$^{233}$U and reactor-grade Pu regardless of the absorber material type. 
+However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
+initially loaded with transuranic (TRU) elements. Increasing the number of SSD 
+cluster or changing their location would increase the worth.
 
-The inner ring of the CSD is located in the central zone of the SD-TMSR core (Figure~\ref{fig:core_25}), where the ratio between molten salt and graphite moderator is $0.357$.
-Results show that the inner ring of the CSD has the worth almost equal to the worth of all other CRs together regardless of the absorber material type (Table~\ref{tab:worth}).
-This may be attributed to the fact that the absorption cross section decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much greater than in fast spectrum.
+The inner ring of the CSD is located in the central zone of the SD-TMSR core 
+(Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
+graphite is $0.357$. Results show that the inner ring of the CSD has 
+the worth almost equal to the worth of all other CRs together regardless of 
+the absorber material type (Table~\ref{tab:worth}). This may be attributed to 
+the fact that the absorption cross section decreases with the energy of 
+incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
+greater than in fast spectrum.
 
-In case of malfunction of the other CR clusters (e.g.
-stuck in the upper position), the outer ring of the CSD failures to counteract the excess reactivity of the core initially loaded by reactor-grade Pu and transuranic (TRU) elements.
-However, the worth of the outer ring of the CSD is sufficient to compensate the excess reactivity for the core refueled by $^{233}$U .
+In case of malfunction of other CR clusters (e.g., stuck in the upper 
+position), the outer ring of the CSD cannot compensate the excess 
+reactivity of the core initially loaded by reactor-grade Pu and transuranic 
+(TRU) elements. However, the outer ring of the CSD worth is sufficient 
+to compensate the excess reactivity for the core refueled by $^{233}$U .
 
-We separately calculate the worth of CSD2, CSD9, SSD1, and SSD4 clusters to investigate the variation of CRW with the position in the active core.
-The CRW decreases in the direction of the peripheral zone.
-The peripheral zone has a high ratio between molten salt and graphite moderator about ($1.162$) compared with the central zone ($0.357$).
-As mentioned previously, the absorption ability decreases in fast spectrum.
+We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters to 
+investigate the variation of CRW with the position in the active core.
+The CRW decreases in the direction of the outer core zone. The outer core zone 
+has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
+($2.8$), consequently, the neutron energy spectrum is faster in the peripheral 
+zone than in the center of the core. As mentioned previously, the CRs 
+absorption ability degrades in fast spectrum.
 
@@
 
-The SSD clusters are designed mainly for an emergency shutdown, thus it should provide the reactor core with sufficient and adequate negative reactivity.
-The shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
-Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core initially loaded by $^{233}$U,  reactor-grade Pu, and transuranic (TRU) elements for different absorber materials.
-All absorber materials provide an adequate shutdown margin for the SD-TMSR core that initially loaded by $^{233}$U and reactor-grade Pu.
-However, the shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters ineffective to shut down the reactor loaded by TRU.
-
-\begin{table}  %[!ht]
+The SSD clusters are designed mainly for an emergency shutdown, thus it should 
+provide the reactor core with sufficient and adequate negative reactivity. The 
+shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.  
+Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
+initially loaded with $^{233}$U,  reactor-grade Pu, and transuranic (TRU) 
+elements for different absorber materials. All absorber materials provide an 
+adequate shutdown margin for the SD-TMSR core that initially loaded with 
+$^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are 
+negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters 
+ineffective to shut down the reactor loaded with TRU.
+\begin{table}  [!hb]
 	\caption{The shutdown margins for the SD-TMSR core for different absorber materials.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{2cm}|s|s|s}
+	\begin{tabularx}{\textwidth}{p{3cm} s s s}
 		\hline
@@
 
-The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects.
-The anti-shadowing is observed when the combined rod worth is greater than the sum of the individual worths.
-The strongest anti-shadowing effect has occurred in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
+The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
+ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
+anti-shadowing is observed when the combined rod worth is greater than the sum 
+of the individual worths. The strongest anti-shadowing effect has occurred in 
+SSD4 and CSD9 clusters that are located at the boundary between the core zones 
+with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
 The obtained results emphasize the absence of the effect of the absorption material on the interference between the control rod clusters.
 
-Insertion of the control rod affects the neutron flux distribution, which is the basic reason for the amplification of CR worths indicated in Table~\ref{tab:worth}.
-Figure~\ref{fig:totalflux} illustrates the radial neutron flux distribution at mid-core with different CRs position: (1) all CRs withdrawn (2) all CRs inserted (3) all CSD inserted (4) all SSD inserted.
-We chose the B$_4$C-90 as absorber materials because of its high absorption ability.
-As shown in Figure~\ref{fig:totalflux}, the insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions.
-This shifts the neutron flux from the core center towards the periphery.
-A maximum neutron flux shift occurs when all CRs are inserted into the core.
-
-\begin{figure}
+Insertion of the control rod affects the neutron flux distribution, which is 
+the primary reason for the amplification of CR worths indicated in 
+Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
+neutron flux distribution at the mid-core level with different CRs position: 
+(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
+inserted. We chose the B$_4$C-90 as absorber materials because of its high 
+absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
+CRs deforms the radial flux shape in certain positions, i.e., around CRs 
+positions. This shifts the neutron flux from the core center towards the 
+periphery. The maximum neutron flux shift occurs when all CRs are inserted 
+into the core.
+\begin{figure}[!ht]
 	\centering
@@
 	\vspace{-0.5in}
-	\caption{Radial neutron flux distribution at mid-core with different CRs position: (1) all CRs withdrawn (2) all CRs inserted (3) all CSD inserted (4) all SSD inserted.} 
+	\caption{Radial neutron flux distribution at the mid-core for different 
+	CRs positions.} 
 	\label{fig:totalflux}
@@
 
-The integral and differential control rod worth are calculated for three different systems: all control rods, CSD, and SSD systems.
-The CRs are inserted gradually into the core from top to bottom.
-Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and differential CRW.
-Figure~\ref{fig:integ} illustrates the integral CRW for CRs made of B$_4$C-90.
-The maximum integral worth of All CRs, CSD, and SSD clusters are about $48.39$ , $25.3$, and $16.46$ \$, respectively.
-The integral worth of SSD clusters is sufficient to shut down the reactor from any state.
+The integral and differential control rod worth are calculated for three 
+different systems: all control rods, CSD, and SSD systems. The CRs are 
+inserted gradually into the core from the top to the bottom. 
+Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
+differential CRW. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
+made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
+clusters are about $48.39$ , $25.3$, and $16.46$ \$, respectively. The 
+integral worth of SSD clusters is sufficient to shut down the reactor from any 
+state.
 
@@
 
-Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five different absorber materials.
-The results show that all absorber materials have almost the same integral rod worth in the upper quarter of the core ($x$$<$$130$).
-Further insertion of the control rods shows the unique absorption characteristics of each material see part \ref{CR_worth}.
-Enriched B$_4$C-90 absorbs neutrons much grater than the Gd$_2$O$_3$ that has the lowest absorption ability among the other absorber materials in this study.
-All result are based on steady state calculations.
-Further and detailed analysis including burnup calculation will be represented in the near future.
-
+Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
+different absorber materials. The results show that all absorber materials 
+have almost the same integral rod worth in the upper quarter of the core 
+($<130$cm from the upper boundary of the core). Further insertion of the 
+control rods shows the unique absorption characteristics of each material (see 
+part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
+Gd$_2$O$_3$, which has the lowest absorption ability among the other absorber 
+materials in this study. All result are based on steady state calculations. 
+Further and detailed analysis including burnup calculation will be represented 
+in the near future.
 \begin{figure}
@@
 \end{figure}
-
 \begin{figure}

### 2019-12-16 paper/conclusion.tex

--- 2019-11-14 paper/conclusion.tex
@@
 \section{Conclusion} \label{Conclusion}
+In the current work, we introduced design of reactivity control system for the 
+Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
+design has been evaluated at the startup for the full-core geometry using 
+SERPENT-2 Monte-Carlo code. We considered three various startup composition of 
+the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
+(2) $^{232}$Th and plutonium, extracted from \gls{LWR} \gls{SNF}; (3) 
+$^{232}$Th and transuranic vector, extracted from \gls{LWR} \gls{SNF}.
+
+The excess reactivity $\rho_e$ is calculated at zero burnup when all CRs are 
+fully withdrawn. $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
+TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, 
+respectively.
+
+Five different absorber materials are considered based on their neutronics and 
+safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
+HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
+absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
+the other absorber materials in this study. Both CSD and SSD clusters are 
+separately able to shut down the reactor initially loaded with $^{233}$U and 
+reactor-grade Pu regardless of the absorber material type. However, only SSD 
+clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
+with transuranium vector from \gls{LWR}. The reason for this is much larger 
+absorption cross section of $^{10}$B in the relatively soft neutron energy 
+spectrum of the SD-TMSR core started with TRU.
+
+In case of malfunction of the other CR clusters (e.g., stuck in the upper 
+position), the outer ring of the CSD failures to counteract the excess 
+reactivity of the core initially loaded with reactor-grade Pu and transuranic 
+(TRU) elements. However, the worth of the outer ring of the CSD is sufficient 
+to compensate the excess reactivity for the core refueled by $^{233}$U.
+
+All absorber materials provide an adequate shutdown margin for the SD-TMSR 
+core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
+shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
+case), this makes the SSD clusters ineffective to shut down the reactor loaded 
+with TRU.
+
+The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects.
+The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio.
+
+The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions. This shifts the neutron flux from the core center towards the periphery.
+
+The integral and differential control rod worth are calculated for three 
+different systems: all control rods, CSD, and SSD systems. The results show 
+that all absorber materials have almost the same integral rod worth in the 
+upper half of the core. Further insertion of the control rods shows the unique 
+absorption characteristics of each material.
 
 \section{Future work}
+In Part II of this research effort we will evaluate effect of fuel salt 
+burnup on the CRW. The depleted fuel composition will be obtained using 
+SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
+batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
+rykhlevskii_milestone_2019}. Additionally, the authors indent to investigate 
+kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
+effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
+during the SD-TMSR operation. These parameters are crucial for accident 
+transient analysis, which will be performed using Moltres 
+\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
+simulation with taking into account the neutron precursors drift.
 

### 2019-12-16 paper/methods.tex

@@
 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
-\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The \gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power of 2,250 MW$_{th}$. The 
-design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
-\cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential} after modifying the geometry to 
-control the positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
+\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
+\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
+of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
+\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
+\cite{nuttin2005potential} after modifying the geometry to control the 
+positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
 geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
-\cite{li_optimization_2018,ashraf2019whole_core}.
-The active zone of the \gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to enhance breeding performance.
+\cite{li_optimization_2018,ashraf2019whole_core}. The core of the  
+\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
+and the outer zone (522 fuel tubes) to enhance breeding performance.
 
-In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e.
-$^{232}$Th and fissile materials), and $N$ is dependent on the chosen fissile material and the thermochemical state of the liquid fuel salt.
-Three different types of initial fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
-The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, respectively.
-The liquid fuel salt circulates continuously through the fuel tubes that pierce the graphite hexagonal 
-prisms.
-The active zone is surrounded by axial and radial graphite reflectors to minimize the neutron leakage.
-Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of a Hastelloy N alloy.
-The main
-characteristics of the \gls{SD-TMSR} are summarized in Table~\ref{tab:table1}.
+In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
+12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
+materials), and $N$ depends on the chosen fissile material and the  
+thermochemical state of the liquid fuel salt. Three different types of initial 
+fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, 
+(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
+elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
+The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
+respectively. The liquid fuel salt circulates continuously through the fuel 
+tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
+axial and radial graphite reflectors to minimize the neutron leakage. Finally, 
+the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
+a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
+summarized in Table~\ref{tab:table1}.
 
@@
 
-The reactivity of the SD-TMSR core is controlled through two systems of control assemblies:
+The reactivity of the SD-TMSR core is controlled by two clusters of control 
+rods:
 \begin{enumerate}
-\item The Control Safety Devices (CSD), and
-\item The Shutdown Safety Devices (SSD).
+\item Control Safety Devices (CSD);
+\item Shutdown Safety Devices (SSD).
 \end{enumerate}
@@
 \begin{enumerate}
-\item B$_4$C with boron enriched to 90\% $^{10}$B isotope,
-\item hafnium diboride (HfB$_2$),
-\item hafnium hydride (HfH$_{1.62}$),
-\item gadolinium oxide (Gd$_2$O$_3$), and
+\item B$_4$C with boron enriched to 90\% $^{10}$B;
+\item hafnium diboride (HfB$_2$);
+\item hafnium hydride (HfH$_{1.62}$);
+\item gadolinium oxide (Gd$_2$O$_3$);
 \item europium oxide (Eu$_2$O$_3$).
 \end{enumerate}
-Boron carbide (B$_4$C) is widely used in control rods fabrication.
-Enriching B$_4$C increases the fraction of highly neutron absorber isotope (i.e.
-$^{10}$B) and helps to reach the necessary absorptivity.
-However, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C lifespan \cite{guo2019optimized}.
-Hafnium and rare earth elements oxides absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.
+Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching 
+PB$_4$C increases the fraction of highly neutron absorber isotope (i.e. 
+$^{10}$B) and helps to reach the necessary absorptivity. However, issues 
+related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, 
+swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C 
+lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides 
+absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.
 
 The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
-The absorber material is surrounded by a 0.25-cm-thick clad made of AIM1 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of SiC structural material (see Figure~\ref{fig:cr}).
-A small gap between the cladding and rod follower is considered to facilitate the control rod movement.
+The absorber material is surrounded by a 0.25-cm-thick cladding made of AIM1 
+(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 
+SiC structural material (see Figure~\ref{fig:cr}). A small gap between the 
+cladding and rod follower is considered to facilitate the control rod movement.
 
@@
 The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.
-
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 \end{figure}
-
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 	\includegraphics[width=\textwidth]{graphite_element.png}
-	\caption{Graphite element with the four control rods (cluster) located at the same distance from the fuel channel.}
+	\caption{$XY$ section of graphite element with the four control rods 
+	(cluster) located at the same distance from the fuel channel.}
 	\label{fig:graphite_elemen}
 \end{figure}
-
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 	\includegraphics[width=\textwidth]{graphite_element1.png}
-	\caption{Axial view of graphite element with control rods.}
+	\caption{$XZ$ section of graphite element with control rods.}
 	\label{fig:graphite_elemen1}
@@
 
-Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods clusters in the SD-TMSR core.
+Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
+clusters in the SD-TMSR core.
 The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring).
@@
 Red color stands for SSD1-9 clusters.
-We distributed the graphite elements with control rods clusters homogeneously in the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
-The selected core segment in the above corner of the Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four control rods located at the same distance from the fuel channel.
-
+We distributed the graphite elements with control rods clusters uniformly in 
+the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
+The selected core segment at the upper left corner of the 
+Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
+control rods located at the same distance from the fuel channel center.
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 \subsection{Control rod design evaluation}
+In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to 
+perform steady state calculations for the full-core of the SD-TMSR with 
+suggested control rod design. We adopted the ENDF-VII.0 cross section library 
+for all calculations in the present work. The results demonstrate whole-core 
+runs of $12.5\times 10^6$ neutron histories per depletion step. The 
+statistical error in $k_{eff}$ from SERPENT-2 output is equal to $\pm$ $25$ 
+$pcm$.
 
-In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to perform steady state calculations for the full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with control rod design.
-We adopted the ENDF-VII.0 cross section library for all calculations in the present work.
-The results demonstrate whole-core runs of $12.5\times 10^6$ neutron histories per depletion step.
-The statistical error in $k_{eff}$ from SERPENT-2 output is equal to $\pm$ $25$ $pcm$.
-
-The initial calculation state of the SD-TMSR is identified by normal operation conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods clusters.
-In this case, the control rods are located above the upper plenum as shown in Figure~\ref{fig:core_26}.
-To validate the proposed control rods system we adopted the same operation conditions (as in the initial calculation state) and changed the position of the control rod clusters along $Z$ direction.
-The main calculated parameters including reactivity, control rod worth, and interference effects (shadowing effects) will describe in the following parts.
+The initial calculation state of the SD-TMSR is identified by normal operation 
+conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods 
+clusters. In this case, the control rods are located above the upper plenum as 
+shown in Figure~\ref{fig:core_26}. To validate the proposed control rods 
+system we adopted the same operation conditions (as in the initial calculation 
+state) and changed the position of the control rod clusters along $Z$ 
+direction. The main calculated parameters including reactivity, control rod 
+worth, and interference effects (shadowing effects) are described below.
 
@@
 
-Interference between control rods (CRs) or shadowing effects occurs when one (or more) control rod affects the reactivity worth of another control rod in the surroundings.
-Thus, anti-shadowing is observed when the combined rod worth is greater than the sum of the individual worths, however, the shadowing effect appears when the combined rod worth is less than the sum of the individual worths.
-The core height-to-diameter ratio (H/D) and the three-dimensional configuration of the control rods affect the degree of the interference between CRs \cite{girardin2007control}.
+Interference between control rods (CRs) or shadowing effects occurs when one 
+(or more) control rod affects the reactivity worth of another control rod in 
+the surroundings. Thus, anti-shadowing is observed when the combined rod worth 
+is greater than the sum of the individual worths. Oppositely, the shadowing 
+effect appears when the combined rod worth is less than the sum of the 
+individual worths. The core height-to-diameter ratio (H/D) and the 
+three-dimensional configuration of the control rods affect the degree of the 
+interference between CRs \cite{girardin2007control}.
 
@@
 
-The integral CRW is the total reactivity change due to control rod insertion or withdrawal.
-However, the differential CRW is the amount of reactivity inserted per unit of withdrawal [$\$/cm$].
-We change the position of CRs clusters parallel to the z-axis from top to the bottom of the core.
-Equation~\ref{Equ:4} is used to calculate the integral CRW [\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor after and before CR insertion to i$^{th}$ step.
-$\beta_{i}$ is the effective fraction of delayed neutrons at i$^{th}$ step.
-N is the number of steps.
+The integral CRW is the total reactivity change due to the control rod full 
+insertion or withdrawal. In contrast, the differential CRW is the amount of 
+reactivity inserted per unit of withdrawal [$\$/cm$]. To calculate those 
+parameters, we varied the position of CRs clusters from fully withdrawn to 
+fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
+[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
+after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
+fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.
 
@@
 
-Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where $\Delta H$ is the height change of control rod [cm] before and after insertions.
+Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where 
+$\Delta H$ is the height change of control rod [cm] before and after 
+insertions.
 

### 2019-12-17 paper/conclusion.tex
After Andrei's comments in Title, Abstract and Intro #4

@@
 
-Five different absorber materials are considered based on their neutronics and 
+Five different absorbing materials are considered based on their neutronics and 
 safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
@@
 absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
-the other absorber materials in this study. Both CSD and SSD clusters are 
+the other absorbing materials in this study. Both CSD and SSD clusters are 
 separately able to shut down the reactor initially loaded with $^{233}$U and 
-reactor-grade Pu regardless of the absorber material type. However, only SSD 
+reactor-grade Pu regardless of the absorbing material type. However, only SSD 
 clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
@@
 
-All absorber materials provide an adequate shutdown margin for the SD-TMSR 
+All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
 core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
@@
 different systems: all control rods, CSD, and SSD systems. The results show 
-that all absorber materials have almost the same integral rod worth in the 
+that all absorbing materials have almost the same integral rod worth in the 
 upper half of the core. Further insertion of the control rods shows the unique 

### 2019-12-17 paper/introduction.tex
After Andrei's comments in Title, Abstract and Intro #4

@@
 a negative total temperature coefficient of reactivity 
-\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
+\cite{ashraf2019whole_core,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
-the core heats up. However, temperature coefficient of reactivity for graphite 
-is small but positive due to Doppler effect \cite{mathieu2006thorium, 
-rykhlevskii_full-core_2017}. The graphite expansion is not a 
-dominating factor, thus core reactivity will decrease automatically when the 
-core heats up \cite{li_optimization_2018}. MSR designs have a drain tanks to 
+the core heats up. MSR designs have a drain tanks to 
 hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
@@
 
-Safety aspects in the MSRs can be listed as follows 
-\cite{elsheikh2013safety,merle2008optimization}:
-\begin{enumerate}
-\item The negative coefficient of reactivity - high core temperature will reduce reactivity.
-\item The fuel feed rate - decreasing the refueling rate slows down and eventually stops the nuclear chain reaction.
-\item The drain tanks, which have subcritical geometry and passively cooled.
-\item The control rods compensate the excess reactivity, regulate temperature, and/or shut down the reactor.
-\item The continuous removing of fission products and radioactive gasses minimize the chance of radiation exposure.
-\item The outer containment vessel.
-\end{enumerate}
-
-At the Beginning of Life (BOL), we must load the MSR with larger amount of 
+At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
 fuel than that required to achieve criticality (necessary for long term core 
-operation). This leads to excess reactivity at the BOL 
-\cite{duderstadt650nuclear}. Additionally, during burnup, the online 
+operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
+at the BOL is quite large for many refueling scenarios 
+\cite{ashraf2020Strategies,ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
+Additionally, during burnup, the online 
 reprocessing and refueling leads to slow reactivity change, which 
-should be compensated \cite{ashraf2019whole_core}. The most common procedure 
+should be compensated \cite{ashraf2020Strategies,ashraf2019whole_core}. 
+The online reprocessing and refueling system helps to control the reactivity of 
+the MSRs \cite{ashraf2019whole_core}. However, the most common and reliable procedure 
 for reactor control is to insert or withdraw control rods made of material 
@@
 However, we may need to enrich the boron isotope ($^{10}$B) to reach 
-the necessary absorption cross section. Notably, the spatial self-shielding 
-effect correlates with $^{10}$B concentration. For example, B$_4$C enriched to 
-90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its 
-absorption ability is about 2.3 times compared with natural B$_4$C. 
-Additionally, issues related to helium gas release, swelling, melting risk, 
+the necessary absorption cross section. Additionally, issues related to helium gas release, swelling,
 and high loss of the reactivity worth limit the B$_4$C lifespan 
-\cite{guo2019optimized}.
-
-Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
+\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
 potential alternative absorbers for Generation-IV reactors such as 
@@
 \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
-molten salt reactor. Recent studies on MSRs showed that the excess reactivity 
-at the beginning of the operation is quite large for many refueling scenarios 
-\cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
- Adjusting fertile and fissile feed rates helps to control the reactivity of 
-the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a 
-reliable safety system beside the online feed system to control the excess 
-reactivity. Therefore, the main objective of our study is to introduce a new 
-fast reactivity control based on control rods in the \gls{SD-TMSR} to control 
-the reactivity during normal operation. Five different absorber materials are 
+molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
+the SD-TMSR \cite{ashraf2019whole_core,ashraf2020Strategies,li_optimization_2018}.
+However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
+Therefore, the main objective of our study is to introduce a new
+fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
+the reactivity during normal operation and shut down the reactor in case of  
+emergency. Five different absorbing materials are 
 applied to study the main neutronics and safety parameters in the SD-TMSR. We 
 focus on the control rod design, absorption ability, integral and differential 
-control rod worths, shutdown margin of absorber materials, and shadowing 
+control rod worths, shutdown margin of absorbing materials, and shadowing 
 effects at steady state calculation.

### 2019-12-17 paper/methods.tex
After Andrei's comments in Title, Abstract and Intro #4

@@
 The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
-In the present work, five different absorber materials are considered based on their neutronics and safety performance:
+In the present work, five different absorbing materials are considered based on their neutronics and safety performance:
 \begin{enumerate}
@@
 The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
-The absorber material is surrounded by a 0.25-cm-thick cladding made of AIM1 
+The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 

### 2019-12-17 paper/results.tex
After Andrei's comments in Title, Abstract and Intro #4

@@
 between CR clusters, and integral and differential control rod worths are 
-described in this part. Five different absorber materials are considered based 
+described in this part. Five different absorbing materials are considered based 
 on their neutronics and safety performance (see part \ref{CRD}). 
@@
 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
-absorption compared with the other absorber materials in this study. This 
+absorption compared with the other absorbing materials in this study. This 
 result agrees with macroscopic absorption cross sections data 
@@
 Additionally, the worth of the CSD clusters is by factor $1.56$ greater than 
-the worth of the SSD system for all absorber materials. Either CSD or SSD 
+the worth of the SSD system for all absorbing materials. Either CSD or SSD 
 clusters are able to shut down the reactor initially loaded by 
-$^{233}$U and reactor-grade Pu regardless of the absorber material type. 
+$^{233}$U and reactor-grade Pu regardless of the absorbing material type. 
 However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
@@
 the worth almost equal to the worth of all other CRs together regardless of 
-the absorber material type (Table~\ref{tab:worth}). This may be attributed to 
+the absorbing material type (Table~\ref{tab:worth}). This may be attributed to 
 the fact that the absorption cross section decreases with the energy of 
@@
 initially loaded with $^{233}$U,  reactor-grade Pu, and transuranic (TRU) 
-elements for different absorber materials. All absorber materials provide an 
+elements for different absorbing materials. All absorbing materials provide an 
 adequate shutdown margin for the SD-TMSR core that initially loaded with 
@@
 \begin{table}  [!hb]
-	\caption{The shutdown margins for the SD-TMSR core for different absorber materials.}
+	\caption{The shutdown margins for the SD-TMSR core for different absorbing materials.}
 	\vspace{0.1in}
@@
 		\hline
-		Absorber materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
+		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
 		\hline
@@
 (1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
-inserted. We chose the B$_4$C-90 as absorber materials because of its high 
+inserted. We chose the B$_4$C-90 as absorbing materials because of its high 
 absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
@@
 Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
-different absorber materials. The results show that all absorber materials 
+different absorbing materials. The results show that all absorbing materials 
 have almost the same integral rod worth in the upper quarter of the core 
@@
 part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
-Gd$_2$O$_3$, which has the lowest absorption ability among the other absorber 
+Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
 materials in this study. All result are based on steady state calculations. 
@@
 	\vspace{-0.5in}
-	\caption{Integral control rod worth of CSD clusters for different absorber materials.} 
+	\caption{Integral control rod worth of CSD clusters for different absorbing materials.} 
 	\label{fig:CSD}

### 2019-12-20 paper/introduction.tex
After Andrei's comments in Model Description #6

@@
 However, we may need to enrich the boron isotope ($^{10}$B) to reach 
-the necessary absorption cross section. Additionally, issues related to helium gas release, swelling,
+the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling,
 and high loss of the reactivity worth limit the B$_4$C lifespan 
@@
 high thermal conductivity, good resistance to neutron irradiation, and release 
-almost no gas 
+almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
 \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

### 2019-12-20 paper/methods.tex
After Andrei's comments in Model Description #6

@@
 tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
-axial and radial graphite reflectors to minimize the neutron leakage. Finally, 
-the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
+axial and radial graphite reflectors to minimize the neutron leakage.
+A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
+Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
 a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
@@
 \end{enumerate}
-Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching 
-PB$_4$C increases the fraction of highly neutron absorber isotope (i.e. 
-$^{10}$B) and helps to reach the necessary absorptivity. However, issues 
-related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, 
-swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C 
-lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides 
-absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.
 
@@
 The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
-(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 
-SiC structural material (see Figure~\ref{fig:cr}). A small gap between the 
-cladding and rod follower is considered to facilitate the control rod movement.
+(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
+SiC structural material (see Figure~\ref{fig:cr}). We simulated a small gap between the 
+cladding and guide tube to facilitate the control rod movement.
 
@@
 	\includegraphics[width=\textwidth]{core_25.png}
-	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core.}
+	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
 	\label{fig:core_25}
@@
 for all calculations in the present work. The results demonstrate whole-core 
-runs of $12.5\times 10^6$ neutron histories per depletion step. The 
-statistical error in $k_{eff}$ from SERPENT-2 output is equal to $\pm$ $25$ 
+runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles. The 
+statistical error in $k_{eff}$ from SERPENT-2 output is $\leq$ $25$ 
 $pcm$.
@@
 	\includegraphics[width=\textwidth]{core_26.png}
-	\caption{$XZ$ section of the full-core model of the SD-TMSR, CRs are fully withdrawn.}
+	\caption{$XZ$ view at the midplane of the full-core model of the SD-TMSR, 10 CRs are fully withdrawn.}
 	\label{fig:core_26}
@@
 Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where 
-$\Delta H$ is the height change of control rod [cm] before and after 
-insertions.
+$Z$ is the coordinate of the bottom of the control rod.
 
@@
 \label{Equ:5}
-\dfrac{{\partial}{\rho}_{i}}{{\partial{H}}}=\dfrac{1}{{\Delta}{H}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
+\dfrac{{\partial}{\rho}_{i}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
 \end{equation}

### 2019-12-20 paper/conclusion.tex
After Andrei's comments in #7 and #8

@@
 The excess reactivity $\rho_e$ is calculated at zero burnup when all CRs are 
-fully withdrawn. $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
+fully withdrawn. The $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
 TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, 
@@
 reactor-grade Pu regardless of the absorbing material type. However, only SSD 
-clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
+clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
 with transuranium vector from \gls{LWR}. The reason for this is much larger 
@@
 shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
-case), this makes the SSD clusters ineffective to shut down the reactor loaded 
-with TRU.
+case), this makes the SSD clusters unreliable to shut down the reactor loaded 
+with TRU because the SSD clusters should provide a sufficient positive shutdown margin.
 
@@
 
+Finally, the proposed design of CRs successfully control the excess reactivity and enhance the safety aspects of the SD-TMSR.
+
 \section{Future work}
@@
 batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
-rykhlevskii_milestone_2019}. Additionally, the authors indent to investigate 
+rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
 kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 

### 2019-12-20 paper/introduction.tex
After Andrei's comments in #7 and #8

@@
 centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
-ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
+ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
 The MSR is a promising technology because of its dynamics, especially for 
@@
 a negative total temperature coefficient of reactivity 
-\cite{ashraf2019whole_core,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
+\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
@@
 at the BOL is quite large for many refueling scenarios 
-\cite{ashraf2020Strategies,ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
+\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
 Additionally, during burnup, the online 
 reprocessing and refueling leads to slow reactivity change, which 
-should be compensated \cite{ashraf2020Strategies,ashraf2019whole_core}. 
+should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
 The online reprocessing and refueling system helps to control the reactivity of 
-the MSRs \cite{ashraf2019whole_core}. However, the most common and reliable procedure 
+the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
 for reactor control is to insert or withdraw control rods made of material 
@@
 The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
-\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
+\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
 molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
-the SD-TMSR \cite{ashraf2019whole_core,ashraf2020Strategies,li_optimization_2018}.
+the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}.
 However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.

### 2019-12-20 paper/methods.tex
After Andrei's comments in #7 and #8

@@
 geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
-\cite{li_optimization_2018,ashraf2019whole_core}. The core of the  
+\cite{li_optimization_2018,ashraf2020whole}. The core of the 
 \gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
@@
 thermochemical state of the liquid fuel salt. Three different types of initial 
-fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, 
+fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
 (2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
@@
 \begin{table}  %[!ht]
-	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
+	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
 	\vspace{0.1in}
@@
 insertion or withdrawal. In contrast, the differential CRW is the amount of 
-reactivity inserted per unit of withdrawal [$\$/cm$]. To calculate those 
+reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
 parameters, we varied the position of CRs clusters from fully withdrawn to 

### 2019-12-20 paper/results.tex
After Andrei's comments in #7 and #8

@@
 The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
-calculation), when all CRs are fully withdrawn. $\rho_e$ for $^{233}$U, 
+calculation), when all CRs are fully withdrawn. The $\rho_e$ for $^{233}$U, 
 reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
-$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively. For $^{233}$U 
-case, the maximum excess reactivity $\rho$$_e$ is about $4.27\pm0.01$ $\$$ 
-during 60 effective full-power years (EFPY) of reactor operation (see 
-Figure~\ref{fig:keff_25}). 
-The SD-TMSR is able to control the reactivity by adjusting the online 
-refueling and reprocessing rates \cite{ashraf2019whole_core}. An effective and 
-reliable reactivity control system must be designed beside the online feed 
-system to operate with such reactivity changes during burnup.
-
+$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
+Additionally, the previously studied $^{233}$U case recorded the maximum reactivity
+during 60 effective full-power years (EFPY) of reactor operation to be 
+$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25}).
+The proposed reactivity control system must compensate such reactivity at startup and during burnup.
 \begin{figure}
@@
 	\vspace{-0.5in}
-	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2019whole_core}.}
+	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.}
 	\label{fig:keff_25}
@@
 
-The total worth of all control rods ranges from $33.7\pm0.4$ to $48.19\pm0.68$ 
-\$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
+The total worth of all control rods ranges from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
+$\$$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
@@
 
-Additionally, the worth of the CSD clusters is by factor $1.56$ greater than 
+As shown in Table~\ref{tab:worth}, the worth of the CSD clusters is by factor $1.56$ greater than 
 the worth of the SSD system for all absorbing materials. Either CSD or SSD 
@@
 However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
-initially loaded with transuranic (TRU) elements. Increasing the number of SSD 
-cluster or changing their location would increase the worth.
+initially loaded with transuranic (TRU) elements. The reason for this is much larger 
+absorption cross section of $^{10}$B in the relatively soft neutron energy 
+spectrum of the SD-TMSR core started with TRU \cite{ashraf2020Strategies}.
 
@@
 (Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
-graphite is $0.357$. Results show that the inner ring of the CSD has 
+graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
 the worth almost equal to the worth of all other CRs together regardless of 
-the absorbing material type (Table~\ref{tab:worth}). This may be attributed to 
-the fact that the absorption cross section decreases with the energy of 
-incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
+the absorbing material type (Table~\ref{tab:worth}). This happens because the absorption cross section
+decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
 greater than in fast spectrum.
@@
 The SSD clusters are designed mainly for an emergency shutdown, thus it should 
-provide the reactor core with sufficient and adequate negative reactivity. The 
+provide the reactor core with sufficient negative reactivity. The 
 shutdown margin (SDM) is calculated by equation~\ref{Equ:6}.
@@
 initially loaded with $^{233}$U, reactor-grade Pu, and transuranic (TRU) 
-elements for different absorbing materials. All absorbing materials provide an 
-adequate shutdown margin for the SD-TMSR core that initially loaded with 
+elements for different absorbing materials. All absorbing materials provide a sufficient positive
+shutdown margin for the SD-TMSR core that initially loaded with 
 $^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are 
 negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters 
-ineffective to shut down the reactor loaded with TRU.
+unreliable to shut down the reactor loaded with TRU.
+As mentioned previously, the SSD clusters should 
+provide a sufficient positive shutdown margin.
+
 \begin{table}  [!hb]
@@
 with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
-The obtained results emphasize the absence of the effect of the absorption material on the interference between the control rod clusters.
+The obtained results emphasize that there is no relation between the absorbing
+materials type and the interference between the control rod clusters
+(i.e., the amplification factor (A$_{CRi}$)).
 
@@
 Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
-differential CRW. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
+differential CRW, respectively. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
 made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
-clusters are about $48.39$ , $25.3$, and $16.46$ \$, respectively. The 
+clusters are about $48.39$ $\$$, $25.3$ $\$$, and $16.46$ $\$$, respectively. The 
 integral worth of SSD clusters is sufficient to shut down the reactor from any 
@@
 From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux).
-Figure~\ref{fig:diff} shows that the maximum differential CRW  is shifted toward the bottom of the core.
-This because (Need to find a reason(s)).
+Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves is not exactly symmetrical.
+This is due to the asymmetrical distribution for the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.
 
@@
 different absorbing materials. The results show that all absorbing materials 
-have almost the same integral rod worth in the upper quarter of the core 
-($<130$cm from the upper boundary of the core). Further insertion of the 
+have almost the same integral rod worth in the upper half of the core 
+($<250$ cm from the upper boundary of the core). Further insertion of the 
 control rods shows the unique absorption characteristics of each material (see 
@@
 Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
-materials in this study. All result are based on steady state calculations. 
-Further and detailed analysis including burnup calculation will be represented 
-in the near future.
+materials in this study. Notably, all result are based on steady state calculations.
+
 \begin{figure}

### 2020-01-10 paper/introduction.tex
Ready for Andrei's review before proofreading

@@
 
-At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
-fuel than that required to achieve criticality (necessary for long term core 
+At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
+fuel than that required to achieve criticality (necessary for long-term core 
 operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
-at the BOL is quite large for many refueling scenarios 
+at the BOL is large for many refueling scenarios 
 \cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
@@
 the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
-for reactor control is to insert or withdraw control rods made of material 
-with large neutron absorption cross section (e.g., boron, cadmium) 
+to control the reactor is to insert or withdraw control rods made of material 
+with a large neutron absorption cross section (e.g., boron, cadmium) 
 \cite{duderstadt650nuclear}. 
@@
 
-Boron carbide (B$_4$C) is commonly used material for the control rods 
+Boron carbide (B$_4$C) is a commonly used material for the control rods 
 \cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
 However, we may need to enrich the boron isotope ($^{10}$B) to reach 
-the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling,
-and high loss of the reactivity worth limit the B$_4$C lifespan 
+the necessary absorption cross section.
+Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan
 \cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 

### 2020-01-10 paper/results.tex
Ready for Andrei's review before proofreading

@@
 $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
-Additionally, the previously studied $^{233}$U case recorded the maximum reactivity
+The previously studied $^{233}$U case recorded the maximum reactivity
 during 60 effective full-power years (EFPY) of reactor operation to be 
@@
 
-The total worth of all control rods ranges from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
-$\$$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
+The total worth of all control rods extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
+$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 $-$ boron enriched to 90\% $^{10}$B $-$
 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
@@
 absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
-finally Gd$_2$O$_3$. The control rod material are being transmuted during 
-operation. The effect of the fuel salt burnup on the control rod worth is not 
-considered herein, and will be investigated and presented in Part II of this 
+finally Gd$_2$O$_3$. The control rod material is being transmuted during 
+operation. The effect of the fuel salt burnup on the control rod worth is neglected
+herein, and will be investigated and presented in Part II of this 
 study.
 
-As shown in Table~\ref{tab:worth}, the worth of the CSD clusters is by factor $1.56$ greater than 
+The worth of the CSD clusters is by factor $1.56$ greater than 
 the worth of the SSD system for all absorbing materials. Either CSD or SSD 
 clusters are able to shut down the reactor initially loaded by 
-$^{233}$U and reactor-grade Pu regardless of the absorbing material type. 
-However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
-initially loaded with transuranic (TRU) elements. The reason for this is much larger 
+$^{233}$U and reactor-grade Pu regardless of the absorbing material type because 
+the $\rho_e$ for $^{233}$U and reactor-grade Pu as initial fissile material are $1.65\pm0.04$ 
+$\$$ and $4.11\pm0.02$ $\$$, respectively. However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
+initially loaded with transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$). The reason for this is much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 The inner ring of the CSD is located in the central zone of the SD-TMSR core 
-(Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
+(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
 graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
 the worth almost equal to the worth of all other CRs together regardless of 
-the absorbing material type (Table~\ref{tab:worth}). This happens because the absorption cross section
+the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
 decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
@@
 In case of malfunction of other CR clusters (e.g., stuck in the upper 
-position), the outer ring of the CSD cannot compensate the excess 
+position), the outer ring of the CSD failed to compensate the excess 
 reactivity of the core initially loaded by reactor-grade Pu and transuranic 
 (TRU) elements. However, the outer ring of the CSD worth is sufficient 
-to compensate the excess reactivity for the core refueled by $^{233}$U .
+to compensate the excess reactivity for the core refueled by $^{233}$U.
 
 We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters to 
-investigate the variation of CRW with the position in the active core.
+investigate the variation of CRW with the position in the inner core.
 The CRW decreases in the direction of the outer core zone. The outer core zone 
@@
 		\hline
-		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ &$1.01\pm0.09$ $\$$ \\
-		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.8\pm0.09$ $\$$\\
+		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
+		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.80\pm0.09$ $\$$\\
 		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
-		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
-		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.89\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
+		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.120\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
+		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
 		\hline
@@
 with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
-The obtained results emphasize that there is no relation between the absorbing
+The obtained results emphasize that no relation between the absorbing
 materials type and the interference between the control rod clusters
@@
 periphery. The maximum neutron flux shift occurs when all CRs are inserted 
-into the core.
+into the core \cite{girardin2007control}.
 \begin{figure}[!ht]
@@
 
-The integral and differential control rod worth are calculated for three 
+The integral and differential control rod worths are calculated for three 
 different systems: all control rods, CSD, and SSD systems. The CRs are 
@@
 Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
-materials in this study. Notably, all result are based on steady state calculations.
+materials in this study. Notably, all results are based on steady state calculations.
 

### 2020-01-13 paper/conclusion.tex

@@
 clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
-with transuranium vector from \gls{LWR}. The reason for this is much larger 
+with transuranic vector from \gls{LWR}. The reason for this is much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 In case of malfunction of the other CR clusters (e.g., stuck in the upper 
-position), the outer ring of the CSD failures to counteract the excess 
+position), the outer ring of the CSD failed to counteract the excess 
 reactivity of the core initially loaded with reactor-grade Pu and transuranic 
@@
 \section{Future work}
-In Part II of this research effort we will evaluate effect of fuel salt 
+In Part II of this research effort, we will evaluate effect of fuel salt 
 burnup on the CRW. The depleted fuel composition will be obtained using 

### 2020-01-13 paper/methods.tex

@@
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
+The Chinese Academy of Sciences proposed the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design in 2011
 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
@@
 \cite{nuttin2005potential} after modifying the geometry to control the 
-positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
-geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
+positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
+described in detail the \gls{SD-TMSR} core geometry
 \cite{li_optimization_2018,ashraf2020whole}. The core of the 
@@
 
-Since the total quantity and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis.
+Since the total number and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis.
 We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
@@
 Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
-The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.
+The total number of graphite elements with control rods are 25: 16 CSD and 9 SSD.
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 We distributed the graphite elements with control rods clusters uniformly in 
-the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
+the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
 The selected core segment at the upper left corner of the 
@@
 
-Interference between control rods (CRs) or shadowing effects occurs when one 
+Interference between control rods (CRs) or shadowing effects occur when one 
 (or more) control rod affects the reactivity worth of another control rod in 
-the surroundings. Thus, anti-shadowing is observed when the combined rod worth 
-is greater than the sum of the individual worths. Oppositely, the shadowing 
-effect appears when the combined rod worth is less than the sum of the 
-individual worths. The core height-to-diameter ratio (H/D) and the 
-three-dimensional configuration of the control rods affect the degree of the 
-interference between CRs \cite{girardin2007control}.
+the surroundings. Thus, the shadowing effect appears when the combined rod worth
+is less than the sum of the individual worths. Oppositely, anti-shadowing is observed 
+when the combined rod worth is greater than the sum of the individual worths.
+The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
+of the control rods affect the degree of the interference between CRs \cite{girardin2007control}.
 
@@
 The integral CRW is the total reactivity change due to the control rod full 
-insertion or withdrawal. In contrast, the differential CRW is the amount of 
+insertion or withdrawal. However, the differential CRW is the amount of 
 reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
@@
 after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
-fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.
+fraction of delayed neutrons at i$^{th}$ step. $N$ is the number of steps.
 

### 2020-01-21 paper/methods.tex
After Tikhomirov's review

@@
 		B$_4$C density, g/cm$^3$					& 2.52  \\ 
-		$^{10}$B enrichment, \%						&  18.4  \\
 		Core diameter, cm								& 460  \\
@@
 The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
-In the present work, five different absorbing materials are considered based on their neutronics and safety performance:
+In the present work, six different absorbing materials are considered based on their neutronics and safety performance:
 \begin{enumerate}
+\item natural B$_4$C (19.9\% $^{10}$B);
 \item B$_4$C with boron enriched to 90\% $^{10}$B;
@@
 \subsection{Control rod design evaluation}
-In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to 
+In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
 perform steady state calculations for the full-core of the SD-TMSR with 
@@
 fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
-[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
-after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
-fraction of delayed neutrons at i$^{th}$ step. $N$ is the number of steps.
+[\$], where $k_{j}$ and $k_{j-1}$ are the effective multiplication factor 
+after and before CR insertion to $j$$^{th}$ step. $\beta_{j}$ is the effective 
+fraction of delayed neutrons at $j$$^{th}$ step. $N$ is the number of steps.
 
@@
 \label{Equ:4}
-{{\Delta}{\rho}_{i}}=\sum_{i=1}^{N}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
+{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}},
 \end{equation}
@@
 \label{Equ:5}
-\dfrac{{\partial}{\rho}_{i}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
+\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}},
 \end{equation}

### 2020-01-21 paper/results.tex
After Tikhomirov's review

@@
 between CR clusters, and integral and differential control rod worths are 
-described in this part. Five different absorbing materials are considered based 
-on their neutronics and safety performance (see part \ref{CRD}). 
+described in this part. 
 Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
-factor (A$_{CRi}$), and the type of interference for five different 
+factor (A$_{CRi}$), and the type of interference for the six different 
 absorbers.
@@
 \begin{sidewaystable}
-	\fontsize{6}{9}\selectfont
+	\fontsize{5}{7}\selectfont
 	\centering
@@
 	\vspace{1ex}
-	\begin{tabularx}{\textwidth}{|X|p{0.65cm}|p{0.65cm}|p{0.65cm}| 
-	p{0.65cm}|p{0.65cm}|p{0.65cm}| p{0.65cm}|p{0.65cm}|p{0.65cm}| 
-	p{0.65cm}|p{0.65cm}|p{0.65cm}| p{0.65cm}|p{0.65cm}|p{0.65cm}|}
+	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
+	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
+	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|}
 		\hline
 		\multirow{2}{*}{Control Rod group}		& 
-		\multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	
+		\multicolumn{3}{c|}{Nat. B$_4$C} & \multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	
 		&\multicolumn{3}{c|}{HfH$_{1.62}$} 
@@
 		\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
-		\cline{2-16}
-		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Interfe\-rence	
-		&$\Delta\rho$$_{CRi}$ [\$]&A$_{CRi}$	& Interfe\-rence	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Interfe\-rence	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Interfe\-rence	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  &	Interfe\-rence \\
+		\cline{2-19}
+		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference
+		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference	
+		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$	& Inter\-ference	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  &	Inter\-ference \\
 		\hline                   
-		All control rods        				& $48.19\pm0.68$   &	&	
-		&$40.4\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.7\pm0.4$	&	
+		All control rods      &  $42.04\pm0.60$	&	&		& $48.19\pm0.68$   &	&	
+		&$40.40\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.70\pm0.40$	&	
 		&	&$42.39\pm0.48$	& &	 \\
 		\hline 
-		CSD 							& $25.5\pm0.23$   &$1.24\pm0.01$	&$\star$	&$21.9\pm0.17$	&$1.1\pm0.01$	&$\star$	&$20.62\pm0.34$	&$1.1\pm0.01$	&$\star$	&$18.48\pm0.25$	&$1.17\pm0.01$	&$\star$	&$22.96\pm0.18$	&$1.2\pm0.01$ &$\star$ \\
+		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	&	$\star$				& $25.50\pm0.23$   &$1.24\pm0.01$	&$\star$	&$21.90\pm0.17$	&$1.10\pm0.01$	&$\star$	&$20.62\pm0.34$	&$1.10\pm0.01$	&$\star$	&$18.48\pm0.25$	&$1.17\pm0.01$	&$\star$	&$22.96\pm0.18$	&$1.20\pm0.01$ &$\star$ \\
 		\hline 
-		SSD		  		&$16.39\pm0.11$ &$1.38\pm0.02$	&$\star$	&$14.27\pm0.21$	&$1.29\pm0.01$	&$\star$	&$13.23\pm0.18$	&$1.3\pm0.06$	&$\star$	&$12\pm0.2$	&$1.26\pm0.01$	&$\star$	&$14.58\pm0.11$	&$1.3\pm0.02$	&$\star$ \\
+		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	&	$\star$	&$16.39\pm0.11$ &$1.38\pm0.02$	&$\star$	&$14.27\pm0.21$	&$1.29\pm0.01$	&$\star$	&$13.23\pm0.18$	&$1.30\pm0.06$	&$\star$	&$12.00\pm0.20$	&$1.26\pm0.01$	&$\star$	&$14.58\pm0.11$	&$1.30\pm0.02$	&$\star$ \\
 		\hline 
-		CSD inner ring  &  $18.42\pm0.05$  &$1.6\pm0.04$	&$\star$		&$16.29\pm0.29$	&$1.48\pm0.02$	&$\star$	&$15.5\pm0.17$	& $1.46\pm0.01$ &$\star$	&$14.12\pm0.07$	&$1.39\pm0.01$	&$\star$	&$16.92\pm0.13$	&$1.5\pm0.01$	 &$\star$\\
+		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	&$\star$ &  $18.42\pm0.05$  &$1.60\pm0.04$	&$\star$		&$16.29\pm0.29$	&$1.48\pm0.02$	&$\star$	&$15.50\pm0.17$	& $1.46\pm0.01$ &$\star$	&$14.12\pm0.07$	&$1.39\pm0.01$	&$\star$	&$16.92\pm0.13$	&$1.50\pm0.01$	 &$\star$\\
 		\hline 
-		CSD outer ring            	    &$2.26\pm0.02$ &$4.21\pm0.07$	&$\star$	&$2.1\pm0.06$	&$3.11\pm0.1$&$\star$	&$1.85\pm0.07$	&$3.24\pm0.06$	&$\star$	&$1.8\pm0.1$	&$2.54\pm0.14$	&$\star$	&$2.14\pm0.05$	&$3.2\pm0.05$	 &$\star$	\\
+		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	&	$\star$    &$2.26\pm0.02$ &$4.21\pm0.07$	&$\star$	&$2.10\pm0.06$	&$3.11\pm0.10$&$\star$	&$1.85\pm0.07$	&$3.24\pm0.06$	&$\star$	&$1.80\pm0.10$	&$2.54\pm0.14$	&$\star$	&$2.14\pm0.05$	&$3.20\pm0.05$	 &$\star$	\\
 		\hline 
-		CSD2								& $2.25\pm0.04$   &$3.69\pm0.16$	&$\star$	&$2.24\pm0.05$	&$2.42\pm0.1$	&$\star$	&$2\pm0.1$	&$2.68\pm0.03$	&$\star$	&$1.8\pm0.1$	&$2.55\pm0.2$	&$\star$	&$2.19\pm0.12$	&$2.9\pm0.08$	&$\star$ \\
+		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	&	$\star$				& $2.25\pm0.04$   &$3.69\pm0.16$	&$\star$	&$2.24\pm0.05$	&$2.42\pm0.10$	&$\star$	&$2.00\pm0.10$	&$2.68\pm0.03$	&$\star$	&$1.80\pm0.10$	&$2.55\pm0.20$	&$\star$	&$2.19\pm0.12$	&$2.90\pm0.08$	&$\star$ \\
 		\hline 
-		CSD9								& $0.15\pm0.04$   & $10.53\pm0.01$	&$\star$$\star$	&$0.1\pm0.05$	&$5.1\pm0.05$	&$\star$	&$0.05\pm0.01$	&$16.4\pm0.1$	&$\star$$\star$	&$0.09\pm0.07$	&$5.55\pm0.2$	&$\star$$\star$	&$0.07\pm0.05$	&$14\pm0.1$	&$\star$$\star$ \\
+		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	&	$\star$$\star$				& $0.15\pm0.04$   & $10.53\pm0.01$	&$\star$$\star$	&$0.10\pm0.05$	&$5.10\pm0.05$	&$\star$	&$0.05\pm0.01$	&$16.40\pm0.10$	&$\star$$\star$	&$0.09\pm0.07$	&$5.55\pm0.20$	&$\star$$\star$	&$0.07\pm0.05$	&$14.00\pm0.10$	&$\star$$\star$ \\
 		\hline
-		SSD1					& $4.18\pm0.07$   &$1.59\pm0.08$	&$\star$	&$3.95\pm0.13$	&$1.3\pm0.07$	&$\star$	&$3.59\pm0.03$	&$1.49\pm0.01$	&$\star$	&$3.45\pm0.12$	&$1.4\pm0.08$	&$\star$	&$3.91\pm0.06$	&$1.4\pm0.01$&$\star$ \\
+		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	&	$\star$		& $4.18\pm0.07$   &$1.59\pm0.08$	&$\star$	&$3.95\pm0.13$	&$1.30\pm0.07$	&$\star$	&$3.59\pm0.03$	&$1.49\pm0.01$	&$\star$	&$3.45\pm0.12$	&$1.40\pm0.08$	&$\star$	&$3.91\pm0.06$	&$1.40\pm0.01$&$\star$ \\
 		\hline 
-		SSD4					&  $0.57\pm0.09$  &$7.84\pm0.15$	&$\star$$\star$	&$0.63\pm0.06$	&$4.4\pm0.1$	&$\star$	&$1\pm0.05$	&$2.51\pm0.16$	&$\star$	&$0.6\pm0.8$	&$3.31\pm0.27$	&$\star$	&$0.6\pm0.08$	&$5.1\pm0.28$	&$\star$$\star$ \\
+		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	&	$\star$$\star$		&  $0.57\pm0.09$  &$7.84\pm0.15$	&$\star$$\star$	&$0.63\pm0.06$	&$4.40\pm0.10$	&$\star$	&$1.00\pm0.05$	&$2.51\pm0.16$	&$\star$	&$0.60\pm0.80$	&$3.31\pm0.27$	&$\star$	&$0.60\pm0.08$	&$5.10\pm0.28$	&$\star$$\star$ \\
 		\hline
@@
 \cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
-absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
+absorption cross sections followed by Eu$_2$O$_3$, natural B$_4$C (Nat. B$_4$C), HfB$_2$, HfH$_{1.62}$, and 
 finally Gd$_2$O$_3$. The control rod material is being transmuted during 
@@
 graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
-the worth almost equal to the worth of all other CRs together regardless of 
+the worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
 the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
@@
 		\hline
+		Nat. B$_4$C					& $12.62\pm0.08$ $\$$ &$10.18\pm0.09$ $\$$ &$-1.12\pm0.08$ $\$$ \\
 		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
@@
 		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
-		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.120\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
+		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
 		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
@@
 	\caption{Radial neutron flux distribution at the mid-core for different 
-	CRs positions.} 
+	CRs positions (CRs made of B$_4$C-90).} 
 	\label{fig:totalflux}
@@
 made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
-clusters are about $48.39$ $\$$, $25.3$ $\$$, and $16.46$ $\$$, respectively. The 
-integral worth of SSD clusters is sufficient to shut down the reactor from any 
+clusters are about $48.39$ $\$$, $25.30$ $\$$, and $16.46$ $\$$, respectively. The 
+integral worth of SSD clusters made of B$_4$C-90 is sufficient to shut down the reactor from any 
 state.
@@
 
-Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
+Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with the six 
 different absorbing materials. The results show that all absorbing materials 
@@
 	\vspace{-0.5in}
-	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters.} 
+	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
 	\label{fig:integ}
@@
 	\vspace{-0.5in}
-	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters.} 
+	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
 	\label{fig:diff}

### 2020-01-21 paper/results.tex
Minor changes from Andrei

@@
 Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
-factor (A$_{CRi}$), and the type of interference for the six different 
+factor (A$_{CRi}$), and the type of interference for six different 
 absorbers.
@@
 
-Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with the six 
+Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with six 
 different absorbing materials. The results show that all absorbing materials 

### 2020-01-21 paper/conclusion.tex

@@
 
-Five different absorbing materials are considered based on their neutronics and 
-safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
+Six different absorbing materials are considered in this work:
+natural B$_4$C, B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
 HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 

### 2020-01-21 paper/introduction.tex

@@
 The online reprocessing and refueling system helps to control the reactivity of 
-the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
+the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
 to control the reactor is to insert or withdraw control rods made of material 
@@
 the reactivity during normal operation and shut down the reactor in case of 
-emergency. Five different absorbing materials are 
+emergency. Six different absorbing materials are 
 applied to study the main neutronics and safety parameters in the SD-TMSR. We 

### 2020-01-22 paper/conclusion.tex
After proofreading

@@
 \section{Conclusion} \label{Conclusion}
-In the current work, we introduced design of reactivity control system for the 
+In the current work, we introduced design of a reactivity control system for the 
 Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
 design has been evaluated at the startup for the full-core geometry using 
-SERPENT-2 Monte-Carlo code. We considered three various startup composition of 
+SERPENT-2 Monte-Carlo code. We considered three various startup compositions of 
 the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
-(2) $^{232}$Th and plutonium, extracted from \gls{LWR} \gls{SNF}; (3) 
-$^{232}$Th and transuranic vector, extracted from \gls{LWR} \gls{SNF}.
+(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
+$^{232}$Th and TRU vector, extracted from \gls{LWR} \gls{SNF}.
 
@@
 clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
-with transuranic vector from \gls{LWR}. The reason for this is much larger 
+with TRU vector from \gls{LWR}. The reason for this is the much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 position), the outer ring of the CSD failed to counteract the excess 
-reactivity of the core initially loaded with reactor-grade Pu and transuranic 
-(TRU) elements. However, the worth of the outer ring of the CSD is sufficient 
+reactivity of the core initially loaded with reactor-grade Pu and TRU elements.
+However, the worth of the outer ring of the CSD is sufficient 
 to compensate the excess reactivity for the core refueled by $^{233}$U.
@@
 
-The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions. This shifts the neutron flux from the core center towards the periphery.
+The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs. This shifts the neutron flux from the core center towards the periphery.
 
-The integral and differential control rod worth are calculated for three 
-different systems: all control rods, CSD, and SSD systems. The results show 
+The integral and differential CR worth are calculated for three 
+different systems: all CRs, CSD, and SSD systems. The results show 
 that all absorbing materials have almost the same integral rod worth in the 
-upper half of the core. Further insertion of the control rods shows the unique 
+upper half of the core. Further insertion of the CRs shows the unique 
 absorption characteristics of each material.
@@
 \section{Future work}
-In Part II of this research effort, we will evaluate effect of fuel salt 
-burnup on the CRW. The depleted fuel composition will be obtained using 
+In Part II of this research effort, we will evaluate the effect of fuel salt 
+burnup on the CRW. The depleted fuel composition will be obtained using a
 SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
@@
 rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
-kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
+kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
 effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 

### 2020-01-22 paper/introduction.tex
After proofreading

@@
 online reprocessing, and fuel handling. Safety is one of the primary goals of 
-the MSR systems, which was understudied and require further investigation. The 
-unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
+the MSR system, which was understudied and requires further investigation. The 
+unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
 etc.) strongly affect its control system design. Graphite-moderated MSRs have 
@@
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
-the core heats up. MSR designs have a drain tanks to 
+the core heats up. MSR designs have drain tanks to 
 hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
-located under the core, passively melts when the fuel temperature reaches a 
+is located under the core, passively melts when the fuel temperature reaches a 
 critical point, and drains the fuel salt from the reactor vessel to the drain 
@@
 fuel than that required to achieve criticality (necessary for long-term core 
-operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
+operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
 at the BOL is large for many refueling scenarios 
@@
 Boron carbide (B$_4$C) is a commonly used material for the control rods 
-\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
-However, we may need to enrich the boron isotope ($^{10}$B) to reach 
+\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
+however, we may need to enrich the boron isotope ($^{10}$B) to reach 
 the necessary absorption cross section.
@@
 hafnium-based materials and rare earth element oxides. These absorbers have 
-high thermal conductivity, good resistance to neutron irradiation, and release 
-almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
+high thermal conductivity, good resistance to neutron irradiation, and
+almost no gas release (absorbing neutrons mainly through (n,$\gamma$) reactions)
 \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
@@
 the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}.
-However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
+However, a reactivity control system for maneuvering and emergency shutdown has not been introduced in literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
 Therefore, the main objective of our study is to introduce a new

### 2020-01-22 paper/results.tex
After proofreading

@@
 The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
-calculation), when all CRs are fully withdrawn. The $\rho_e$ for $^{233}$U, 
+calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
 reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
@@
 described in this part. 
-Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
+Table~\ref{tab:worth} shows calculated CRW, the amplification 
 factor (A$_{CRi}$), and the type of interference for six different 
@@
 
-The total worth of all control rods extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
-$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 $-$ boron enriched to 90\% $^{10}$B $-$
+The total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
+$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
 absorption compared with the other absorbing materials in this study. This 
-result agrees with macroscopic absorption cross sections data 
+result agrees with macroscopic absorption cross section data 
 \cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
-absorption cross sections followed by Eu$_2$O$_3$, natural B$_4$C (Nat. B$_4$C), HfB$_2$, HfH$_{1.62}$, and 
-finally Gd$_2$O$_3$. The control rod material is being transmuted during 
-operation. The effect of the fuel salt burnup on the control rod worth is neglected
-herein, and will be investigated and presented in Part II of this 
+absorption cross section followed by Eu$_2$O$_3$, natural B$_4$C (Nat. B$_4$C), HfB$_2$, HfH$_{1.62}$, and 
+finally Gd$_2$O$_3$. The CR material is being transmuted during 
+operation; the effect of the fuel salt burnup on the CRW is neglected
+herein and will be investigated and presented in Part II of this 
 study.
 
-The worth of the CSD clusters is by factor $1.56$ greater than 
+The worth of the CSD clusters is $1.56$ times greater than 
 the worth of the SSD system for all absorbing materials. Either CSD or SSD 
@@
 $\$$ and $4.11\pm0.02$ $\$$, respectively. However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
-initially loaded with transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$). The reason for this is much larger 
+initially loaded with transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$). The reason for this is the much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
-the worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
+a worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
 the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
-decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
-greater than in fast spectrum.
+decreases with the energy of the incident neutron; for example, boron absorbs neutrons in the thermal spectrum much 
+greater than in the fast spectrum.
 
@@
 position), the outer ring of the CSD failed to compensate the excess 
-reactivity of the core initially loaded by reactor-grade Pu and transuranic 
-(TRU) elements. However, the outer ring of the CSD worth is sufficient 
+reactivity of the core initially loaded by reactor-grade Pu and TRU elements. However, the outer ring of the CSD worth is sufficient 
 to compensate the excess reactivity for the core refueled by $^{233}$U.
@@
 has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
-($2.8$), consequently, the neutron energy spectrum is faster in the peripheral 
-zone than in the center of the core. As mentioned previously, the CRs 
-absorption ability degrades in fast spectrum.
+($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
+zone than in the center of the core. As mentioned previously, the CR's 
+absorption ability degrades in the fast spectrum.
 
-\subsubsection{Shutdown Margin (SDM)}
+\subsubsection{Shutdown margin (SDM)}
 
@@
 Table~\ref{tab:table2} summarizes the shutdown margins for the SD-TMSR core 
-initially loaded with $^{233}$U, reactor-grade Pu, and transuranic (TRU) 
+initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
 elements for different absorbing materials. All absorbing materials provide a sufficient positive
-shutdown margin for the SD-TMSR core that initially loaded with 
-$^{233}$U and reactor-grade Pu. However, the shutdown margins for TRU case are 
-negative or slightly positive (in B$_4$C-90 case), this makes the SSD clusters 
+SDM for the SD-TMSR core that is initially loaded with 
+$^{233}$U and reactor-grade Pu. However, the SDMs for the TRU case are 
+negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
 unreliable to shut down the reactor loaded with TRU.
 As mentioned previously, the SSD clusters should 
-provide a sufficient positive shutdown margin.
+provide a sufficient positive SDM.
 
 \begin{table}  [!hb]
-	\caption{The shutdown margins for the SD-TMSR core for different absorbing materials.}
+	\caption{The SDMs for the SD-TMSR core for different absorbing materials.}
 	\vspace{0.1in}
@@
 anti-shadowing is observed when the combined rod worth is greater than the sum 
-of the individual worths. The strongest anti-shadowing effect has occurred in 
+of the individual worths. The strongest anti-shadowing effect occurred in 
 SSD4 and CSD9 clusters that are located at the boundary between the core zones 
-with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
-The obtained results emphasize that no relation between the absorbing
-materials type and the interference between the control rod clusters
-(i.e., the amplification factor (A$_{CRi}$)).
+with different moderator-to-fuel ratios (see Table~\ref{tab:worth}).
+The obtained results emphasize that no relation exists between the absorbing
+material type and the interference between the CR clusters
+(i.e., the A$_{CRi}$).
 
-Insertion of the control rod affects the neutron flux distribution, which is 
-the primary reason for the amplification of CR worths indicated in 
+Insertion of the CR affects the neutron flux distribution, which is 
+the primary reason for the amplification of CRWs indicated in 
 Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
-neutron flux distribution at the mid-core level with different CRs position: 
+neutron flux distribution at the mid-core level with different CR positions: 
 (1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
-inserted. We chose the B$_4$C-90 as absorbing materials because of its high 
+inserted. We chose the B$_4$C-90 as the absorbing material because of its high 
 absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
-CRs deforms the radial flux shape in certain positions, i.e., around CRs 
-positions. This shifts the neutron flux from the core center towards the 
+CRs deforms the radial flux shape in certain positions, i.e., around CRs.
+This shifts the neutron flux from the core center towards the 
 periphery. The maximum neutron flux shift occurs when all CRs are inserted 
@@
 	\caption{Radial neutron flux distribution at the mid-core for different 
-	CRs positions (CRs made of B$_4$C-90).} 
+	CR positions (CRs made of B$_4$C-90).} 
 	\label{fig:totalflux}
@@
 
-The integral and differential control rod worths are calculated for three 
-different systems: all control rods, CSD, and SSD systems. The CRs are 
+The integral and differential CRWs are calculated for three 
+different systems: all CRs, CSD, and SSD systems. The CRs are 
 inserted gradually into the core from the top to the bottom. 
-Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
+Equations~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
 differential CRW, respectively. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
-made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
+made of B$_4$C-90. The maximum integral worth of all CRs, CSD, and SSD 
 clusters are about $48.39$ $\$$, $25.30$ $\$$, and $16.46$ $\$$, respectively. The 
@@
 From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux).
-Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves is not exactly symmetrical.
-This is due to the asymmetrical distribution for the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.
+Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves are not exactly symmetrical.
+This is due to the asymmetrical distribution of the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.
 
@@
 ($<250$ cm from the upper boundary of the core). Further insertion of the 
-control rods shows the unique absorption characteristics of each material (see 
+CRs shows the unique absorption characteristics of each material (see 
 part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
@@
 	\vspace{-0.5in}
-	\caption{Integral control rod worth of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
+	\caption{Integral CRW of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
 	\label{fig:integ}
@@
 	\vspace{-0.5in}
-	\caption{Differential control rod worth of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
+	\caption{Differential CRW of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
 	\label{fig:diff}
@@
 	\vspace{-0.5in}
-	\caption{Integral control rod worth of CSD clusters for different absorbing materials.} 
+	\caption{Integral CRW of CSD clusters for different absorbing materials.} 
 	\label{fig:CSD}

### 2020-01-23 paper/methods.tex

@@
 Since the total number and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis.
-We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
+We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
 Every four control rods (cluster) can move together as one group.
-Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
+Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
 The total number of graphite elements with control rods are 25: 16 CSD and 9 SSD.
@@
 
-Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
+Figure~\ref{fig:core_25} illustrates the numbering scheme of control rod 
 clusters in the SD-TMSR core.
-The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring).
+The CSD1-16 clusters are represented as yellow and distributed as two rings: inner and outer (peripheral) ring.
 The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16.
-Red color stands for SSD1-9 clusters.
-We distributed the graphite elements with control rods clusters uniformly in 
+Red stands for SSD1-9 clusters.
+We distributed the graphite elements with control rod clusters uniformly in 
 the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
-The selected core segment at the upper left corner of the 
+The selected core segment at the upper left corner of 
 Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
@@
 	\includegraphics[width=\textwidth]{core_25.png}
-	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
+	\caption{Distribution of the graphite elements with CRs in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
 	\label{fig:core_25}
@@
 In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
-perform steady state calculations for the full-core of the SD-TMSR with 
-suggested control rod design. We adopted the ENDF-VII.0 cross section library 
+perform steady state calculations for the full core of the SD-TMSR with 
+the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
 for all calculations in the present work. The results demonstrate whole-core 
 runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles. The 
-statistical error in $k_{eff}$ from SERPENT-2 output is $\leq$ $25$ 
+statistical error in $k_{eff}$ from the SERPENT-2 output is $\leq$ $25$ 
 $pcm$.
@@
 The initial calculation state of the SD-TMSR is identified by normal operation 
-conditions (see Table~\ref{tab:table1}) and fully withdrawn control rods 
+conditions (see Table~\ref{tab:table1}) and fully withdrawn control rod 
 clusters. In this case, the control rods are located above the upper plenum as 
@@
 system we adopted the same operation conditions (as in the initial calculation 
-state) and changed the position of the control rod clusters along $Z$ 
+state) and changed the position of the control rod clusters along the $Z$ 
 direction. The main calculated parameters including reactivity, control rod 
@@
 The excess reactivity $\rho$$_e$ is the reactivity of the core when all control rods are withdrawn.
-$\rho$$_e$ is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core and $\beta_{eff}$ is the effective fraction of delayed neutrons.
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using perturbation technique in SERPENT-2 \cite{leppanen2014calculation}.
+$\rho$$_e$ is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core and $\beta_{eff}$ is the effective fraction of delayed neutrons:
 
@@
 \label{Equ:1}
-{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}{{\beta}_{eff}}},
+{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}{{\beta}_{eff}}}.
 \end{equation}
 
-\subsubsection{The control rod worths (CRW)}
+The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}.
 
-The control rod worth (CRW) is the amount of negative reactivity that associated with the control rod insertion.
-The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of i$^{th}$ CR, $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion i$^{th}$ CR \cite{vcerba2017optimization}.
+\subsubsection{The control rod worth (CRW)}
+
+The control rod worth (CRW) is the amount of negative reactivity associated with the control rod insertion.
+The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ control rod (CR), $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion of the i$^{th}$ CR \cite{vcerba2017optimization}:
 
@@
 \label{Equ:2}
-{{\Delta}{\rho}_{CRi}}={{\rho}_{e}}-{{\rho}_{CRi}},
+{{\Delta}{\rho}_{CRi}}={{\rho}_{e}}-{{\rho}_{CRi}}.
 \end{equation}
 
-\subsubsection{Shutdown Margin (SDM)}
+\subsubsection{Shutdown margin (SDM)}
 
 The shutdown margin (SDM) is the amount of reactivity by which a full reactor core is subcritical from a given state.
-The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity.
+The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity:
 
@@
 \label{Equ:6}
-{SDM}={{\Delta}{\rho}_{SSD}}-{{\rho}_{e}},
+{SDM}={{\Delta}{\rho}_{SSD}}-{{\rho}_{e}}.
 \end{equation}
@@
 The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
-of the control rods affect the degree of the interference between CRs \cite{girardin2007control}.
+of the CRs affect the degree of the interference between CRs \cite{girardin2007control}.
 
-The amplification factor (A$_{CRi}$) of i$^{th}$ control rod helps to evaluate the shadowing effects between control rod clusters.
-The amplification factor is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all control rods (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the investigated one i$^{th}$ and $\Delta\rho$$_{CRi}$ the worth of the i$^{th}$ rod.
+The amplification factor (A$_{CRi}$) of the i$^{th}$ CR helps to evaluate the shadowing effects between CR clusters.
+The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:
 
@@
 \label{Equ:3}
-{{A}_{CRi}}=\dfrac{{{\Delta}{\rho}_{CR(1,2,\ldots N)}}-{{\Delta}{\rho}_{CR(1,2,\ldots N-i)}}}{{\Delta}{\rho}_{CRi}},
+{{A}_{CRi}}=\dfrac{{{\Delta}{\rho}_{CR(1,2,\ldots N)}}-{{\Delta}{\rho}_{CR(1,2,\ldots N-i)}}}{{\Delta}{\rho}_{CRi}}.
 \end{equation}
 
-If A$_{CRi}$ is $<$1, the control rod worth is reduced due to shadowing effects, while if A$_{CRi}$ is $>$1 the control rod worth is amplified and anti-shadowing effects occur.
-A$_{CRi}$ = 1 means no shadowing effects occur.
+If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1 the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.
 
@@
 
-The integral CRW is the total reactivity change due to the control rod full 
-insertion or withdrawal. However, the differential CRW is the amount of 
+The integral CRW is the total reactivity change due to the full 
+insertion or withdrawal of the CR. However, the differential CRW is the amount of 
 reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
-parameters, we varied the position of CRs clusters from fully withdrawn to 
+parameters, we varied the position of CR clusters from fully withdrawn to 
 fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
 [\$], where $k_{j}$ and $k_{j-1}$ are the effective multiplication factor 
-after and before CR insertion to $j$$^{th}$ step. $\beta_{j}$ is the effective 
-fraction of delayed neutrons at $j$$^{th}$ step. $N$ is the number of steps.
+after and before CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the effective 
+fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:
 
@@
 \label{Equ:4}
-{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}},
+{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
 \end{equation}
 
-Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where 
-$Z$ is the coordinate of the bottom of the control rod.
+Equation~\ref{Equ:5} is used to calculate the differential CRW, where 
+$Z$ is the coordinate of the bottom of the control rod:
 
@@
 \label{Equ:5}
-\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}},
+\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
 \end{equation}

### 2020-03-24 paper/conclusion.tex
after Prof. Huff's comments

@@
 \section{Conclusion} \label{Conclusion}
-In the current work, we introduced design of a reactivity control system for the 
+In the current work, we proposed a reactivity control system design for the 
 Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
-design has been evaluated at the startup for the full-core geometry using 
-SERPENT-2 Monte-Carlo code. We considered three various startup compositions of 
+design has been evaluated at the startup for the full-core geometry using the
+SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions of 
 the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
 (2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
-$^{232}$Th and TRU vector, extracted from \gls{LWR} \gls{SNF}.
+$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.
 
@@
 transient analysis, which will be performed using Moltres 
-\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
-simulation with taking into account the neutron precursors drift.
+\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
+simulation which takes into account the neutron precursors drift.
 

### 2020-03-24 paper/introduction.tex
after Prof. Huff's comments

@@
 The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
-systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
+systems for further research and commercialization: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
 Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
@@
 The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
-centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
-ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
-The MSR is a promising technology because of its dynamics, especially for 
+centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
+ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity} since
+the MSR is a promising technology because of its dynamics, especially for 
 thorium fuel utilization. However, this technology has difficulties in safety, 
 online reprocessing, and fuel handling. Safety is one of the primary goals of 
-the MSR system, which was understudied and requires further investigation. The 
-unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
-etc.) strongly affect its control system design. Graphite-moderated MSRs have 
+the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case.
+The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
+etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
+core reactivity when the core heats up, thus, graphite-moderated MSRs have 
 a negative total temperature coefficient of reactivity 
 \cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
-Doppler effect and thermal expansion of the fuel reduce core reactivity when 
-the core heats up. MSR designs have drain tanks to 
-hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
+MSR designs have drain tanks to 
+hold and cool down the liquid fuel in an emergency. In most MSR design concepts, a freeze plug, which 
 is located under the core, passively melts when the fuel temperature reaches a 
@@
 
-At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
+At the Beginning of Life (BOL), MSRs are commonly loaded with more
 fuel than that required to achieve criticality (necessary for long-term core 
 operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
-at the BOL is large for many refueling scenarios 
-\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
-Additionally, during burnup, the online 
-reprocessing and refueling leads to slow reactivity change, which 
-should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
-The online reprocessing and refueling system helps to control the reactivity of 
+at the BOL is large for many refueling scenarios and may reach $\approx$ $8100$ $pcm$
+\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
+Additionally, during burnup, online reprocessing and refueling system helps to control the reactivity of 
 the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
@@
 \cite{duderstadt650nuclear}. 
-Insertion of control rods introduces an amount of negative reactivity into the 
-core. This negative reactivity helps to compensate the excess reactivity and 
+Insertion of control rods introduces negative reactivity into the 
+core which helps to compensate the excess reactivity and 
 adjust the power level of the core or shut down the reactor in case of 
@@
 the necessary absorption cross section.
-Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan
+Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the absorption ability under irradiation, and swelling limit the B$_4$C lifespan
 \cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
 potential alternative absorbers for Generation-IV reactors such as 
-hafnium-based materials and rare earth element oxides. These absorbers have 
+hafnium-based materials and rare earth oxides. These absorbers have 
 high thermal conductivity, good resistance to neutron irradiation, and
-almost no gas release (absorbing neutrons mainly through (n,$\gamma$) reactions)
+absorb neutrons mainly through (n,$\gamma$) reactions
 \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
 
-The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
+The SD-TMSR with a thermal power of 2,250 MW$_{th}$ 
 \cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
@@
 the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}.
-However, a reactivity control system for maneuvering and emergency shutdown has not been introduced in literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
-Therefore, the main objective of our study is to introduce a new
-fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
+However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
+Therefore, the main objective of our study is to introduce a new,
+rapid reactivity control system based on control rods in the SD-TMSR to control 
 the reactivity during normal operation and shut down the reactor in case of 
-emergency. Six different absorbing materials are 
-applied to study the main neutronics and safety parameters in the SD-TMSR. We 
-focus on the control rod design, absorption ability, integral and differential 
-control rod worths, shutdown margin of absorbing materials, and shadowing 
+emergency. Six absorbing material options are considered in the context of the 
+neutronics and safety parameters in the SD-TMSR. We 
+focus on control rod design, absorption ability, integral and differential 
+control rod worths, shutdown margin, and shadowing 
 effects at steady state calculation.
 
+Xuemei \emph{et al.} (2013) calculated the control worth in the thorium molten salt
+reactor by using MCNP5 \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
+core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which
+is different from the Molten Salt Breeder Reactor-like geometry by Mathieu \emph{et al.}
+\cite{mathieu2006thorium} adopted by Xuemei \emph{et al.} \cite{xuemei2013study}.
+Additionally, Xuemei \emph{et al.} studied the natural B$_4$C as absorbing material
+while we considered six different absorbing materials.
+
 \v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
-GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes 
+GFR. They utilized the MCNP5 and KENO6 codes 
 \cite{petrie1984keno} to calculate the reactivity worth and analyze the 
 performance of this control system \cite{vcerba2017optimization}. Since no
-final geometry design of the control rods system is available for the SD-TMSR, 
+geometry design of the control rods system is available for the SD-TMSR, 
 \v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting 
@@
 
-This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.
+This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

### 2020-03-24 paper/methods.tex
after Prof. Huff's comments

@@
 
-The Chinese Academy of Sciences proposed the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design in 2011
+The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
-\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
-of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
+SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
+of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
 \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
@@
 positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
-described in detail the \gls{SD-TMSR} core geometry
+described in detail the SD-TMSR core geometry
 \cite{li_optimization_2018,ashraf2020whole}. The core of the 
-\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
-and the outer zone (522 fuel tubes) to enhance breeding performance.
+SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
+and an outer zone (522 fuel tubes) to enhance breeding performance.
 
-In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
-12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
+In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
+where HM is the heavy metal (i.e. $^{232}$Th and fissile 
 materials), and $N$ depends on the chosen fissile material and the 
@@
 The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
-respectively. The liquid fuel salt circulates continuously through the fuel 
-tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
+respectively. The liquid fuel salt circulates continuously through the channels
+that pierce the graphite hexagonal prisms. The core is surrounded by 
 axial and radial graphite reflectors to minimize the neutron leakage.
 A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
-Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
-a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
+Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
+a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
 summarized in Table~\ref{tab:table1}.
@@
 		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
-		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
+		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\
 		Graphite density, g/cm$^3$             	    & 2.3	\\  
-		B$_4$C density, g/cm$^3$					& 2.52  \\ 
 		Core diameter, cm								& 460  \\
@@
 		Outer radius, cm							& 5  \\
-		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
-		Ratio of molten salt and graphite in the outer zone &  1.162  \\
+		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
+		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\
 		Fuel volume, m$^3$  &	52.9 \\
+		B$_4$C density, g/cm$^3$  &  2.54 \\
+		HfB$_2$ density, g/cm$^3$  &  10.5 \\
+		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
+		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
+		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
+		SiC density, g/cm$^3$  & 3.21 \\
+		AIM1 cladding density, g/cm$^3$  & 7.987 \\
 		\hline
@@
 
-The reactivity of the SD-TMSR core is controlled by two clusters of control 
-rods:
+The present paper proposes two sets of rods to control the reactivity of the SD-TMSR core:
 \begin{enumerate}
@@
 \item natural B$_4$C (19.9\% $^{10}$B);
-\item B$_4$C with boron enriched to 90\% $^{10}$B;
+\item B$_4$C (enriched to 90\% $^{10}$B);
 \item hafnium diboride (HfB$_2$);
@@
 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
-SiC structural material (see Figure~\ref{fig:cr}). We simulated a small gap between the 
+SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.04-cm-thick gap between the 
 cladding and guide tube to facilitate the control rod movement.
+All densities of rod materials are listed in
+Table~\ref{tab:table1}.
 
-Since the total number and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis.
-We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
-Every four control rods (cluster) can move together as one group.
-Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
-The total number of graphite elements with control rods are 25: 16 CSD and 9 SSD.
-\begin{figure}[t!]  % replace 't' with 'b' to \centering
+\begin{figure}[b!]  % replace 't' with 'b' to \centering
 	\centering
@@
 \end{figure}
+
+Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, we propose an original distribution as a starting point of this analysis.
+We added clusters consisting of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core.
+Every four control rods can move together as one group (cluster).
+Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
+We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).
+
 \begin{figure}[t!]  % replace 't' with 'b' to \centering
@@
 	\includegraphics[width=\textwidth]{core_25.png}
-	\caption{Distribution of the graphite elements with CRs in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
+	\caption{Distribution of the graphite elements with CRs in the SD-TMSR core.}
 	\label{fig:core_25}
@@
 for all calculations in the present work. The results demonstrate whole-core 
-runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles. The 
-statistical error in $k_{eff}$ from the SERPENT-2 output is $\leq$ $25$ 
+runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and
+statistical error in $k_{eff}$ of $\leq$ $25$ 
 $pcm$.
@@
 Interference between control rods (CRs) or shadowing effects occur when one 
-(or more) control rod affects the reactivity worth of another control rod in 
+(or more) control rod impacts the reactivity worth of another control rod in 
 the surroundings. Thus, the shadowing effect appears when the combined rod worth
-is less than the sum of the individual worths. Oppositely, anti-shadowing is observed 
+is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
 when the combined rod worth is greater than the sum of the individual worths.
@@
 
-The amplification factor (A$_{CRi}$) of the i$^{th}$ CR helps to evaluate the shadowing effects between CR clusters.
+The amplification factor of the i$^{th}$ CR (A$_{CRi}$) helps to evaluate the shadowing effects between CR clusters.
 The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:
@@
 
-If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1 the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.
+If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.
 
@@
 The integral CRW is the total reactivity change due to the full 
-insertion or withdrawal of the CR. However, the differential CRW is the amount of 
+insertion or withdrawal of the CR. However, the \textit{differential CRW} is the
 reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
@@
 fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
-[\$], where $k_{j}$ and $k_{j-1}$ are the effective multiplication factor 
-after and before CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the effective 
+[\$], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
+before and after CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the
 fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:
@@
 Equation~\ref{Equ:5} is used to calculate the differential CRW, where 
-$Z$ is the coordinate of the bottom of the control rod:
+$\Delta Z$ is the length of rod inserted:
 

### 2020-03-24 paper/results.tex
after Prof. Huff's comments

@@
 
-\subsection{The excess reactivity $\rho$$_e$}
+\subsection{Excess reactivity}
 
@@
 calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
-reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
-$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
+reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
 The previously studied $^{233}$U case recorded the maximum reactivity
@@
 	\vspace{-0.5in}
-	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.}
+	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.}
 	\label{fig:keff_25}
 \end{figure}
+
+Table~\ref{tab:excess}
+
+\begin{table}  %[!hb]
+	\caption{The excess reactivity for the SD-TMSR core with different initial fissile materials.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{3cm} s s s}
+		\hline
+		Initial fissile materials       				&  $^{233}$U & reactor-grade Pu&  TRU \\
+		\hline
+		$\rho_e$					& $1.65\pm0.04$ $\$$ & $4.11\pm0.02$ $\$$ & $15.38\pm0.04$ $\$$ \\
+		\hline
+	\end{tabularx}
+	\label{tab:excess}
+\end{table}
 
@@
 
-The total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
+Among the absorbers investigated, the total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
 $\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
@@
 
-The worth of the CSD clusters is $1.56$ times greater than 
-the worth of the SSD system for all absorbing materials. Either CSD or SSD 
+The worth of the Control Safety Devices (CSD) clusters is $1.56$ times greater than 
+the worth of the Shutdown Safety Devices (SSD) system for all absorbing materials. Either CSD or SSD 
 clusters are able to shut down the reactor initially loaded by 
-$^{233}$U and reactor-grade Pu regardless of the absorbing material type because 
-the $\rho_e$ for $^{233}$U and reactor-grade Pu as initial fissile material are $1.65\pm0.04$ 
-$\$$ and $4.11\pm0.02$ $\$$, respectively. However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
-initially loaded with transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$). The reason for this is the much larger 
+$^{233}$U and reactor-grade Pu regardless the absorbing material type.
+However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
+initially loaded by transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$).
+The reason for this is the much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 In case of malfunction of other CR clusters (e.g., stuck in the upper 
-position), the outer ring of the CSD failed to compensate the excess 
-reactivity of the core initially loaded by reactor-grade Pu and TRU elements. However, the outer ring of the CSD worth is sufficient 
-to compensate the excess reactivity for the core refueled by $^{233}$U.
+position), the outer ring of the CSD will be able to compensate the excess reactivity of the core initially loaded by $^{233}$U.
+Meanwhile, it will fail to compensate the excess 
+reactivity of the core initially loaded by reactor-grade Pu and TRU elements.
 
-We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters to 
-investigate the variation of CRW with the position in the inner core.
+We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (CR clusters located in the center and at the boundary between the core
+zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
 The CRW decreases in the direction of the outer core zone. The outer core zone 
@@
 ($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
-zone than in the center of the core. As mentioned previously, the CR's 
-absorption ability degrades in the fast spectrum.
+zone than in the center of the core degrading the CR's 
+absorption ability in that region.
 
@@
 ($<250$ cm from the upper boundary of the core). Further insertion of the 
-CRs shows the unique absorption characteristics of each material (see 
-part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
-Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
-materials in this study. Notably, all results are based on steady state calculations.
+CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
+Notably, all results are based on steady state calculations.
 
@@
 	\vspace{-0.5in}
-	\caption{Integral CRW of CSD clusters for different absorbing materials.} 
+	\caption{Integral CRW of CSD clusters for various absorbing materials.} 
 	\label{fig:CSD}

### 2020-03-25 paper/introduction.tex
after Andrei's comments

@@
 operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
-at the BOL is large for many refueling scenarios and may reach $\approx$ $8100$ $pcm$
+at the BOL must be large (up to $8.1$\%) for many refueling scenarios
 \cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
-Additionally, during burnup, online reprocessing and refueling system helps to control the reactivity of 
+Additionally, during burnup, online reprocessing and refueling system as long-term reactivity control in
 the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
@@
 Xuemei \emph{et al.} (2013) calculated the control worth in the thorium molten salt
-reactor by using MCNP5 \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
+reactor by using MCNP \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
 core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which
@@
 \v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
-GFR. They utilized the MCNP5 and KENO6 codes 
+GFR. They utilized the MCNP \cite{briesmeister2000mcnptm} and KENO6 codes 
 \cite{petrie1984keno} to calculate the reactivity worth and analyze the 
@@
 
-This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.
+This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on calculated control rod parameters such as integral and differential worth, shutdown margin (SDM), and amplification factors, and section \ref{Conclusion} highlights the conclusions.

### 2020-03-25 paper/methods.tex
after Andrei's comments

@@
 described in detail the SD-TMSR core geometry
-\cite{li_optimization_2018,ashraf2020whole}. The core of the 
+\cite{li_optimization_2018,ashraf2020whole}. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
+SD-TMSR. The core of the 
 SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
 and an outer zone (522 fuel tubes) to enhance breeding performance.
-
+\begin{figure} % replace 't' with 'b' to \centering [hbp!]
+	\includegraphics[width=\textwidth]{ff.png}
+	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
+		SD-TMSR \cite{ashraf2019Preliminary}.}
+	\label{fig:ff}
+\end{figure}
 In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
@@
 		Fuel temperature, K 							& 900  \\
+		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
+		Fuel volume, m$^3$  &	52.9 \\
 		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
-		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\
 		Graphite density, g/cm$^3$             	    & 2.3	\\ 
-		Core diameter, cm								& 460  \\
-		Core height, cm									& 460  \\
-		Side length of the graphite hexagonal prism, cm   & 7.5 \\
-		Inner radius, cm							& 3.5  \\
-		Outer radius, cm							& 5  \\
-		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
-		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\
-		Fuel volume, m$^3$  &	52.9 \\
 		B$_4$C density, g/cm$^3$  &  2.54 \\
@@
 		AIM1 cladding density, g/cm$^3$  & 7.987 \\
+		Core diameter, cm								& 460  \\
+		Core height, cm									& 460  \\
+		Side length of the graphite hexagonal prism, cm   & 7.5 \\
+		Radius (inner fuel channel), cm							& 3.5  \\
+		Radius (outer fuel channel), cm							& 5  \\
+		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
+		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\
+
 		\hline
@@
 
-\begin{figure}[b!]  % replace 't' with 'b' to \centering
+\begin{figure}[t!]  % replace 't' with 'b' to \centering
 	\centering
@@
 (or more) control rod impacts the reactivity worth of another control rod in 
-the surroundings. Thus, the shadowing effect appears when the combined rod worth
+the surroundings. 
+The insertion of a CR depresses the neutron flux
+in its vicinity and makes the curvature of the neutron flux greater. The gradient
+of the neutron flux will contrarily increase at a radial distance. The CRs, distributed in the core,
+will distort the neutron flux around each other and will impact the reactivity worth.
+The term ``shadowing effect" has been used to describe this \cite{oka2014nuclear}.
+The shadowing effect appears when the combined rod worth
 is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
 when the combined rod worth is greater than the sum of the individual worths.
-The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
-of the CRs affect the degree of the interference between CRs \cite{girardin2007control}.
+The core height-to-diameter ratio (H/D), CR locations, and the three-dimensional configuration 
+of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear,girardin2007control}.
 
@@
 
-If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.
+If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur \cite{girardin2007control}.
+A$_{CRi}$ = 1 means no shadowing effects occur.
 

### 2020-03-25 paper/cover-letter/cover-letter.tex
cover letter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
% It was modified by Katy Huff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10.75pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\usepackage{eso-pic,graphicx}

%--------------------------------------------------------------------------------------
%--------INPUT DATA
%--------------------------------------------------------------------------------------
\usepackage{xspace}
\newcommand{\StudentFirstName}{O.\xspace}
\newcommand{\StudentLastName}{Ashraf\xspace}
\newcommand{\RecipientName}{Profs. Azmy, Joyce, and Su\xspace}
\newcommand{\RecipientAddress}{Executive Editor\\Progress in Nuclear Energy}
%\newcommand{\<++>}{<++>\xspace}

\begin{document}
	\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

	%----------------------------------------------------------------------------------------
	%    ADDRESSEE SECTION
	%----------------------------------------------------------------------------------------

	\begin{letter}{\RecipientName\\
			\RecipientAddress\xspace}

		%-------------------------------------------------------------------------------
		%    YOUR NAME & ADDRESS SECTION
		%-------------------------------------------------------------------------------
		\address{O. Ashraf\\
			oabdelaziz@mephi.ru\\
			osama.ashraf@edu.asu.edu.eg\\
			Institute of Nuc. Physics and Eng.\\
			National Research Nuclear University\\
			Moscow, Russia, 115409}

		%-------------------------------------------------------------------------------
		%    LETTER CONTENT SECTION
		%-------------------------------------------------------------------------------

		\opening{To \RecipientName,}

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR). Part I: Design development, material selection, and worth analysis'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Progress in Nuclear Energy. The current manuscript is the first part of the two-part series that introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. Part I focus on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state. Meanwhile, Part II will focus on control rod worth evolution during operation. We intended to submit Part II on June-July, 2020.

		In the present paper, all calculations presented were performed using Monte-Carlo code SERPENT-2. We considered three different initial fissile loadings and applied six different absorbing materials to investigate the main operational and safety parameters in the SD-TMSR. Result showed that $^{233}$U and reactor-grade Pu startup cores maintain adequate shutdown margin with all considered absorbers. Finally, this paper proposes a design of control rod clusters that compensate the excess reactivity of the SD-TMSR loaded with different initial fissile material.

		Thank you for your consideration of our work. I expect it will be of interest
		to a broad readership concerned with simulation of MSRs.\\

		%Declarations of interest: none\\

		\closing{Sincere regards,
			\includegraphics[height=1.3cm]{signature.png}\\
			\fromsig{O. Ashraf\\
				Assistant Teacher\\
				Institute of Nuc. Physics and Eng.\\
				National Research Nuclear University (MEPhI)}
		}

		%-------------------------------------------------------------------------------

	\end{letter}

\end{document}

### 2020-03-25 paper/conclusion.tex
before submission

@@
 design has been evaluated at the startup for the full-core geometry using the
-SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions of 
-the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
+SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
+(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
 (2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
@@
 absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
-the other absorbing materials in this study. Both CSD and SSD clusters are 
+the other absorbing materials in this study. Both Control Safety Devices (CSD)
+and Shutdown Safety Devices (SSD) clusters are 
 separately able to shut down the reactor initially loaded with $^{233}$U and 
@@
 clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
-with TRU vector from \gls{LWR}. The reason for this is the much larger 
+with TRU from \gls{LWR}. The reason for this is the much larger 
 absorption cross section of $^{10}$B in the relatively soft neutron energy 
@@
 shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
-case), this makes the SSD clusters unreliable to shut down the reactor loaded 
-with TRU because the SSD clusters should provide a sufficient positive shutdown margin.
+case).
 

### 2020-03-25 paper/results.tex
before submission

@@
 \end{figure}
-
-Table~\ref{tab:excess}
 
@@
 
-We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (CR clusters located in the center and at the boundary between the core
+We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e. clusters located in the center and at the boundary between the core
 zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
@@
 
-The SSD clusters are designed mainly for an emergency shutdown, thus it should 
+The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should 
 provide the reactor core with sufficient negative reactivity. The 
@@
 
-\begin{table}  [!hb]
+\begin{table}  %[!hb]
 	\caption{The SDMs for the SD-TMSR core for different absorbing materials.}
@@
 material type and the interference between the CR clusters
-(i.e., the A$_{CRi}$).
+(i.e. the A$_{CRi}$).
 
@@
 
-Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with six 
+Figure~\ref{fig:CSD} shows the integral CRW for only Control Safety Devices (CSD) clusters with six 
 different absorbing materials. The results show that all absorbing materials 

### 2020-03-25 paper/introduction.tex

@@
 centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
-ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity} since
-the MSR is a promising technology because of its dynamics, especially for 
-thorium fuel utilization. However, this technology has difficulties in safety, 
+ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}
+thanks to its advantages, for example, thorium fuel utilization, small waste production, and ability to use spent fuel.
+However, this technology has difficulties in safety, 
 online reprocessing, and fuel handling. Safety is one of the primary goals of 
@@
 operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
-at the BOL must be large (up to $8.1$\%) for many refueling scenarios
-\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
-Additionally, during burnup, online reprocessing and refueling system as long-term reactivity control in
+at the BOL may vary from 1.2 \% for $^{233}$U-loaded core \cite{ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling} to 8.1 \% for Pu/TRU-loaded core \cite{ashraf2020Strategies,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
+Additionally, online reprocessing and refueling system is designed to operate as long-term reactivity control in
 the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 

### 2020-07-17 paper/conclusion.tex
After Osama's changes

@@
 burnup on the CRW. The depleted fuel composition will be obtained using a
-SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
-batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
-rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
+SERPENT-2 online reprocessing subroutine and 
+batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
 kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 

### 2020-07-17 paper/introduction.tex
After Osama's changes

--- 2020-03-25 paper/introduction.tex
@@
 centers are pursuing MSRs with renewed interest \cite{betzler_impacts_2019, 
-ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity} since
-the MSR is a promising technology because of its dynamics, especially for 
-thorium fuel utilization. However, this technology has difficulties in safety, 
+ashraf2020whole}
+due to its potential advantages, for example, thorium fuel utilization, small waste production, and ability to use spent fuel.
+However, this technology has difficulties including safety, 
 online reprocessing, and fuel handling. Safety is one of the primary goals of
@@
 etc.) strongly affect its control system design. Doppler effect and thermal expansion of the fuel reduce
-core reactivity when the core heats up, thus, graphite-moderated MSRs have 
-a negative total temperature coefficient of reactivity 
-\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
+core reactivity when the core heats up, thus MSRs have negative total temperature coefficient of reactivity 
+\cite{nuttin2005potential}.
 MSR designs have drain tanks to 
-hold and cool down the liquid fuel in an emergency. In most MSR design concepts, a freeze plug, which 
+hold and cool down the liquid fuel in an emergency. In some MSR design concepts, a freeze plug, which 
 is located under the core, passively melts when the fuel temperature reaches a 
@@
 fuel than that required to achieve criticality (necessary for long-term core 
-operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
-at the BOL must be large (up to $8.1$\%) for many refueling scenarios
-\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
-Additionally, during burnup, online reprocessing and refueling system as long-term reactivity control in
-the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
-to control the reactor is to insert or withdraw control rods made of material 
-with a large neutron absorption cross section (e.g., boron, cadmium) 
-\cite{duderstadt650nuclear}. 
+operation); this leads to excess reactivity at the BOL.
+Robertson (1971) assumed small excess reactivity for \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel, thus only 2 control (graphite) rods for adjusting reactivity and 2 safety (B$_4$C) rods for emergency shutdown were suggested \cite{robertson_conceptual_1971}.
+However, scientists are concerned about $^{233}$U supply, since it does not exist anywhere.
+Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required.
+Betzler \emph{et al.} (2017) also reported large excess reactivity to operate Transatomic Power Molten Salt Reactor (TAP MSR) for a long time \cite{betzler2017assessment}.
+Additionally, Rykhlevskii \emph{et al.} (2019) studied the fuel cycle performance for various designs of the \gls{MSFR}.
+For MSFRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}.
+Recent studies on MSRs showed that the excess reactivity
+at the BOL may vary from 1.2 \% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1 \% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.
+
+The online reprocessing and refueling system is designed to operate as long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}.
+However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its clones.
+Consequently, we need a prompt reactivity control system for emergencies.
+The most common and reliable procedure to control the reactor is to insert or withdraw control rods made of material with a large neutron absorption cross section (e.g., boron).
 Insertion of control rods introduces negative reactivity into the 
@@
 adjust the power level of the core or shut down the reactor in case of 
-emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
-the reactivity worth of the control rods 
-\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
+emergency. Therefore, we should estimate 
+the reactivity worth of the control rods.
 The reactivity worth of control rods correlates with the interference 
 (shadowing effects) between control rod clusters 
-\cite{girardin2008development,vcerba2017optimization}. 
-The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.
+\cite{vcerba2017optimization}. 
+The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{atkinson2019small}.
+Additionally, Nuclear Regulatory Commission (NRC) regulation requires that one of the reactivity control systems use control rods \cite{nuclear1987standard}.
 
-Boron carbide (B$_4$C) is a commonly used material for the control rods 
-\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
+Boron carbide (B$_4$C) is a commonly used material for the control rods; 
 however, we may need to enrich the boron isotope ($^{10}$B) to reach 
@@
 absorb neutrons mainly through (n,$\gamma$) reactions
-\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.
+\cite{guo2019optimized}.
 
 The SD-TMSR with a thermal power of 2,250 MW$_{th}$ 
-\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
+\cite{li_optimization_2018} is a graphite-moderated 
 molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
-the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}.
-However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}.
+the SD-TMSR \cite{ashraf2020Strategies,li_optimization_2018}.
+However, a reactivity control system for maneuvering and emergency shutdown in the SD-TMSR has not been introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity}.
 Therefore, the main objective of our study is to introduce a new,
@@
 
+The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors.
+Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those of startup.
+The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing.
+Therefore, the worth of the control rods should be corresponding to the reprocessing scheme; that is, the rate of extraction and addition of elements.
+However, the present work focuses on the steady state calculations (i.e.
+without burnup).
+
 All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.

### 2020-07-17 paper/methods.tex
After Osama's changes

@@
 
-The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
-\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
-SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
-of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
-\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
-\cite{nuttin2005potential} after modifying the geometry to control the 
-positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
-described in detail the SD-TMSR core geometry
-\cite{li_optimization_2018,ashraf2020whole}. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
+The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}.
+Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$.
+The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum.
+The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR.
+Figure~\ref{fig:ff} illustrates the quarter-core view of the
 SD-TMSR. The core of the 
@@
 		Graphite density, g/cm$^3$             	    & 2.3	\\ 
-		B$_4$C density, g/cm$^3$  &  2.54 \\
-		HfB$_2$ density, g/cm$^3$  &  10.5 \\
-		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
-		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
-		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
-		SiC density, g/cm$^3$  & 3.21 \\
-		AIM1 cladding density, g/cm$^3$  & 7.987 \\
 		Core diameter, cm								& 460  \\
@@
 
-The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
+\begin{figure}[t!]  % replace 't' with 'b' to \centering
+	\centering
+	\hspace{+0.65in} 
+	\includegraphics[width=\textwidth]{Radius.png}
+	\caption{The change of the effective multiplication factor with the radius of the B$_4$C control rod.}
+	\label{fig:Radius}
+\end{figure}
+
+The assessment of the optimal absorber radius should be an important consideration.
+If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding.
+We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted.
+Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod.
+As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius.
+However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$.
+This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
+From the obtained results, the control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
 The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
-SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.04-cm-thick gap between the 
+SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
 cladding and guide tube to facilitate the control rod movement.
 All densities of rod materials are listed in
-Table~\ref{tab:table1}.
+Table~\ref{tab:table111}.
+
+\begin{table}
+	\caption{The densities of the absorbing materials.}
+	\vspace{0.05in}
+	\begin{center}	
+		\begin{tabular}{|l | r|}  %[!ht]
+			%%	\begin{tabularx}{\textwidth}{l | r}
+			\hline
+			Absorbers & Density [g/cm$^3$]\\
+			\hline
+			B$_4$C   &  2.54 \\
+			HfB$_2$   &  10.5 \\
+			HfH$_{1.62}$  &  11.4 \\
+			Gd$_2$O$_3$   &  7.04 \\
+			Eu$_2$O$_3$  &  7.38 \\
+			SiC   & 3.21 \\
+			AIM1 cladding   & 7.987 \\
+			\hline
+			%	\end{tabularx}
+		\end{tabular}
+		\label{tab:table111}
+	\end{center}
+\end{table}
+
+%From the figure it can be seen that in the outer region of the B4C
+%absorber, the flux is degraded rapidly, but in the region between 0 and 2 cm there is almost no change of the neutron flux.
+This phenomenon can be explained by the geometry self-shielding of the neutron flux.
+Due to absorption of low energy neutrons at the outside region ofthe absorber pin, the radius ofthe investigated pin is significantly larger than the penetration distance of the neutrons in the absorber.
+Therefore, the 10B atoms in the central part of the pin have no reasonable chance for neutron capture.
+Based
+%
+%
+%On the basis of the obtained results the 5 ring configuration was selected for further
+%ness (low self-shielding) and simplicity. On the basis of the obtained results the 5 ring configuration was selected for further
+%analyses.
+%
+%This CR design consists of 61 absorber pins. Using Eq. (6) the radius of the absorber pins was calculated to 0.574 cm.
+%
+%In terms of neutronics, we an appropriate way to find the optimal pin radius could be the investigation of the neutron penetration distance, performed on a simple absorber pin.
+%
+%A single-pin design is a semi 1D approach preventing any interference caused by the self-shielding or geometrical influences of the surrounding absorber pins.
 
@@
 Every four control rods can move together as one group (cluster).
-Figures~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods.
+Figure~\ref{fig:graphite_elemen} demonstrates the plan view of the graphite element with the control rods.
 We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).
@@
 \end{figure}
-\begin{figure}[t!]  % replace 't' with 'b' to \centering
-	\centering
-	\hspace{+0.65in}
-	\includegraphics[width=\textwidth]{graphite_element1.png}
-	\caption{$XZ$ section of graphite element with control rods.}
-	\label{fig:graphite_elemen1}
-\end{figure}
+%\begin{figure}[t!]  % replace 't' with 'b' to \centering
+%	\centering
+%	\hspace{+0.65in}
+%	\includegraphics[width=\textwidth]{graphite_element1.png}
+%	\caption{$XZ$ section of graphite element with control rods.}
+%	\label{fig:graphite_elemen1}
+%\end{figure}
 
@@
 the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
-for all calculations in the present work. The results demonstrate whole-core 
-runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and
-statistical error in $k_{eff}$ of $\leq$ $25$ 
-$pcm$.
+for all calculations in the present work.
+The results demonstrated in this study were obtained after full-core calculations simulating 25$\times$10$^6$ active neutron histories per cycle.
+Simulations consisted in 500 active cycles of 5$\times$10$^4$ neutrons subdivided in 8 parallel tasks.
+Each simulation skipped 50 inactive cycles before beginning active tallies to allow for the convergence of the fission source distribution.
+Convergence has been checked through the fission source entropy.
+The statistical error in $k_{eff}$ was $\leq$ $25$ $pcm$.
+
+%The results demonstrate whole-core runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles, and statistical error in $k_{eff}$ of $\leq$ $25$ $pcm$.
+%
+%Simulations consisted in 500 active cycles of 2∙104 neutrons. 20 inactive cycles were used for the convergence of the
+%fission source distribution.
+%
+%Each simulation in this study skipped 200 generations before beginning active tallies to ensure fission source convergence.
+%
+%In order to minimize statistical errors and assure reliable fission source convergence, up to 2000 active fission source iteration cycles with 150,000 histories per cycle were used in neutron transport calculations with MCNP
+%
+%The MCNP transport step within the VESTA simulation uses 300 active cycles, 50 inactive cycles,
+%and 100,000 particles per cycl
+%
+%The fission source defined in Serpent Code automatically dis-
+%tributes the initial guess in fuel zones, with enhances the overall performance.
+Besides, the number of histories was selected to get the intended statistical convergence, considering the computa- tional effort involved.
+Accordingly, the following scheme was selected:
+%?
+A Source with v3 ?
+108 histories was selected for all cases where CRW is calculated in order to reach a statistical uncer- tainty of v5 pcm at 1 r for each calculation and a final value of CRW uncertainty below 5%.
+%? A Source with v2 ? 107 histories was selected for all burnup cases in order to reach a statistical uncertainty of v20 pcm at 1 r for each calculation.
+%3.3.
+%
+%The results presented in the following were obtained after full-core calculations simulating 250 million active neutron histories with the version 1.1.16 of the code.
+Simulations consisted in 500 active cycles of 5∙105 neutrons subdivided in 16 parallel tasks.
+Seventy inactive cycles were adopted to allow for the convergence of the fission source distribution.
+Convergence has been checked through the fission source entropy.
+Results
 
@@
 
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}.
+The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.
 
@@
 The shutdown margin (SDM) is the amount of reactivity by which a full reactor core is subcritical from a given state.
+The Shutdown Safety Devices (SSD) clusters are designed mainly for an emergency shutdown, thus it should
+provide the reactor core with sufficient negative reactivity.
 The SDM is expressed in terms of reactivity and calculated by equation~\ref{Equ:6}, where $\Delta\rho_{SSD}$ is the total worth of the Shutdown Safety Devices (SSD) and $\rho$$_e$ is the core excess reactivity:
@@
 The core height-to-diameter ratio (H/D), CR locations, and the three-dimensional configuration 
-of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear,girardin2007control}.
+of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear}.
 
 The amplification factor of the i$^{th}$ CR (A$_{CRi}$) helps to evaluate the shadowing effects between CR clusters.
-The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{girardin2007control,vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:
+The A$_{CRi}$ is calculated by equation~\ref{Equ:3} \cite{vcerba2017optimization}, where $\Delta\rho$$_{CR(1,2,\ldots N)}$ is the total worth of all CRs (from $1$ to $N$), $\Delta\rho$$_{CR(1,2,\ldots N-i)}$ is the total worth of all CRs except the i$^{th}$ rod, and $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ rod:
 

### 2020-07-17 paper/results.tex
After Osama's changes

@@
 between CR clusters, and integral and differential control rod worths are 
-described in this part. 
-Table~\ref{tab:worth} shows calculated CRW, the amplification 
-factor (A$_{CRi}$), and the type of interference for six different 
-absorbers.
+described in this part. Table~\ref{tab:worth} shows calculated CRW and the amplification 
+factor (A$_{CRi}$) for six different 
+absorbers. The types of interference for all different 
+absorbers are listed in Table ~\ref{tab:table25}.
+Fuel salt composition of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ at 70-17.5-12.3-0.2 mole\% is used to generate the results listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}.
+\begin{sidewaystable}
+	\fontsize{5}{7}\selectfont
+	\centering
+	\caption{The control rod worth for different CR 
+		materials.}
+	\vspace{1ex}
+	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
+			p{1cm}|p{1cm}|p{1cm}|p{1cm}| 
+			p{1cm}|p{1cm}|p{1cm}|p{0.9cm}|}
+		\hline
+		\multirow{2}{*}{Control Rod group}		& 
+		\multicolumn{2}{c|}{Nat. B$_4$C} & \multicolumn{2}{c|}{B$_4$C-90}   	&\multicolumn{2}{c|}{HfB$_2$}	
+		&\multicolumn{2}{c|}{HfH$_{1.62}$} 
+		&\multicolumn{2}{c|}{Gd$_2$O$_3$}	& 	
+		\multicolumn{2}{c|}{Eu$_2$O$_3$} \\
+		\cline{2-13}
+		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	
+		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  \\
+		\hline                   
+		All control rods      &  $42.04\pm0.60$	&	& $48.19\pm0.68$   &		
+		&$40.40\pm0.41$	&		&$37.96\pm0.36$	&		&$33.70\pm0.40$	&	
+			&$42.39\pm0.48$	& 	 \\
+		\hline 
+		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	 			& $25.50\pm0.23$   &$1.24\pm0.01$	 	&$21.90\pm0.17$	&$1.10\pm0.01$	 	&$20.62\pm0.34$	&$1.10\pm0.01$	 	&$18.48\pm0.25$	&$1.17\pm0.01$	 	&$22.96\pm0.18$	&$1.20\pm0.01$   \\
+		\hline 
+		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	 	&$16.39\pm0.11$ &$1.38\pm0.02$	 	&$14.27\pm0.21$	&$1.29\pm0.01$	 	&$13.23\pm0.18$	&$1.30\pm0.06$	 	&$12.00\pm0.20$	&$1.26\pm0.01$	 	&$14.58\pm0.11$	&$1.30\pm0.02$	  \\
+		\hline 
+		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	  &  $18.42\pm0.05$  &$1.60\pm0.04$	 		&$16.29\pm0.29$	&$1.48\pm0.02$	 	&$15.50\pm0.17$	& $1.46\pm0.01$  	&$14.12\pm0.07$	&$1.39\pm0.01$	 	&$16.92\pm0.13$	&$1.50\pm0.01$	  \\
+		\hline 
+		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	     &$2.26\pm0.02$ &$4.21\pm0.07$	 	&$2.10\pm0.06$	&$3.11\pm0.10$ 	&$1.85\pm0.07$	&$3.24\pm0.06$	 	&$1.80\pm0.10$	&$2.54\pm0.14$	 	&$2.14\pm0.05$	&$3.20\pm0.05$	  	\\
+		\hline 
+		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	 			& $2.25\pm0.04$   &$3.69\pm0.16$	 	&$2.24\pm0.05$	&$2.42\pm0.10$	 	&$2.00\pm0.10$	&$2.68\pm0.03$	 	&$1.80\pm0.10$	&$2.55\pm0.20$	 	&$2.19\pm0.12$	&$2.90\pm0.08$	  \\
+		\hline 
+		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	 				& $0.15\pm0.04$   & $10.53\pm0.01$	  	&$0.10\pm0.05$	&$5.10\pm0.05$	 	&$0.05\pm0.01$	&$16.40\pm0.10$	  	&$0.09\pm0.07$	&$5.55\pm0.20$	  	&$0.07\pm0.05$	&$14.00\pm0.10$	  \\
+		\hline
+		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	 	& $4.18\pm0.07$   &$1.59\pm0.08$	 	&$3.95\pm0.13$	&$1.30\pm0.07$	 	&$3.59\pm0.03$	&$1.49\pm0.01$	 	&$3.45\pm0.12$	&$1.40\pm0.08$	 	&$3.91\pm0.06$	&$1.40\pm0.01$  \\
+		\hline 
+		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	 		&  $0.57\pm0.09$  &$7.84\pm0.15$	 	&$0.63\pm0.06$	&$4.40\pm0.10$	 	&$1.00\pm0.05$	&$2.51\pm0.16$	 	&$0.60\pm0.80$	&$3.31\pm0.27$	 	&$0.60\pm0.08$	&$5.10\pm0.28$	  \\
+		\hline
+	\end{tabularx}
+	\label{tab:worth}
+\end{sidewaystable}
 
@@
 	\centering
-	\caption{The control rod worth and shadowing effect for different CR 
-	materials.}
-	\vspace{1ex}
-	\begin{tabularx}{\textwidth}{|p{1.8cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
-	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}| 
-	p{0.56cm}|p{0.5cm}|p{0.49cm}|p{0.56cm}|p{0.5cm}|p{0.49cm}|}
+	\caption{The shadowing effect for different CR materials.}
+	\vspace{0.1in}
+		\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
 		\hline
-		\multirow{2}{*}{Control Rod group}		& 
-		\multicolumn{3}{c|}{Nat. B$_4$C} & \multicolumn{3}{c|}{B$_4$C-90}   	&\multicolumn{3}{c|}{HfB$_2$}	
-		&\multicolumn{3}{c|}{HfH$_{1.62}$} 
-		&\multicolumn{3}{c|}{Gd$_2$O$_3$}	& 	
-		\multicolumn{3}{c|}{Eu$_2$O$_3$} \\
-		\cline{2-19}
-		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference
-		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	& Inter\-ference	
-		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$	& Inter\-ference	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$	& Inter\-ference	
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  &	Inter\-ference \\
+		\multirow{2}{*}{Control Rod group}		& Nat. B$_4$C & B$_4$C-90  	&HfB$_2$
+		&HfH$_{1.62}$
+		&Gd$_2$O$_3$& 	
+		Eu$_2$O$_3$ \\
+		\cline{2-7}
+		&  Interference
+		& Interference	
+		& Interference	
+		& Interference	
+		& Interference
+		& Interference \\
 		\hline                   
-		All control rods      &  $42.04\pm0.60$	&	&		& $48.19\pm0.68$   &	&	
-		&$40.40\pm0.41$	&	&	&$37.96\pm0.36$	&	&	&$33.70\pm0.40$	&	
-		&	&$42.39\pm0.48$	& &	 \\
+	CSD 		&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\
 	\hline 
-		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	&	$\star$				& $25.50\pm0.23$   &$1.24\pm0.01$	&$\star$	&$21.90\pm0.17$	&$1.10\pm0.01$	&$\star$	&$20.62\pm0.34$	&$1.10\pm0.01$	&$\star$	&$18.48\pm0.25$	&$1.17\pm0.01$	&$\star$	&$22.96\pm0.18$	&$1.20\pm0.01$ &$\star$ \\
+	SSD		   &	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\ 
 	\hline 
-		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	&	$\star$	&$16.39\pm0.11$ &$1.38\pm0.02$	&$\star$	&$14.27\pm0.21$	&$1.29\pm0.01$	&$\star$	&$13.23\pm0.18$	&$1.30\pm0.06$	&$\star$	&$12.00\pm0.20$	&$1.26\pm0.01$	&$\star$	&$14.58\pm0.11$	&$1.30\pm0.02$	&$\star$ \\
+	CSD inner ring   &  	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\
 	\hline 
-		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	&$\star$ &  $18.42\pm0.05$  &$1.60\pm0.04$	&$\star$		&$16.29\pm0.29$	&$1.48\pm0.02$	&$\star$	&$15.50\pm0.17$	& $1.46\pm0.01$ &$\star$	&$14.12\pm0.07$	&$1.39\pm0.01$	&$\star$	&$16.92\pm0.13$	&$1.50\pm0.01$	 &$\star$\\
+	CSD outer ring       &	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\     
 	\hline 
-		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	&	$\star$    &$2.26\pm0.02$ &$4.21\pm0.07$	&$\star$	&$2.10\pm0.06$	&$3.11\pm0.10$&$\star$	&$1.85\pm0.07$	&$3.24\pm0.06$	&$\star$	&$1.80\pm0.10$	&$2.54\pm0.14$	&$\star$	&$2.14\pm0.05$	&$3.20\pm0.05$	 &$\star$	\\
+	CSD2			&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$	 \\  
 	\hline 
-		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	&	$\star$				& $2.25\pm0.04$   &$3.69\pm0.16$	&$\star$	&$2.24\pm0.05$	&$2.42\pm0.10$	&$\star$	&$2.00\pm0.10$	&$2.68\pm0.03$	&$\star$	&$1.80\pm0.10$	&$2.55\pm0.20$	&$\star$	&$2.19\pm0.12$	&$2.90\pm0.08$	&$\star$ \\
+	CSD9		&	$\star$$\star$				& $\star$$\star$	&$\star$		&$\star$$\star$			&$\star$$\star$	  &$\star$$\star$		 \\ 	 
 	\hline
-		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	&	$\star$$\star$				& $0.15\pm0.04$   & $10.53\pm0.01$	&$\star$$\star$	&$0.10\pm0.05$	&$5.10\pm0.05$	&$\star$	&$0.05\pm0.01$	&$16.40\pm0.10$	&$\star$$\star$	&$0.09\pm0.07$	&$5.55\pm0.20$	&$\star$$\star$	&$0.07\pm0.05$	&$14.00\pm0.10$	&$\star$$\star$ \\
+	SSD1	&	$\star$				& $\star$	&$\star$		&$\star$		&$\star$  &$\star$ \\	  
 	\hline 
-		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	&	$\star$		& $4.18\pm0.07$   &$1.59\pm0.08$	&$\star$	&$3.95\pm0.13$	&$1.30\pm0.07$	&$\star$	&$3.59\pm0.03$	&$1.49\pm0.01$	&$\star$	&$3.45\pm0.12$	&$1.40\pm0.08$	&$\star$	&$3.91\pm0.06$	&$1.40\pm0.01$&$\star$ \\
-		\hline 
-		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	&	$\star$$\star$		&  $0.57\pm0.09$  &$7.84\pm0.15$	&$\star$$\star$	&$0.63\pm0.06$	&$4.40\pm0.10$	&$\star$	&$1.00\pm0.05$	&$2.51\pm0.16$	&$\star$	&$0.60\pm0.80$	&$3.31\pm0.27$	&$\star$	&$0.60\pm0.08$	&$5.10\pm0.28$	&$\star$$\star$ \\
+	SSD4		&		$\star$$\star$			& 	$\star$$\star$	&$\star$		&$\star$		&$\star$  &	$\star$$\star$	 \\  
 	\hline
@@
 \end{tablenotes}
-	\label{tab:worth}
+	\label{tab:table25}
 \end{sidewaystable}
-
 \subsubsection{CRW} \label{CR_worth}
@@
 greater than in the fast spectrum.
+Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.
 
@@
 anti-shadowing is observed when the combined rod worth is greater than the sum 
-of the individual worths. The strongest anti-shadowing effect occurred in 
+of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
 SSD4 and CSD9 clusters that are located at the boundary between the core zones 
-with different moderator-to-fuel ratios (see Table~\ref{tab:worth}).
-The obtained results emphasize that no relation exists between the absorbing
-material type and the interference between the CR clusters
-(i.e. the A$_{CRi}$).
+with different moderator-to-fuel ratios.
+This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}).
+Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed.
+The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e.
+the A$_{CRi}$).
 
@@
 The differential CRWs are demonstrated in Figure~\ref{fig:diff}.
-Ideally, at the top of the core, the CR insertion has little effect since this region has low thermal neutron flux.
-Thus, the differential CRW has the lowest values in this region.
+Theoretically, at the top of the core, the CR insertion has little effect since this region has low thermal neutron flux.
+Thus the differential CRW has the lowest values in this region.
 The effect of CR insertion increases gradually near the center of the core.

### 2020-07-20 paper/methods.tex
After Andrei's comments

@@
 In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
-where HM is the heavy metal (i.e. $^{232}$Th and fissile 
+where HM is the heavy metal (i.e., $^{232}$Th and fissile 
 materials), and $N$ depends on the chosen fissile material and the 

### 2020-07-20 paper/results.tex
After Andrei's comments

@@
 between CR clusters, and integral and differential control rod worths are 
-described in this part. Table~\ref{tab:worth} shows calculated CRW and the amplification 
+described in this work. Table~\ref{tab:worth} shows calculated CRW and the amplification 
 factor (A$_{CRi}$) for six different 
@@
 operation; the effect of the fuel salt burnup on the CRW is neglected
-herein and will be investigated and presented in Part II of this 
-study.
+herein and will be investigated in future work.
 
@@
 
-We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e. clusters located in the center and at the boundary between the core
+We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters (i.e., clusters located in the center and at the boundary between the core
 zones, see Figure~\ref{fig:core_25}) to investigate the variation of CRW with the position in the inner core.
@@
 Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed.
-The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e.
-the A$_{CRi}$).
+The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).
 

### 2020-07-20 paper/conclusion.tex
After Andrei's comments
Cover letter and minor changes

@@
 
-The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs. This shifts the neutron flux from the core center towards the periphery.
+The insertion of CRs deforms the radial flux shape close to CRs. This shifts the neutron flux from the core center towards the periphery.
 
@@
 \section{Future work}
-In Part II of this research effort, we will evaluate the effect of fuel salt 
+The authors intend to evaluate the effect of fuel salt 
 burnup on the CRW. The depleted fuel composition will be obtained using a

### 2020-07-20 paper/cover-letter/cover-letter.tex
Cover letter and minor changes

@@
 
-\documentclass[10.75pt]{letter} % Default font size of the document, change to 10pt to fit more text
+\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
 \usepackage{graphicx}
@@
 \newcommand{\StudentLastName}{Ashraf\xspace}
-\newcommand{\RecipientName}{Profs. Azmy, Joyce, and Su\xspace}
-\newcommand{\RecipientAddress}{Executive Editor\\Progress in Nuclear Energy}
+\newcommand{\RecipientName}{Prof. Mostafa Ghiaasiaan\xspace}
+\newcommand{\RecipientAddress}{Executive Editor\\Annals of Nuclear Energy}
 %\newcommand{\<++>}{<++>\xspace}
@@
 
-		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR).
-Part I: Design development, material selection, and worth analysis'' which I and my coauthors (Mr.
+		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr.
 Andrei Rykhlevskii, Prof.
@@
 Kathryn D.
-Huff) are submitting for exclusive consideration of publication as a research article in Progress in Nuclear Energy.
-The current manuscript is the first part of the two-part series that introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR.
-Part I focus on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.
-Meanwhile, Part II will focus on control rod worth evolution during operation.
-We intended to submit Part II on June-July, 2020.
+Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy.
+The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR.
+This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.
+
+		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal.
+However, we have addressed the major concerns of the reviewers.
+It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.
 
@@
 
-		Thank you for your consideration of our work. I expect it will be of interest
+		Thank you for your consideration of our work. We expect it will be of interest
 		to a broad readership concerned with simulation of MSRs.\\
@@
 		\closing{Sincere regards,
-			\includegraphics[height=1.3cm]{signature.png}\\
+	\includegraphics[height=1.5cm]{signature.png}\\
 	\fromsig{O. Ashraf\\

### 2020-07-20 paper/methods.tex
After addressed some comments from #16

@@
 axial and radial graphite reflectors to minimize the neutron leakage.
+We adopted the same graphite density reported in the original SD-TMSR paper \cite{li_optimization_2018}.
+Just have one sentence state it somewhere.
 A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
@@
 In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
-perform steady state calculations for the full core of the SD-TMSR with 
+perform steady-state calculations for a full 3D model of the SD-TMSR with 
 the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
@@
 
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.
+The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady-state of the fuel salt.
 
@@
 
-Equation~\ref{Equ:5} is used to calculate the differential CRW, where 
+Equation~\ref{Equ:5} is used to calculate the theoretical differential CRW, where 
 $\Delta Z$ is the length of rod inserted:

### 2020-07-21 paper/conclusion.tex
After Andrei's review

@@
 \section{Conclusion} \label{Conclusion}
-In the current work, we proposed a reactivity control system design for the 
+
+The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs.
+However, we cannot rely on online reprocessing to adjust reactivity quickly.
+Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods.
+Consequently, we proposed a reactivity control system design based on control rods in addition to the
+online feed system reactivity control in the 
 Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
-design has been evaluated at the startup for the full-core geometry using the
+design has been evaluated at the startup for a full 3D model of the SD-TMSR using the
 SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
@@
 position), the outer ring of the CSD failed to counteract the excess 
-reactivity of the core initially loaded with reactor-grade Pu and TRU elements.
+reactivity of the core initially loaded with reactor-grade Pu and TRU elements. Therefore, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
 However, the worth of the outer ring of the CSD is sufficient 
@@
 \section{Future work}
-The authors intend to evaluate the effect of fuel salt 
-burnup on the CRW. The depleted fuel composition will be obtained using a
+The authors intend to evaluate the effect of the fuel salt 
+depletion on the CRW. The depleted fuel composition will be obtained using a
 SERPENT-2 online reprocessing subroutine and 
-batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
+batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. Additionally, the authors intend to investigate
 kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 

### 2020-07-21 paper/cover-letter/cover-letter.tex
After Andrei's review

@@
 
-		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr.
+		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr.
 Andrei Rykhlevskii, Prof.
@@
 
-		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal.
+		I want to inform you that this manuscript in its initial form has been rejected by Progress of Nuclear Energy journal.
 However, we have addressed the major concerns of the reviewers.

### 2020-07-21 paper/introduction.tex
After Andrei's comments
Cover letter and minor changes
After addressed some comments from #16
After Andrei's review

@@
 operation); this leads to excess reactivity at the BOL.
-Robertson (1971) assumed small excess reactivity for \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel, thus only 2 control (graphite) rods for adjusting reactivity and 2 safety (B$_4$C) rods for emergency shutdown were suggested \cite{robertson_conceptual_1971}.
-However, scientists are concerned about $^{233}$U supply, since it does not exist anywhere.
-Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required.
-Betzler \emph{et al.} (2017) also reported large excess reactivity to operate Transatomic Power Molten Salt Reactor (TAP MSR) for a long time \cite{betzler2017assessment}.
-Additionally, Rykhlevskii \emph{et al.} (2019) studied the fuel cycle performance for various designs of the \gls{MSFR}.
-For MSFRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}.
+Robertson \emph{et al.} analyzed the \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel and concluded that two graphite rods are sufficient for adjusting reactivity during operation due to a small reactivity swing.
+Robertson \emph{et al.} also reported that 2 safety rods made of boron carbide (B$_4$C) are enough to safely shut the \gls{MSBR} down from any state \cite{robertson_conceptual_1971}.
+However, the $^{233}$U supply for commercial power plants is not readily available.
+Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., enriched U/$^{232}$Th, TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required.
+Betzler \emph{et al.} also reported large excess reactivity in Transatomic Power Molten Salt Reactor (TAP MSR) to ensure a 30-year operation cycle \cite{betzler2017assessment}.
+Additionally, Rykhlevskii \emph{et al.} studied the fuel cycle performance for various Fast-Spectrum \gls{MSR} designs.
+For a fast MSRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}.
 Recent studies on MSRs showed that the excess reactivity
-at the BOL may vary from 1.2 \% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1 \% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.
+at the BOL may vary from 1.2\% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1\% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.
 
-The online reprocessing and refueling system is designed to operate as long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}.
-However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its clones.
+The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}.
+However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs.
 Consequently, we need a prompt reactivity control system for emergencies.
-The most common and reliable procedure to control the reactor is to insert or withdraw control rods made of material with a large neutron absorption cross section (e.g., boron).
+The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
 Insertion of control rods introduces negative reactivity into the 
@@
 \cite{vcerba2017optimization}. 
-The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{atkinson2019small}.
-Additionally, Nuclear Regulatory Commission (NRC) regulation requires that one of the reactivity control systems use control rods \cite{nuclear1987standard}.
+The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}.
+Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
 
@@
 The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors.
-Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those of startup.
+Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those at startup.
 The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing.
 Therefore, the worth of the control rods should be corresponding to the reprocessing scheme; that is, the rate of extraction and addition of elements.
-However, the present work focuses on the steady state calculations (i.e.
-without burnup).
+However, the present work focuses on the steady-state calculations without taking into account fuel salt depletion.
 
-All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.
+All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}. Delayed neutron precursor drift was neglected in this study.
 

### 2020-07-21 paper/methods.tex
After Andrei's review

@@
 
-The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}.
+The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li2015analysis}.
 Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$.
 The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum.
-The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR.
+SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}.
 Figure~\ref{fig:ff} illustrates the quarter-core view of the
@@
 axial and radial graphite reflectors to minimize the neutron leakage.
-We adopted the same graphite density reported in the original SD-TMSR paper \cite{li_optimization_2018}.
-Just have one sentence state it somewhere.
+We adopted the same graphite density reported in the original SD-TMSR paper (2.3 g/cm$^3$) \cite{li_optimization_2018} to be consistent with results in the literature.
 A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
@@
 	\begin{center}	
-		\begin{tabular}{|l | r|}  %[!ht]
+		\begin{tabular}{l  r}  %[!ht]
 			%%	\begin{tabularx}{\textwidth}{l | r}

### 2020-07-21 paper/results.tex
Cover letter and minor changes
After Andrei's review

@@
 \section{Results and discussion} \label{Results-and-discussion}
+
+The SERPENT-2 is used to obtain the presented results.
+We use the ENDF-VII.0 cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
+The initial calculation state of a full 3D model of the SD-TMSR is identified by normal operation 
+conditions (see Table~\ref{tab:table1}) and fully withdrawn control rod 
+clusters. 
+To validate the proposed control rods 
+system we adopted the same operation conditions (as in the initial calculation 
+state) and changed the position of the control rod clusters along the $Z$ 
+direction.
+The obtained results including reactivity, control rod 
+worth, and interference effects (shadowing effects) are discussed below.
 
@@
 
-The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
+The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady-state 
 calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
 reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
-The previously studied $^{233}$U case recorded the maximum reactivity
+The previously studied $^{233}$U case \cite{ashraf2020Strategies} recorded the maximum reactivity
 during 60 effective full-power years (EFPY) of reactor operation to be 
-$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25}).
+$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
 The proposed reactivity control system must compensate such reactivity at startup and during burnup.
@@
 greater than in the fast spectrum.
-Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.
+Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore, the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.
 
@@
 Meanwhile, it will fail to compensate the excess 
-reactivity of the core initially loaded by reactor-grade Pu and TRU elements.
+reactivity of the core initially loaded by reactor-grade Pu and TRU elements. In this unlikely case, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
 
@@
 absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
-CRs deforms the radial flux shape in certain positions, i.e., around CRs.
+CRs deforms the radial flux shape close to CRs.
 This shifts the neutron flux from the core center towards the 
@@
 CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
-Notably, all results are based on steady state calculations.
+Notably, all results are based on steady-state calculations.
 

### 2020-07-21 paper/cover-letter/cover-letter.tex
Minor changes

@@
 The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR.
-This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.
+This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady-state.
 

### 2020-07-21 paper/conclusion.tex

@@
 
-The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs.
-However, we cannot rely on online reprocessing to adjust reactivity quickly.
-Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods.
-Consequently, we proposed a reactivity control system design based on control rods in addition to the
+In the current work, we proposed a first-ever reactivity control system design based on control rods in addition to the 
 online feed system reactivity control in the 
@@
 position), the outer ring of the CSD failed to counteract the excess 
-reactivity of the core initially loaded with reactor-grade Pu and TRU elements. Therefore, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
+reactivity of the core initially loaded with reactor-grade Pu and TRU elements.
+Therefore, the fuel salt temperature will rise, melt a freeze plug, and hot salt will be drained into subcritical drain tanks to safely shut down the reactor.
 However, the worth of the outer ring of the CSD is sufficient 

### 2020-07-21 paper/results.tex

@@
 reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
-The previously studied $^{233}$U case \cite{ashraf2020Strategies} recorded the maximum reactivity
-during 60 effective full-power years (EFPY) of reactor operation to be 
-$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
+For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
 The proposed reactivity control system must compensate such reactivity at startup and during burnup.
@@
 	\vspace{-0.5in}
-	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.}
+	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation
+		including periodic $^{233}$U/$^{232}$Th insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
 	\label{fig:keff_25}
@@
 \begin{table}  %[!hb]
-	\caption{The excess reactivity for the SD-TMSR core with different initial fissile materials.}
+	\caption{The excess reactivity at startup for the SD-TMSR core with different initial fissile materials.}
 	\vspace{0.1in}
@@
 Meanwhile, it will fail to compensate the excess 
-reactivity of the core initially loaded by reactor-grade Pu and TRU elements. In this unlikely case, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
+reactivity of the core initially loaded by reactor-grade Pu and TRU elements.
+In this unlikely case, the fuel salt temperature will rise, melt a freeze plug, and hot salt will be drained into subcritical drain tanks to safely shut down the reactor.
 

### 2020-07-22 paper/introduction.tex
Before submitting to Annals

@@
 online reprocessing, and fuel handling. Safety is one of the primary goals of
-the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case.
+the MSR system, and the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR), in particular, requires further investigation to support a licensing case.
 The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
@@
 Robertson \emph{et al.} analyzed the \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel and concluded that two graphite rods are sufficient for adjusting reactivity during operation due to a small reactivity swing.
-Robertson \emph{et al.} also reported that 2 safety rods made of boron carbide (B$_4$C) are enough to safely shut the \gls{MSBR} down from any state \cite{robertson_conceptual_1971}.
+Robertson \emph{et al.} also reported that two safety rods made of boron carbide (B$_4$C) are enough to safely shut the \gls{MSBR} down from any state \cite{robertson_conceptual_1971}.
 However, the $^{233}$U supply for commercial power plants is not readily available.
-Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., enriched U/$^{232}$Th, TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required.
+Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., enriched U/$^{232}$Th, TRU/$^{232}$Th, and Pu/$^{232}$Th), large excess reactivity is required.
 Betzler \emph{et al.} also reported large excess reactivity in Transatomic Power Molten Salt Reactor (TAP MSR) to ensure a 30-year operation cycle \cite{betzler2017assessment}.
@@
 control rod worths, shutdown margin, and shadowing 
-effects at steady state calculation.
+effects at steady-state calculation.
 
@@
 The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors.
-Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those at startup.
+Its neutron characters including effective multiplication factor ($k_{eff}$), excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those at startup.
 The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing.

### 2020-07-22 paper/methods.tex
Before submitting to Annals

@@
 The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum.
-SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}.
+The SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}.
 Figure~\ref{fig:ff} illustrates the quarter-core view of the
@@
 		Core height, cm									& 460  \\
+		Upper plenum, cm								& 30  \\
+		Lower plenum, cm								& 30  \\
 		Side length of the graphite hexagonal prism, cm   & 7.5 \\
@@
 This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
-From the obtained results, the control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
+From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
 The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
@@
 SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
-cladding and guide tube to facilitate the control rod movement.
+cladding and guide tube to facilitate the control rod movement. However, absorber-cladding gap was neglected for simplicity.
 All densities of rod materials are listed in
@@
 
-\begin{table}
+\begin{figure}[t!]  % replace 't' with 'b' to \centering
+	\centering
+	\hspace{+0.65in} 
+	\includegraphics[width=\textwidth]{cr.png}
+	\caption{Cross section of the B$_4$C control rod.}
+	\label{fig:cr}
+\end{figure}
+
+\begin{table}[b!]
 	\caption{The densities of the absorbing materials.}
@@
 
-\begin{figure}[t!]  % replace 't' with 'b' to \centering
-	\centering
-	\hspace{+0.65in} 
-	\includegraphics[width=\textwidth]{cr.png}
-	\caption{Cross section of the B$_4$C control rod.}
-	\label{fig:cr}
-\end{figure}
-
 Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, we propose an original distribution as a starting point of this analysis.
@@
 We propose 25 graphite elements with control rods: 16 Control Safety Devices (CSD) and 9 Shutdown Safety Devices (SSD).
+We distributed the 25 graphite elements with control rod clusters uniformly in the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
 
@@
 Red stands for SSD1-9 clusters.
-We distributed the graphite elements with control rod clusters uniformly in 
-the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
 The selected core segment at the upper left corner of 
@@
 
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady-state of the fuel salt.
+The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.
 
@@
 will distort the neutron flux around each other and will impact the reactivity worth.
-The term ``shadowing effect" has been used to describe this \cite{oka2014nuclear}.
+The term ``shadowing effect" has been used to describe this phenomenon \cite{oka2014nuclear}.
 The shadowing effect appears when the combined rod worth

### 2020-07-22 paper/results.tex
Before submitting to Annals

@@
 
-The SERPENT-2 is used to obtain the presented results.
+The SERPENT-2 is used to obtain all presented results.
 We use the ENDF-VII.0 cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
@@
 clusters. 
-To validate the proposed control rods 
-system we adopted the same operation conditions (as in the initial calculation 
-state) and changed the position of the control rod clusters along the $Z$ 
-direction.
-The obtained results including reactivity, control rod 
-worth, and interference effects (shadowing effects) are discussed below.
+The obtained results including excess reactivity, control rod 
+worth, shutdown margin, interference effects (shadowing effects), etc. are discussed below.
 
@@
 
-The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady-state 
+The excess reactivity $\rho$$_e$ is calculated by using equation~\ref{Equ:1} at zero burnup (steady-state 
 calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
 reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
-For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
+For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} (at $\approx$ 8 EFPY)).
 The proposed reactivity control system must compensate such reactivity at startup and during burnup.
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{keff_25.png}
-	\vspace{-0.5in}
-	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation
-		including periodic $^{233}$U/$^{232}$Th insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
-	\label{fig:keff_25}
-\end{figure}
 
@@
 \end{table}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{keff_25.png}
+	\vspace{-0.5in}
+	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation
+		including periodic $^{233}$U/$^{232}$Th insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
+	\label{fig:keff_25}
+\end{figure}
 
@@
 clusters are able to shut down the reactor initially loaded by 
-$^{233}$U and reactor-grade Pu regardless the absorbing material type.
+$^{233}$U and reactor-grade Pu regardless of the absorbing material type.
 However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
@@
 has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
-($2.8$); consequently, the neutron energy spectrum is faster in the peripheral 
+($2.80$); consequently, the neutron energy spectrum is faster in the peripheral 
 zone than in the center of the core degrading the CR's 
@@
 unreliable to shut down the reactor loaded with TRU.
-As mentioned previously, the SSD clusters should 
-provide a sufficient positive SDM.
+For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.
+This should be carefully studied when designing the reactivity control system.
 
@@
 This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}).
-Consequently, low interference between the SSD4 and CSD9 clusters and other surrounding clusters is observed.
+Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed.
 The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).

### 2020-07-22 paper/conclusion.tex
Before submitting to Annals
After Andrei's review

@@
 shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
-case).
+case). Increasing the number of SSD clusters would provide a sufficient positive SDM for the TRU case.
 
 The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects.
-The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio.
+The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratios.
+This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR.
 

### 2020-07-22 paper/results.tex
After Andrei's review

@@
 
-The SERPENT-2 is used to obtain all presented results.
-We use the ENDF-VII.0 cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
+We employed the SERPENT-2 Monte Carlo code to calculate all parameters herein.
+We used the ENDF/B-VII.0 \cite{CHADWICK20062931} cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
 The initial calculation state of a full 3D model of the SD-TMSR is identified by normal operation 
@@
 reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
-For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} (at $\approx$ 8 EFPY)).
+For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} after $\approx$ 8 EFPY of operation).
 The proposed reactivity control system must compensate such reactivity at startup and during burnup.
@@
 with different moderator-to-fuel ratios.
-This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}).
+This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}).
 Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed.

### 2020-07-22 paper/methods.tex

@@
 SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
-cladding and guide tube to facilitate the control rod movement. However, absorber-cladding gap was neglected for simplicity.
+cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity.
 All densities of rod materials are listed in
@@
 perform steady-state calculations for a full 3D model of the SD-TMSR with 
-the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
+the suggested control rod design. We adopted the ENDF/B-VII.0 \cite{CHADWICK20062931} cross section library 
 for all calculations in the present work.
@@
 
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.
+The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}, and it accounts for the steady-state of the fuel salt.
 

### 2020-09-15 paper/revisions/review-responses.tex
After Osama's edits

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)\\
\large Response to Review Comments}
\author{O. Ashraf, Andrei Rykhlevskii, G. V. Tikhomirov, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which certainly improved the paper.

\begin{questions}
        \section*{Reviewer 1}

        \question The manuscript investigated preliminary design of control rods in the SD-TMSR. Several issues should be clarified and discussed in detail before it can be published.

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question  The total demands of different control rods systems should be discussed first. According to the demands of nuclear safety regulations, two different shutdown systems of SSD and CSD must be adopted in a reactor design to ensure the reactor safe operation, to adjust power and to ensure the shutdown of reactor etc. All the shutdown systems must meet the shutdown margin of the reactor. For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods etc. Hence, the sizes of different control rods should be further optimized to realize their functional properties.
        \begin{solution}

        		 Need answer!

        \end{solution}

        %---------------------------------------------------------------------
        \question  Although Xe can be online removed during regular operation, it may remain in the core in the event of the bubble system failure. Hence, the Xenon poison effect of the SD-TMSR should be assessed for the designs of SSD and CSD. 
        \begin{solution}

		         Thank you for the excellent point. The Xenon poison effect is not considered in this paper, but we intend to study this phenomenon in our upcoming article when calculating the worth of the control rods during fuel depletion. The present work focuses on the steady-state calculations without taking into account fuel salt depletion.

		         The following sentence has been added to the future work to clarify this point:\\

		         The Xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.

        \end{solution}

        %---------------------------------------------------------------------

	\question If an extreme accident of the fuel salt solidification happens, the temperature of the fuel salt would drop significantly to about 300 K. A large positive reactivity may occur due to the large negative temperature feedback coefficient of the SD-TMSR. Hence, the control demands of both SSD and CSD should be assessed to meet all possible extreme accident conditions.
	\begin{solution}

	We appreciate your detailed review.
	Indeed rapid solidification would require a very rapid decline in temperature that is precluded by the same negative temperature feedback coefficient due to a reactivity insertion transient at 300 K. That is, the speed of salt temperature reduction is slowed, throughout any fuel cooling transient, by the negative temperature feedback coefficient. The feedback coefficient does not suddenly start when the temperature of the salt reaches a specific temperature. Indeed, a temperature of 300K could not be reached while power is still being generated in the core. Indeed, it could likely only be reached after the power from post-shutdown decay heat has reduced substantially due to time. If that is the case, then the reactor must have already been shut down.

	\end{solution}
%---------------------------------------------------------------------

	\question Figure~2 shows the neutron saturation thickness of B4C. However, the saturation thicknesses for different neutron absorbing materials may be significantly different from the B4C material, and the saturation thickness of same material is also inconsistent at different locations in the core. Hence, please evaluate the saturation thickness of different materials at different locations of the core.
\begin{solution}

 	 Thank you for your suggestion. The evaluation of the saturation thicknesses of different absorbers is illustrated in Figure~2. 	
	 We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted for all different materials. Results showed that in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding. All other absorbers not significantly affected by the self-shielding phenomenon in the region of study (0.0$<$r$<$1.0 cm).

	 The following paragraph has been added to the text to clarify this point:\\

     We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~2 illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials. As shown in Figure~2, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture. Other absorbers not significantly affected by the self-shielding phenomenon in the region of study (0.0$<$r$<$1.0 cm). From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).

\end{solution}
%---------------------------------------------------------------------

\question As shown in Figure~3, only a small thickness of gap of 0.1 cm is designed in a control rod, which would not meet the heat release requirements. It is necessary to evaluate the thermal emission behavior of the control rods, since the control rod material would release a large amount of heat after absorbing neutrons.
\begin{solution}

    Thank you for the suggestion. According to Robertson \emph{et al.} ``Conceptual design of MSBR`` (1971) the Control rod diameter is 3.75in and the diameter of the hole in the graphite for CR is 4in (ORNL-4548) \cite{robertson_conceptual_1971}. Thus, the gap in the MSBR is about 0.635 cm, i.e., $\sim$7\% of the CR diameter. Consequently, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. Regarding thermal emission calculations - it is out of scope and neglected in the current study.

	The following paragraph has been added to the text to clarify this point:\\

	The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission calculations is out of scope and also neglected in this study.

\end{solution}
%---------------------------------------------------------------------

\question Table~3 lists the initial excess reactivity for different fissile fuel component. Please clarify the corresponding actual reactivity of 1 \$ for each fissile fuel, since all of them may be significantly different from each other. In addition, why is the initial excess reactivity of TRU fuel significantly higher than that of 233U? Also, the large initial excess reactivity of TRU fuel may affect the total SDMs of the different control rods in Table 6.
\begin{solution}

	Thank you for the questions. Now all initial excess reactivities are listed in Table~5 in [pcm] unit. Regarding the initial excess reactivity of TRU fuel; TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly. Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}. The proposed reactivity control system must compensate such reactivity at startup and during burnup.

	The following sentence has been added to the conclusion to clarify this point:\\

	TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly. Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}. The proposed reactivity control system must compensate such reactivity at startup and during burnup.

\end{solution}
%---------------------------------------------------------------------

\question In section of 4.2.1, the total control rod value for different starting fissile fuel conditions is discussed. However, these values for the reactor-grade Pu and TRU are not found in Table~4 and Table~5. Please clarify the data.
\begin{solution}

	Thank you for catching this. Table~8 lists the total CRW of all CRs, CSD, and SSD for SD-TMSR initially loaded by reactor-grade Pu and TRU.

\end{solution}
%---------------------------------------------------------------------

\question For the reactivity adjustment in a reactor, it should be only done by the special adjusting rods rather than by all the control rods. Hence, Figure~10 should only give the differential worth of the adjusting rods. The function and corresponding demand of different control rods should be discussed in detail. In addition, it can be seen from Figure~10 that the differential worth of CSD overturns significantly at about 100 cm, which would not accord with the actual condition. Please clarify the reasons of this phenomenon.
\begin{solution}

	Thank you for catching this. The differential CRWs for only CSD clusters are demonstrated in Figure~11. The function and corresponding demand of different control rods have been discussed in the manuscript. Regarding overturns; sorry for that, we recalculated the differential worth at 100 cm and found a computational error. Now it is corrected in Figure~11.

	The following sentence has been added to the conclusion to clarify this point:\\

	The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems, however, the differential CRWs are calculated for only CSD system. Since the reactivity adjustment in the SD-TMSR should be only done by the special adjusting rods (i.e., CSD).

\end{solution}
%---------------------------------------------------------------------

\question Please assess whether the control rods would still meet the shutdown requirement if a single control rod with maximum worth is withdrawn.
\begin{solution}

	Thank you for your suggestion. Table~10 lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.

		The following paragraph has been added to the manuscript to clarify this point:\\

	Table~10 lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn. As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu. For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM. This should be carefully studied when designing the reactivity control system.

\end{solution}
%---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question The paper is well written, well structured, and covers an important topic. I did not find even a typo. It certainly ought to be published. However, since the cores investigated are static, the reactivity in \$ can be difficult to interpret or even misleading. I suggest adding the values of $\beta$$_{eff}$ [pcm] used in Equation 1, for each of the different fuels, into the paper, so readers can make their own conclusions about the circulation $\beta$$_{eff}$ and this the \$ values. Additionally, I think it would be beneficial for completeness of the paper to include isotopic vectors of the different fuels.

        \begin{solution}
        Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. Now all values of reactivity and SDMs are mentioned in the manuscript in [pcm] unit. Additionally, the isotopic vectors of the different fuels are listed in Table~1 and Table~2, respectively.

        \end{solution}

        %---------------------------------------------------------------------

        \question The models ran were not published (e.g. on github), so it is impossible to independently verify the work, but, alas, this has become a troubling standard in the field.

        \begin{solution}
                 Thank you very much for your interest in our work. Please, follow our scientific group ``Advanced Reactors and Fuel Cycles -
                 ARFC`` on Github on this link: https://github.com/arfc.

        \end{solution}

 %--------------------------------------------------------------------
\section*{Reviewer 3}
        %--------------------------------------------------------------------
        \question This manuscript describes the design of control rods for a graphite moderated molten salt reactor. It is appropriately structured and well written, but it is difficult to discern the main takeaways from this work as it reads like a progress report. The discussion omits some information regarding the design of the control rods and feasibility of geometries. These issues are captured in the below comments.

        \begin{solution}
        	 Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.

        \end{solution}

        %--------------------------------------------------------------------
        \question  The statement, " Safety is one of the primary goals of the MSR system, and the SD-TMSR, in particular, requires further investigation to support a licensing case" is obvious.

        \begin{solution}

              Thank you for the comment. What he meant here??

        \end{solution}

        %--------------------------------------------------------------------
        \question How is 0.1 cm a reasonable gap between the cladding and guide tube?
        \begin{solution}

Thank you for the question. According to Robertson \emph{et al.} ``Conceptual design of MSBR`` (1971) the Control rod diameter is 3.75in and the diameter of the hole in the graphite for CR is 4in (ORNL-4548) \cite{robertson_conceptual_1971}. Thus, the gap in the MSBR is about 0.635 cm, i.e., $\sim$7\% of the CR diameter. Consequently, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. Regarding thermal emission calculations - it is out of scope and neglected in the current study.

The following paragraph has been added to the text to clarify this point:\\

The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission calculations is out of scope and also neglected in this study.

        \end{solution}

        %--------------------------------------------------------------------
        \question Why do the four rods break the 60-degree symmetry of the fuel assemblies?

        \begin{solution}
                 Thank you for the excellent point. We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~8. Results showed that three rods in the graphite element save the 60-degree symmetry of the element, however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$. In the case of four rods, the 60-degree symmetry of the graphite element is broken, however, the SDM is about $228$ $pcm$ and the A$_{CRi}$ is $0.97$. Finally, when six rods are distributed in the graphite element both symmetry and relatively high SDM are obtained ($598$ $pcm$) but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case. Therefore the 3-CRs and 6-CRs configuration are neglected due to the negative SDM and the low A$_{CRi}$, respectively. The 4-CRs configuration is adopted in the current study since the SDM is positive and almost no shadowing effect has observed.

                 The following paragraph has been added to the manuscript:\\

We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~8. Results showed that three rods in the graphite element save the 60-degree symmetry of the element, however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$. In the case of four rods, the 60-degree symmetry of the graphite element is broken, however, the SDM is about $228$ $pcm$ and the A$_{CRi}$ is $0.97$. Finally, when six rods are distributed in the graphite element both symmetry and relatively high SDM are obtained ($598$ $pcm$) but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case. Therefore the 3-CRs and 6-CRs configuration are neglected due to the negative SDM and the low A$_{CRi}$, respectively. The 4-CRs configuration is adopted in the current study since the SDM is positive and almost no shadowing effect has observed.

        \end{solution}

        %--------------------------------------------------------------------
        \question  How are the 16 control safety devices and 9 shutdown safety devices selected?
        \begin{solution}
        	Thank you for the question. Since the total number and distribution of the control assemblies in the SD-TMSR have not been determined, \v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting point of this analysis. The control rod cluster with the maximum worth (i.e., SSD1), which located in the center of the core is selected as a shutdown safety device.
        	Then it followed by the CSD inner ring, SSD ring, and the CSD outer ring. Therefore, 16 CSD and 9 SSD are uniformly distributed in the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high. We taking into account the distance between CR clusters to avoid the shadowing effects.

        \end{solution}

        %--------------------------------------------------------------------
        \question Are control rod guide tubes voided?
        \begin{solution}
                Thank you for your comment. No, the control rod guide tubes are filled by fuel salt. It is necessary to remove the heat released from the CRs after absorbing neutrons. Notably, for example, the CRs made of $B_{4}C$ (lower density among the absorbers in this study) will not float in the fuel salt since the existence of the AIM1 cladding will make the total density $\sim 4.92$ $g/cm^3$ $>$ the density of the fuel salt.

        \end{solution}

        %--------------------------------------------------------------------
        \question Does flux shape also contribute to the reactivity worth of the inner ring of the CSD?
        \begin{solution}
                 Thank you for your question. Need answer!.

        \end{solution}

 %--------------------------------------------------------------------
\question Please speak more to the anti-shadowing effects observed for CSD9 and SSD4.
\begin{solution}
	Thank you for your suggestion.

	The following paragraphs have been added to the manuscript:\\

	As listed in Tables~6 and ~7, the strongest anti-shadowing effect occurred in 
	SSD4 and CSD9 clusters that are located at the boundary between the core zones 
	with different moderator-to-fuel ratios. This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).

\end{solution}
 %--------------------------------------------------------------------
\question What is "sufficient positive SDM"? This phrase is unspecific. What is sufficient? Be more specific here.
\begin{solution}
	Thank you for catching this. Need answer!.

\end{solution}
        %--------------------------------------------------------------------

\end{questions}
\bibliographystyle{elsarticle-num}
\bibliography{../2019-CRs}
\end{document}

%
% End of file `elsarticle-template-num.tex'.

### 2020-09-15 paper/conclusion.tex
After Osama's edits

@@
 fully withdrawn. The $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
-TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, 
-respectively.
+TRU are $1180\pm28$ $pcm$, $2330\pm30$ $pcm$, and $4800\pm35$ $pcm$, respectively.
 
@@
 
-The integral and differential CR worth are calculated for three 
-different systems: all CRs, CSD, and SSD systems. The results show 
+The integral CR worths are calculated for three 
+different systems: all CRs, CSD, and SSD systems, however, the differential CR worths are calculated for only CSD clusters. The results show 
 that all absorbing materials have almost the same integral rod worth in the 
@@
 SERPENT-2 online reprocessing subroutine and 
-batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. Additionally, the authors intend to investigate
+batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. 
+The Xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
+Additionally, the authors intend to investigate
 kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 

### 2020-09-15 paper/highlights/highlights.tex
After Osama's edits

\documentclass[review]{elsarticle}

\usepackage{lineno}
\usepackage{xspace}
\modulolinenumbers[5]

\journal{Annals of Nuclear Energy}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%%%% packages and definitions (optional)
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{hhline}
\usepackage{amsmath}

%\usepackage[demo]{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{x}{>{\hsize=.25\hsize}X}

\graphicspath{ {figures/} }

% tikz %
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

% hyperref %
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{frontmatter}
\title{Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item A reliable safety system based on control rods has been introduced in the SD-TMSR.
	\item Three different initial fissile loadings are considered.
	\item Six different absorbing materials have been investigated.
	\item Integral and differential control rod worth, SDM, and shadowing effects at steady-state were calculated.
	\item SERPENT-2 Monte-Carlo code was used to calculate the reactivity worth.
\end{itemize}
\end{document}

### 2020-09-15 paper/methods.tex
After Osama's edits

@@
 elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
+The reactor-grade Pu and TRU isotopic vectors are summarized in 
+Table~\ref{tab:table52} and ~\ref{tab:table53}, respectively.
+
+\begin{table} % [!ht]
+	\centering
+	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{X X X X X}
+		\hline
+		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
+		\hline
+		$ $ $ $ $ $ $ $ $ $1.3 &$ $ $ $ $ $60.3&$ $ $ $ $ $24.3&$ $ $ $ $ $ $ $ $ $9.1&$ $ $ $ $ $ $ $ $ $ $ $ $ $5 \\
+		\hline
+	\end{tabularx}
+	\label{tab:table52}
+\end{table}
+
+\begin{table} %  [!ht]
+	\centering
+	\caption{TRU vector (wt.\%) \cite{de2000scenarios}.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{X X X X X X X X X X}
+		\hline
+		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
+		\hline
+		$ $ $ $ $ $ $ $ $ $6.3&$ $ $ $ $ $ $ $ $ $2.7& $ $ $ $ $ $45.9& $ $ $ $ $ $21.5& $ $ $ $ $ $10.7&$ $ $ $ $ $ $ $ $ $6.7&$ $ $ $ $ $ $ $ $ $3.4&$ $ $ $ $ $ $ $ $ $1.9&$ $ $ $ $ $ $ $ $ $$ $0.8&$ $ $ $ $ $ $ $ $ $0.1 \\
+		\hline
+	\end{tabularx}
+	\label{tab:table53}
+\end{table}
+
 The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
@@
 We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted.
-Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod.
-As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius.
-However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$.
+Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials.
+As shown in Figure~\ref{fig:Radius}, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers.
+However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$.
 This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
+Other absorbers not significantly affected by the self-shielding phenomenon in the region of study (0.0$<$r$<$1.0 cm).
 From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
@@
 (15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
-SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
-cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity.
+SiC structural material (see Figure~\ref{fig:cr}).
+The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+However, the absorber-cladding gap was neglected for simplicity.
+Thermal emission calculations is out of scope and also neglected in this study.
 All densities of rod materials are listed in
@@
 The excess reactivity $\rho$$_e$ is the reactivity of the core when all control rods are withdrawn.
-$\rho$$_e$ is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core and $\beta_{eff}$ is the effective fraction of delayed neutrons:
+$\rho$$_e$ is calculated by SERPENT-2 based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core:
 
@@
 \label{Equ:1}
-{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}{{\beta}_{eff}}}.
+{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}}.
 \end{equation}
-
-The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}, and it accounts for the steady-state of the fuel salt.
 
@@
 The control rod worth (CRW) is the amount of negative reactivity associated with the control rod insertion.
-The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ control rod (CR), $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion of the i$^{th}$ CR \cite{vcerba2017optimization}:
+The CRW is calculated by SERPENT-2 based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ control rod (CR), $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion of the i$^{th}$ CR \cite{vcerba2017optimization}:
 
@@
 insertion or withdrawal of the CR. However, the \textit{differential CRW} is the
-reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
+reactivity inserted per unit of withdrawal [pcm/cm]. To calculate those 
 parameters, we varied the position of CR clusters from fully withdrawn to 
 fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
-[\$], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
-before and after CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the
-fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:
+[pcm], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
+before and after CR insertion to the $j$$^{th}$ step, respectively, and $N$ is the number of steps:
 
@@
 \label{Equ:4}
-{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
+{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}}.
 \end{equation}
@@
 \label{Equ:5}
-\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
+\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}}.
 \end{equation}

### 2020-09-15 paper/results.tex
After Osama's edits

@@
 The excess reactivity $\rho$$_e$ is calculated by using equation~\ref{Equ:1} at zero burnup (steady-state 
-calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
+calculation), when all control rods are fully withdrawn. The $\rho_e$ for $^{233}$U, 
 reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
-For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} after $\approx$ 8 EFPY of operation).
+For $^{233}$U case \cite{ashraf2020Strategies} the initial excess reactivity is about $1180\pm28$ $pcm$, however, the maximum observed excess reactivity is $1344\pm25$ $pcm$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} after $\approx$ 8 EFPY of operation).
+TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
+Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}.
 The proposed reactivity control system must compensate such reactivity at startup and during burnup.
@@
 		\hline
-		$\rho_e$					& $1.65\pm0.04$ $\$$ & $4.11\pm0.02$ $\$$ & $15.38\pm0.04$ $\$$ \\
+		$\rho_e$					& $1180\pm28$ $pcm$ & $2330\pm30$ $pcm$ & $4800\pm35$ $pcm$ \\
 		\hline
@@
 Fuel salt composition of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$ at 70-17.5-12.3-0.2 mole\% is used to generate the results listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}.
+However, Table~\ref{tab:table51} summarizes the CRW of all CRs, CSD, and SSD for SD-TMSR initially loaded by reactor-grade Pu and TRU.
+
 \begin{sidewaystable}
@@
 	\caption{The control rod worth for different CR 
-		materials.}
+		materials (SD-TMSR initially loaded by $^{233}$U).}
 	\vspace{1ex}
@@
 		\cline{2-13}
-		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$	
-		& $\Delta\rho$$_{CRi}$  [\$]  &A$_{CRi}$		
-		&$\Delta\rho$$_{CRi}$ [\$]  &A$_{CRi}$		
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$		
-		&$\Delta\rho$$_{CRi}$ [\$]	&A$_{CRi}$  \\
+		& $\Delta\rho$$_{CRi}$  [pcm]  &A$_{CRi}$	
+		& $\Delta\rho$$_{CRi}$  [pcm]  &A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [pcm]  &A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [pcm]	&A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [pcm]	&A$_{CRi}$		
+		&$\Delta\rho$$_{CRi}$ [pcm]	&A$_{CRi}$  \\
 		\hline                   
-		All control rods      &  $42.04\pm0.60$	&	& $48.19\pm0.68$   &		
-		&$40.40\pm0.41$	&		&$37.96\pm0.36$	&		&$33.70\pm0.40$	&	
-			&$42.39\pm0.48$	& 	 \\
+		All control rods      &  $13067\pm35$	&	& $14978\pm37$   &		
+		&$12739\pm35$	&		&$11576\pm31$	&		&$10558\pm30$	&	
+			&$13596\pm35$	& 	 \\
 		\hline 
-		CSD 		 & $22.32\pm0.20$ 	& $1.24\pm0.01$	 			& $25.50\pm0.23$   &$1.24\pm0.01$	 	&$21.90\pm0.17$	&$1.10\pm0.01$	 	&$20.62\pm0.34$	&$1.10\pm0.01$	 	&$18.48\pm0.25$	&$1.17\pm0.01$	 	&$22.96\pm0.18$	&$1.20\pm0.01$   \\
+		CSD 		 & $6990\pm29$ 	& $1.22\pm0.01$	 			& $7914\pm28$   &$1.26\pm0.01$	 	&$6534\pm28$	&$1.27\pm0.01$	 	&$6490\pm29$	&$1.16\pm0.01$	 	&$5705\pm25$	&$1.18\pm0.01$	 	&$7080\pm28$	&$1.26\pm0.01$   \\
 		\hline 
-		SSD		   & $14.27\pm0.10$ 	&$1.38\pm0.02$	 	&$16.39\pm0.11$ &$1.38\pm0.02$	 	&$14.27\pm0.21$	&$1.29\pm0.01$	 	&$13.23\pm0.18$	&$1.30\pm0.06$	 	&$12.00\pm0.20$	&$1.26\pm0.01$	 	&$14.58\pm0.11$	&$1.30\pm0.02$	  \\
+		SSD		   & $4482\pm31$ 	&$1.35\pm0.02$	 	&$4998\pm34$ &$1.41\pm0.02$	 	&$4400\pm35$	&$1.41\pm0.01$	 	&$4034\pm29$	&$1.26\pm0.06$	 	&$3805\pm28$	&$1.28\pm0.01$	 	&$4676\pm35$	&$1.39\pm0.02$	  \\
 		\hline 
-		CSD inner ring   &  $16.80\pm0.02$	&$1.50\pm0.01$	  &  $18.42\pm0.05$  &$1.60\pm0.04$	 		&$16.29\pm0.29$	&$1.48\pm0.02$	 	&$15.50\pm0.17$	& $1.46\pm0.01$  	&$14.12\pm0.07$	&$1.39\pm0.01$	 	&$16.92\pm0.13$	&$1.50\pm0.01$	  \\
+		CSD inner ring   &  $5011\pm42$	&$1.61\pm0.01$	  &  $5704\pm47$  &$1.70\pm0.04$	 		&$4951\pm47$	&$1.56\pm0.02$	 	&$4804\pm38$	& $1.53\pm0.01$  	&$4306\pm38$	&$1.57\pm0.01$	 	&$5068\pm31$	&$1.76\pm0.01$	  \\
 		\hline 
-		CSD outer ring            &  $2.16\pm0.02$	&$3.11\pm0.06$	     &$2.26\pm0.02$ &$4.21\pm0.07$	 	&$2.10\pm0.06$	&$3.11\pm0.10$ 	&$1.85\pm0.07$	&$3.24\pm0.06$	 	&$1.80\pm0.10$	&$2.54\pm0.14$	 	&$2.14\pm0.05$	&$3.20\pm0.05$	  	\\
+		CSD outer ring            &  $635\pm31$	&$3.87\pm0.06$	     &$836\pm35$ &$4.16\pm0.07$	 	&$602\pm27$	&$4.26\pm0.10$ 	&$554\pm30$	&$3.94\pm0.06$	 	&$550\pm29$	&$3.31\pm0.14$	 	&$681\pm28$	&$3.75\pm0.05$	  	\\
 		\hline 
-		CSD2			 &  $2.11\pm0.03$	&$3.00\pm0.08$	 			& $2.25\pm0.04$   &$3.69\pm0.16$	 	&$2.24\pm0.05$	&$2.42\pm0.10$	 	&$2.00\pm0.10$	&$2.68\pm0.03$	 	&$1.80\pm0.10$	&$2.55\pm0.20$	 	&$2.19\pm0.12$	&$2.90\pm0.08$	  \\
+		CSD2			 &  $660\pm30$	&$4.10\pm0.08$	 			& $692\pm31$   &$4.44\pm0.16$	 	&$694\pm32$	&$3.61\pm0.10$	 	&$610\pm29$	&$3.33\pm0.03$	 	&$553\pm28$	&$3.68\pm0.20$	 	&$685\pm29$	&$4.26\pm0.08$	  \\
 		\hline 
-		CSD9			 &  $0.06\pm0.01$	&$15.16\pm0.10$	 				& $0.15\pm0.04$   & $10.53\pm0.01$	  	&$0.10\pm0.05$	&$5.10\pm0.05$	 	&$0.05\pm0.01$	&$16.40\pm0.10$	  	&$0.09\pm0.07$	&$5.55\pm0.20$	  	&$0.07\pm0.05$	&$14.00\pm0.10$	  \\
+		CSD9			 &  $111\pm18$	&$7.82\pm0.10$	 				& $127\pm29$   & $7.63\pm0.01$	  	&$99\pm20$	&$10.10\pm0.05$	 	&$87\pm19$	&$6.13\pm0.10$	  	&$82\pm25$	&$9.74\pm0.20$	  	&$115\pm19$	&$10.83\pm0.10$	  \\ 
 		\hline
-		SSD1		 &  $3.95\pm0.05$	&$1.31\pm0.01$	 	& $4.18\pm0.07$   &$1.59\pm0.08$	 	&$3.95\pm0.13$	&$1.30\pm0.07$	 	&$3.59\pm0.03$	&$1.49\pm0.01$	 	&$3.45\pm0.12$	&$1.40\pm0.08$	 	&$3.91\pm0.06$	&$1.40\pm0.01$  \\
+		SSD1		 &  $1257\pm25$	&$1.41\pm0.01$	 	& $1290\pm27$   &$2.09\pm0.08$	 	&$1205\pm30$	&$2.05\pm0.07$	 	&$1104\pm25$	&$1.77\pm0.01$	 	&$1071\pm27$	&$2.02\pm0.08$	 	&$1224\pm31$	&$2.33\pm0.01$  \\
 		\hline 
-		SSD4		 &  $0.59\pm0.08$	& $9.52\pm0.10$	 		&  $0.57\pm0.09$  &$7.84\pm0.15$	 	&$0.63\pm0.06$	&$4.40\pm0.10$	 	&$1.00\pm0.05$	&$2.51\pm0.16$	 	&$0.60\pm0.80$	&$3.31\pm0.27$	 	&$0.60\pm0.08$	&$5.10\pm0.28$	  \\
+		SSD4		 &  $183\pm32$	& $10.18\pm0.10$	 		&  $179\pm25$  &$10.68\pm0.15$	 	&$191\pm35$	&$7.78\pm0.10$	 	&$298\pm37$	&$7.51\pm0.16$	 	&$188\pm36$	&$6.96\pm0.27$	 	&$185\pm25$	&$10.43\pm0.28$	  \\
 		\hline
@@
 	\centering
-	\caption{The shadowing effect for different CR materials.}
+	\caption{The shadowing effect for different CR materials (SD-TMSR initially loaded by $^{233}$U).}
 	\vspace{0.1in}
@@
 	\hline 
-	CSD9		&	$\star$$\star$				& $\star$$\star$	&$\star$		&$\star$$\star$			&$\star$$\star$	  &$\star$$\star$		 \\ 	 
+	CSD9		&	$\star$$\star$				& $\star$$\star$	&$\star$$\star$		&$\star$$\star$			&$\star$$\star$	  &$\star$$\star$		 \\ 	 
 	\hline
@@
 	\hline 
-	SSD4		&		$\star$$\star$			& 	$\star$$\star$	&$\star$		&$\star$		&$\star$  &	$\star$$\star$	 \\  
+	SSD4		&		$\star$$\star$			& 	$\star$$\star$	&$\star$$\star$		&$\star$$\star$			&$\star$$\star$  &	$\star$$\star$	 \\  
 	\hline
@@
 \end{sidewaystable}
+
+\begin{table} %[b!]
+	\caption{The CRW of all CRs, CSD, and SSD for SD-TMSR initially loaded by reactor-grade Pu and TRU, unit [pcm].}
+	\begin{tabularx}{\textwidth}{ p{2cm} | X X X   X X X } \hline
+		\multirow{1}{*}{Absorbing}
+		 \multirow{1}{*}{materials}
+		 		& 
+		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
+		\space   & \multicolumn{3}{c}{Pu} & 
+		\multicolumn{3}{c}{TRU} \\ \cline{2-7}
+		\space  & All CRs & CSD & SSD & All CRs & CSD & 
+		SSD \\ \hline
+		Nat. B$_4$C 
+		&$11353\pm35$&$5963\pm30$&$3908\pm31$&$12173\pm31$&$6872\pm35$ &$4408\pm30$
+		\\ 
+		B$_4$C-90 
+		&$13264\pm35$&$6755\pm29$&$4837\pm35$&$13915\pm30$&$7883\pm28$&$5028\pm35$ \\
+		HfB$_2$ 
+		&$10825\pm27$&$5562\pm30$&$3741\pm31$&$12027\pm30$&$6795\pm31$&$4477\pm29$ \\ 
+	    HfH$_{1.62}$
+		&$9836\pm30$&$4828\pm32$&$3545\pm30$&$11651\pm30$&$6583\pm31$&$4158\pm30$ \\ 
+		Gd$_2$O$_3$ 
+		&$8608\pm35$&$4384\pm28$&$3471\pm31$&$10356\pm28$&$5851\pm29$&$3858\pm31$ \\ 
+		Eu$_2$O$_3$ 
+		&$11826\pm31$&$6019\pm30$&$4073\pm29$&$12648\pm30$&$7146\pm30$&$4604\pm31$ \\ 
+		\hline
+	\end{tabularx}
+	\label{tab:table51}
+\end{table}
+
 \subsubsection{CRW} \label{CR_worth}
 
-Among the absorbers investigated, the total worth of all CRs extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
-$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
+Among the absorbers investigated, the total worth of all CRs extends from $10558\pm30$ $pcm$ to $14978\pm37$ 
+$pcm$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 (boron enriched to 90\% $^{10}$B)
 has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
@@
 clusters are able to shut down the reactor initially loaded by 
-$^{233}$U and reactor-grade Pu regardless of the absorbing material type.
+$^{233}$U regardless of the absorbing material type.
+For reactor-grade Pu (Table~\ref{tab:table51}), also, either CSD or SSD 
+clusters are able to compensate the initial excess reactivity or shut down the reactor initially loaded by reactor-grade Pu regardless of the absorbing material type.
 However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR
-initially loaded by transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$).
+initially loaded by transuranic (TRU) elements ($\rho_e$ is $4800\pm35$ $pcm$).
 The reason for this is the much larger 
@@
 unreliable to shut down the reactor loaded with TRU.
+Table~\ref{tab:table50} lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn.
+As shown in Table~\ref{tab:table50} the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
 For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{3cm} s s s}
+	\begin{tabularx}{\textwidth}{p{2.5cm} p{2.5cm} p{2.5cm} p{3cm}}
 		\hline
@@
 		\hline
-		Nat. B$_4$C					& $12.62\pm0.08$ $\$$ &$10.18\pm0.09$ $\$$ &$-1.12\pm0.08$ $\$$ \\
-		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
-		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.80\pm0.09$ $\$$\\
-		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
-		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
-		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
+		Nat. B$_4$C					& $3302\pm28$ $pcm$ &$1743\pm31$ $pcm$  &$-392\pm25$ $pcm$ \\
+		B$_4$C-90                   & $3818\pm30$ $pcm$ & $2507\pm39$ $pcm$ & $ $ $ $ $228\pm26$ $pcm$ \\
+		Eu$_2$O$_3$                 &  $3496\pm30$ $pcm$&  $1645\pm25$ $pcm$&$-196\pm25$ $pcm$\\
+		HfB$_2$        				&$3220\pm42$ $pcm$  &$1412\pm42$ $pcm$  &$-323\pm25$ $pcm$   \\
+		HfH$_{1.62}$				& $2854\pm35$ $pcm$ &$1215\pm31$ $pcm$  &$-642\pm31$ $pcm$\\
+		Gd$_2$O$_3$	  		        & $2625\pm41$ $pcm$ &$1141\pm31$ $pcm$  & $-942\pm35$ $pcm$\\
 		\hline
@@
 	\label{tab:table2}
+\end{table}
+\begin{table}  %[!hb]
+	\caption{The SDMs for the SD-TMSR core when the SSD1 cluster is fully withdrawn.}
+	\vspace{0.1in}
+	\begin{tabularx}{\textwidth}{p{2.5cm} p{2.5cm} p{2.5cm} p{3cm}}
+		\hline
+		Absorbing materials         &  $^{233}$U        & reactor-grade Pu  &  TRU \\
+		\hline
+		Nat. B$_4$C					& $2045\pm25$ $pcm$ &$498\pm27$ $pcm$   & $-1637\pm27$ $pcm$ \\
+		B$_4$C-90                   & $2528\pm25$ $pcm$ & $1257\pm25$ $pcm$ &  $-1082\pm26$ $pcm$ \\
+		Eu$_2$O$_3$                 &  $2272\pm30$ $pcm$&  $524\pm27$ $pcm$ &$-1450\pm25$ $pcm$\\
+		HfB$_2$        				&$2015\pm35$ $pcm$  &$257\pm37$ $pcm$   &$-1698\pm35$ $pcm$   \\
+		HfH$_{1.62}$				& $1750\pm25$ $pcm$ &$170\pm27$ $pcm$   &$-1787\pm31$ $pcm$\\
+		Gd$_2$O$_3$	  		        & $1554\pm35$ $pcm$ &$120\pm25$ $pcm$    & $-2166\pm35$ $pcm$\\
+		\hline
+	\end{tabularx}
+	\label{tab:table50}
 \end{table}
@@
 
+We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~\ref{fig:3_CR}.
+Results showed that three rods in the graphite element save the 60-degree symmetry of the element, however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+In the case of four rods, the 60-degree symmetry of the graphite element is broken, however, the SDM is about $228$ $pcm$ and the A$_{CRi}$ is $0.97$.
+Finally, when six rods are distributed in the graphite element both symmetry and relatively high SDM are obtained ($598$ $pcm$) but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
+Therefore the 3-CRs and 6-CRs configuration are neglected due to the negative SDM and the low A$_{CRi}$, respectively.
+The 4-CRs configuration is adopted in the current study since the SDM is positive and almost no shadowing effect has observed.
+
 Insertion of the CR affects the neutron flux distribution, which is 
@@
 into the core \cite{girardin2007control}.
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=\textwidth]{3_CR.png}
+	\vspace{-0.5in}
+	\caption{$XY$ section of graphite element with a) 3-CRs b) 4-CR c) 6-CRs configurations.} 
+	\label{fig:3_CR}
+\end{figure}
+
 \begin{figure}[!ht]
@@
 
-The integral and differential CRWs are calculated for three 
-different systems: all CRs, CSD, and SSD systems. The CRs are 
-inserted gradually into the core from the top to the bottom. 
+The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems, however, the differential CRWs are calculated for only CSD system.
+Since the reactivity adjustment in the SD-TMSR should be only done by the special adjusting rods (i.e., CSD).
+The CRs are inserted gradually into the core from the top to the bottom. 
 Equations~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
@@
 made of B$_4$C-90. The maximum integral worth of all CRs, CSD, and SSD 
-clusters are about $48.39$ $\$$, $25.30$ $\$$, and $16.46$ $\$$, respectively. The 
+clusters are about $14978$ $pcm$, $7914$ $pcm$, and $4998$ $pcm$, respectively. The 
 integral worth of SSD clusters made of B$_4$C-90 is sufficient to shut down the reactor from any 
@@
 From the center of the core to the bottom, the differential CRW values decrease (region with low thermal neutron flux).
-Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curves are not exactly symmetrical.
+Figure~\ref{fig:diff} shows that the maximum differential CRW is shifted toward the bottom of the core and the curve is not exactly symmetrical.
 This is due to the asymmetrical distribution of the fuel and graphite in simulation \cite{xuemei2013study,son2016control}.
@@
 	\vspace{-0.5in}
-	\caption{Differential CRW of all CRs, CSD, and SSD clusters (CRs made of B$_4$C-90).} 
+	\caption{Differential CRW of CSD clusters (CRs made of B$_4$C-90).} 
 	\label{fig:diff}

### 2020-09-16 paper/revisions/review-responses.tex
rest comments

@@
 
-        		 Need answer!
+        		Thank you for the excellent point.
+The demands of different control rods systems have been discussed in the manuscript.
+Optimization of different control rods sizes will be done in our future work.
+
+        		The following paragraph has been added to the manuscript to clarify this point:\\
+
+Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
+According to the demands of nuclear safety regulations, two independent shutdown systems of Control Safety Devices (CSD) and Shutdown Safety Devices (SSD) must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
+All the shutdown systems must meet the shutdown margin of the reactor.
+For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods.
 
@@
         \begin{solution}
-                 Thank you for your question. Need answer!.
+                 Thank you for your question.
+The inner ring of the CSD is located in the central zone of the SD-TMSR core, in which the volume ratio between molten salt and graphite is relatively small ($0.357$).
+The inner ring of the CSD has significantly large reactivity worth due to much greater neutron flux at the center of the core than on the periphery.
 
@@
 	with different moderator-to-fuel ratios.
-This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}).
+This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~5).
 Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed.
@@
 \begin{solution}
-	Thank you for catching this. Need answer!.
+	Thank you for your question. We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
+
+	The following phrase has been added to the manuscript:\\
+
+	We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
 

### 2020-09-16 paper/introduction.tex
rest comments

@@
 However, this technology has difficulties including safety, 
-online reprocessing, and fuel handling. Safety is one of the primary goals of
-the MSR system, and the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR), in particular, requires further investigation to support a licensing case.
+online reprocessing, and fuel handling.
 The unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
@@
 Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
+According to the demands of nuclear safety regulations, two independent shutdown systems of Control Safety Devices (CSD) and Shutdown Safety Devices (SSD) must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
+All the shutdown systems must meet the shutdown margin of the reactor.
+For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods.
 

### 2020-09-16 paper/results.tex
rest comments

@@
 SDM for the SD-TMSR core that is initially loaded with 
-$^{233}$U and reactor-grade Pu. However, the SDMs for the TRU case are 
+$^{233}$U and reactor-grade Pu.
+We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction.
+Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
+The SDMs for the TRU case are
 negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 

### 2020-09-17 paper/revisions/review-responses.tex
After Andrei's review

@@
 
+The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects the reactor safety \cite{atkinson2019small}.
 Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
-According to the demands of nuclear safety regulations, two independent shutdown systems of Control Safety Devices (CSD) and Shutdown Safety Devices (SSD) must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
-All the shutdown systems must meet the shutdown margin of the reactor.
-For the CSD, it should contain the reactivity adjusting rods, reactor safety rods and reactivity compensation rods.
+According to the demands of nuclear safety regulations, two independent shutdown systems must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
+All the shutdown systems must be sufficient to shut down the reactor at any time during operation.
 
@@
 	We appreciate your detailed review.
-	Indeed rapid solidification would require a very rapid decline in temperature that is precluded by the same negative temperature feedback coefficient due to a reactivity insertion transient at 300 K.
+	Indeed rapid solidification would require a very rapid decline in temperature precluded by the same negative temperature feedback coefficient due to a reactivity insertion transient at 300K.
 That is, the speed of salt temperature reduction is slowed, throughout any fuel cooling transient, by the negative temperature feedback coefficient.
 The feedback coefficient does not suddenly start when the temperature of the salt reaches a specific temperature.
-Indeed, a temperature of 300K could not be reached while power is still being generated in the core.
-Indeed, it could likely only be reached after the power from post-shutdown decay heat has reduced substantially due to time.
+Indeed, a temperature of 300K could not be achieved while power is still being generated in the core.
+It could likely only be reached after the post-shutdown decay heat has reduced substantially due to time.
 If that is the case, then the reactor must have already been shut down.
@@
 
+     The assessment of the optimal absorber radius should be an essential consideration.
+If the CR radius is too large, the absorber material is not effectively utilized due to self-shielding.
 We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted.
@@
 However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$.
-This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
-Other absorbers not significantly affected by the self-shielding phenomenon in the region of study (0.0$<$r$<$1.0 cm).
+This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have a relatively low chance for neutron capture.
+In contrast, other absorbers are not affected by the self-shielding phenomenon in the considered region (0.0$<$r$<$1.0 cm).
 From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
@@
     Thank you for the suggestion.
-According to Robertson \emph{et al.} ``Conceptual design of MSBR`` (1971) the Control rod diameter is 3.75in and the diameter of the hole in the graphite for CR is 4in (ORNL-4548) \cite{robertson_conceptual_1971}.
-Thus, the gap in the MSBR is about 0.635 cm, i.e., $\sim$7\% of the CR diameter.
-Consequently, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
-Regarding thermal emission calculations - it is out of scope and neglected in the current study.
+Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}.
+We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+However, the absorber-cladding gap was neglected for simplicity.
+An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 
@@
 
-	The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+	Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}.
+We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
 However, the absorber-cladding gap was neglected for simplicity.
-Thermal emission calculations is out of scope and also neglected in this study.
+An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 
@@
 
-              Thank you for the comment. What he meant here??
+              Thank you for the comment. The statement has been removed from the text.
 
@@
 Thank you for the question.
-According to Robertson \emph{et al.} ``Conceptual design of MSBR`` (1971) the Control rod diameter is 3.75in and the diameter of the hole in the graphite for CR is 4in (ORNL-4548) \cite{robertson_conceptual_1971}.
-Thus, the gap in the MSBR is about 0.635 cm, i.e., $\sim$7\% of the CR diameter.
-Consequently, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
-Regarding thermal emission calculations - it is out of scope and neglected in the current study.
+Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}.
+We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+However, the absorber-cladding gap was neglected for simplicity.
+An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 
@@
 
-The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}.
+We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
 However, the absorber-cladding gap was neglected for simplicity.
-Thermal emission calculations is out of scope and also neglected in this study.
+An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 
@@
 We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~8.
-Results showed that three rods in the graphite element save the 60-degree symmetry of the element, however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
-In the case of four rods, the 60-degree symmetry of the graphite element is broken, however, the SDM is about $228$ $pcm$ and the A$_{CRi}$ is $0.97$.
-Finally, when six rods are distributed in the graphite element both symmetry and relatively high SDM are obtained ($598$ $pcm$) but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
-Therefore the 3-CRs and 6-CRs configuration are neglected due to the negative SDM and the low A$_{CRi}$, respectively.
-The 4-CRs configuration is adopted in the current study since the SDM is positive and almost no shadowing effect has observed.
+Results showed that three rods in the graphite element save the 60-degree symmetry of the component; however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$.
+Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
+Therefore the 3- and 6-CR configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
+The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.
 

### 2020-09-17 paper/methods.tex
After Andrei's review

@@
 
-The assessment of the optimal absorber radius should be an important consideration.
-If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding.
+The assessment of the optimal absorber radius should be an essential consideration.
+If the CR radius is too large, the absorber material is not effectively utilized due to self-shielding.
 We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted.
@@
 SiC structural material (see Figure~\ref{fig:cr}).
-The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
+Robertson \emph{et al.} suggested the thickness of the gap between the CR and graphite in MSBR of about 7\% of the CR diameter \cite{robertson_conceptual_1971}.
+We adopted this design solution and assumed a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement.
 However, the absorber-cladding gap was neglected for simplicity.
-Thermal emission calculations is out of scope and also neglected in this study.
+An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 All densities of rod materials are listed in

### 2020-09-17 paper/results.tex
After Andrei's review

@@
 We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~\ref{fig:3_CR}.
-Results showed that three rods in the graphite element save the 60-degree symmetry of the element, however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
-In the case of four rods, the 60-degree symmetry of the graphite element is broken, however, the SDM is about $228$ $pcm$ and the A$_{CRi}$ is $0.97$.
-Finally, when six rods are distributed in the graphite element both symmetry and relatively high SDM are obtained ($598$ $pcm$) but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
-Therefore the 3-CRs and 6-CRs configuration are neglected due to the negative SDM and the low A$_{CRi}$, respectively.
-The 4-CRs configuration is adopted in the current study since the SDM is positive and almost no shadowing effect has observed.
+Results showed that three rods in the graphite element save the 60-degree symmetry of the component; however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$.
+Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
+Therefore the 3- and 6-CR configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
+The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.
 

### 2020-09-17 paper/revisions/review-responses.tex
minor edits

@@
 
-	The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems, however, the differential CRWs are calculated for only CSD system.
-Since the reactivity adjustment in the SD-TMSR should be only done by the special adjusting rods (i.e., CSD).
+The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems.
+We calculated the differential CRWs for the CSD system only because special adjusting rods (i.e., CSD) were assumed to adjust the reactivity.
 

### 2020-09-17 paper/results.tex
minor edits

@@
 initially loaded with $^{233}$U, reactor-grade Pu, and TRU 
-elements for different absorbing materials. All absorbing materials provide a sufficient positive
-SDM for the SD-TMSR core that is initially loaded with 
-$^{233}$U and reactor-grade Pu.
+elements for different absorbing materials.
+All absorbing materials provide a sufficient positive SDM for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
 We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction.
 Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
-The SDMs for the TRU case are
-negative or slightly positive (in B$_4$C-90 case); this makes the SSD clusters 
-unreliable to shut down the reactor loaded with TRU.
+The SDMs for the TRU case are negative or slightly positive (in B$_4$C-90 case).
+Thus, the SSD clusters made of non-B$_4$C-90 materials are ineffectual to shut down the reactor loaded with TRU.
 Table~\ref{tab:table50} lists the shutdown margin provided by all SSD clusters when a single SSD cluster with maximum worth (i.e., SSD1) is withdrawn.
-As shown in Table~\ref{tab:table50} the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
-For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.
-This should be carefully studied when designing the reactivity control system.
+As shown in Table~\ref{tab:table50}, the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure (withdrawal) for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
+For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.
 
@@
 
-The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems, however, the differential CRWs are calculated for only CSD system.
-Since the reactivity adjustment in the SD-TMSR should be only done by the special adjusting rods (i.e., CSD).
+The integral CRWs are calculated for three different systems: all CRs, CSD, and SSD systems.
+We calculated the differential CRWs for the CSD system only because special adjusting rods (i.e., CSD) were assumed to adjust the reactivity.
 The CRs are inserted gradually into the core from the top to the bottom. 

### 2020-09-17 paper/Credit_Author_Statement/Credit_Author_Statement.tex

--- 2020-09-15 paper/highlights/highlights.tex
@@
 \begin{frontmatter}
-\title{Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)}
+\title{Credit Author Statement}
 \end{frontmatter}
-\section*{Highlights}
+\section*{The authors contributed to this work as described below}
 \begin{itemize}
-	\item A reliable safety system based on control rods has been introduced in the SD-TMSR.
-	\item Three different initial fissile loadings are considered.
-	\item Six different absorbing materials have been investigated.
-	\item Integral and differential control rod worth, SDM, and shadowing effects at steady-state were calculated.
-	\item SERPENT-2 Monte-Carlo code was used to calculate the reactivity worth.
+	\item \textbf{Osama Ashraf} conceived and designed the simulations, wrote the paper, prepared figures 
+	and/or tables, performed the computation work, and reviewed drafts of the paper.
+	\item \textbf{Andrei Rykhlevskii} conceived and designed the simulations, wrote the paper, prepared figures 
+	and/or tables, performed the computation work, and reviewed drafts of the paper.
+	\item \textbf{G. V. Tikhomirov} directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper.
+	\item \textbf{Kathryn D. Huff} supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
 \end{itemize}

### 2020-09-17 paper/cover-letter/cover-letter.tex
Before submitting to Annals

--- 2020-07-20 paper/cover-letter/cover-letter.tex
@@
 
-\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
+\documentclass[10.5pt]{letter} % Default font size of the document, change to 10pt to fit more text
 \usepackage{graphicx}
@@
 
-		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr.
+		Please consider our revised manuscript, ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr.
 Andrei Rykhlevskii, Prof.
@@
 Kathryn D.
-Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy.
-The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR.
-This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.
+Huff) are submitting for publication as a research article
+		in Annals of Nuclear Energy.
 
-		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal.
-However, we have addressed the major concerns of the reviewers.
-It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.
+		We appreciate the interest that the editors and reviewers have taken in our manuscript and the constructive suggestions they have given.
+We have addressed the major concerns of the reviewers.
+It is our belief that the manuscript is substantially improved after making the suggested edits.
 
-		In the present paper, all calculations presented were performed using Monte-Carlo code SERPENT-2.
-We considered three different initial fissile loadings and applied six different absorbing materials to investigate the main operational and safety parameters in the SD-TMSR.
-Result showed that $^{233}$U and reactor-grade Pu startup cores maintain adequate shutdown margin with all considered absorbers.
-Finally, this paper proposes a design of control rod clusters that compensate the excess reactivity of the SD-TMSR loaded with different initial fissile material.
+		Following this letter is the detailed response to reviewers. We included the 
+		answers in the manuscript. Changes made in the manuscript are marked using track changes.
 
-		Thank you for your consideration of our work. We expect it will be of interest
-		to a broad readership concerned with simulation of MSRs.\\
+	Thank you again for consideration of our revised manuscript.
 

### 2020-09-17 paper/introduction.tex

--- 2020-07-22 paper/introduction.tex
@@
 \cite{vcerba2017optimization}. 
-The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}.
+The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects the reactor safety \cite{atkinson2019small}.
 Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
+According to the demands of nuclear safety regulations, two independent shutdown systems must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
+All the shutdown systems must be sufficient to shut down the reactor at any time during operation.
 

### 2020-10-05 paper/revisions/review-responses.tex
minor edits from Prof. Huff

@@
 Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.
-According to the demands of nuclear safety regulations, two independent shutdown systems must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently.
+According to the demands of nuclear safety regulations, two independent shutdown systems must ensure the reactor safe operation, adjust power, and ensure the shutdown of the reactor anytime independently.
 All the shutdown systems must be sufficient to shut down the reactor at any time during operation.
@@
 		         Thank you for the excellent point.
-The Xenon poison effect is not considered in this paper, but we intend to study this phenomenon in our upcoming article when calculating the worth of the control rods during fuel depletion.
+The xenon poison effect is not considered in this paper, but we intend to study this phenomenon in our upcoming article when calculating the worth of the control rods during fuel depletion.
 The present work focuses on the steady-state calculations without taking into account fuel salt depletion.
@@
 
-		         The Xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
+		         The xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
 
@@
 However, the absorber-cladding gap was neglected for simplicity.
-An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
+Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 
@@
 Now all initial excess reactivities are listed in Table~5 in [pcm] unit.
-Regarding the initial excess reactivity of TRU fuel; TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
+Regarding the initial excess reactivity of TRU fuel; The TRU composition includes substantial thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
 Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}.
@@
 
-	TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
+	The TRU composition includes substantial thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
 Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}.
@@
 As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
-For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.
+For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.
 
@@
 As shown in Table~10 the control rods still meet the shutdown requirement even in the case of SSD1 cluster failure for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
-For the TRU case, increasing the number of SSD clusters would provide a sufficient positive SDM.
-This should be carefully studied when designing the reactivity control system.
+For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.
 
@@
                  Thank you for the excellent point.
-We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~8.
-Results showed that three rods in the graphite element save the 60-degree symmetry of the component; however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element.
+The SD-TMSR initially loaded by TRU was selected for this analysis due to the maximum excess reactivity at startup.
+As shown in Figure~8, the three rods in the graphite element save the 60-degree symmetry of the component; however, results show that the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
 In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$.
 Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
-Therefore the 3- and 6-CR configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
+Therefore the 3- and 6-CRs configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
 The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.
@@
 
-We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~8.
-Results showed that three rods in the graphite element save the 60-degree symmetry of the component; however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element.
+The SD-TMSR initially loaded by TRU was selected for this analysis due to the maximum excess reactivity at startup.
+As shown in Figure~8, the three rods in the graphite element save the 60-degree symmetry of the component; however, results show that the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
 In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$.
@@
 \begin{solution}
-	Thank you for your question. We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
+	Thank you for your question.
+We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total fraction of delayed neutron precursors.
+Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
 
@@
 
-	We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
+	We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total fraction of delayed neutron precursors. Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
 

### 2020-10-05 paper/conclusion.tex
minor edits from Prof. Huff

@@
 shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
-case). Increasing the number of SSD clusters would provide a sufficient positive SDM for the TRU case.
+case). For the TRU case, in the case of SSD1 cluster failure, substitutional insertion of CSD with SSD clusters will provide a sufficient positive SDM.
 
@@
 batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. 
-The Xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
+The xenon poison effect will be studied in our upcoming article when calculating the worth of the control rods during fuel depletion.
 Additionally, the authors intend to investigate

### 2020-10-05 paper/methods.tex
minor edits from Prof. Huff

@@
 \begin{table}  %[!ht]
-	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
+	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020thermal}.}
 	\vspace{0.1in}
@@
 	\includegraphics[width=\textwidth]{Radius.png}
-	\caption{The change of the effective multiplication factor with the radius of the B$_4$C control rod.}
+	\caption{The change of the effective multiplication factor with the radius of the control rod for all different absorbers.}
 	\label{fig:Radius}
@@
 However, the absorber-cladding gap was neglected for simplicity.
-An important physical effect, thermal emission, and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
+Thermal emission and corresponding thermal-hydraulics simulations to predict the temperature of the salt around CRs are out of the scope of this study and will be covered in future work.
 All densities of rod materials are listed in

### 2020-10-05 paper/results.tex

@@
 For $^{233}$U case \cite{ashraf2020Strategies} the initial excess reactivity is about $1180\pm28$ $pcm$, however, the maximum observed excess reactivity is $1344\pm25$ $pcm$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} after $\approx$ 8 EFPY of operation).
-TRU has a great amount of thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
+The TRU composition includes substantial thermal neutron absorbers, therefore, the SD-TMSR becomes subcritical relatively quickly.
 Previous studies showed that for promising fueling scenarios (e.g., TRU/$^{232}$Th), large excess reactivity is required for long-term core operation \cite{ashraf2020Strategies,betzler2017assessment,rykhlevskii_fuel_2019}.
@@
 All absorbing materials provide a sufficient positive SDM for the SD-TMSR core that is initially loaded with $^{233}$U and reactor-grade Pu.
-We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total delayed fraction.
+We considered the sufficient positive SDM to be 2$\beta$, where $\beta$ is the total fraction of delayed neutron precursors.
 Thus, the sufficient positive SDM is $\sim$1300 $pcm$.
@@
 
-We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element for the SD-TMSR initially loaded by TRU (maximum excess reactivity at startup) as demonstrated in Figure~\ref{fig:3_CR}.
-Results showed that three rods in the graphite element save the 60-degree symmetry of the component; however, the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
+We calculated the shutdown margin (SDM) and the amplification factor (A$_{CRi}$) for three different configurations of the CRs in the graphite element.
+The SD-TMSR initially loaded by TRU was selected for this analysis due to the maximum excess reactivity at startup.
+As shown in Figure~\ref{fig:3_CR}, the three rods in the graphite element save the 60-degree symmetry of the component; however, results show that the SDM in such a case is $-1058$ $pcm$ and the A$_{CRi}$ is $1.09$.
 In the case of four rods, the 60-degree symmetry of the graphite element is broken; however, the SDM is about $228$ $pcm$, and the A$_{CRi}$ is $0.97$.
 Finally, when six rods are distributed evenly in the graphite element, both symmetry and relatively high SDM are obtained ($598$ $pcm$), but the A$_{CRi}$ is about $0.29$, which means high interference between rods due to the shadowing effect in this case.
-Therefore the 3- and 6-CR configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
+Therefore the 3- and 6-CRs configurations are ineffectual due to the negative SDM and the low A$_{CRi}$, respectively.
 The 4-CRs configuration is adopted in the current study since the SDM is positive, and almost no shadowing effect has been observed.
@@
 	\vspace{-0.5in}
-	\caption{$XY$ section of graphite element with a) 3-CRs b) 4-CR c) 6-CRs configurations.} 
+	\caption{$XY$ section of graphite element with a) 3-CRs b) 4-CRs c) 6-CRs configurations.} 
 	\label{fig:3_CR}
